---
title: "Discrimination task analysis"
format: html
editor: source 
---

## Fit proportion correct

Discrimination Task:

3 Diferent models:

Fit the responses of the discrimination tasks from an internal representation:

Fit 3 different models of the internal representation:



Asymetric naka rushton:

$$
\mu = \frac{p_1 \cdot x^{p_2}}{x^{p_2 + p_4} + p_3^{p_2 + p_4}}
$$


```{r tidy data discrimination, include=FALSE}
d_dat <- d_dat_raw |>
  ungroup() |> 
  select(participant, order, c_pedestal, c_comparison, c_dif, response) |> 
  rename(abs_x_p = c_pedestal, abs_x_c = c_comparison, 
         r = response, x_dif = c_dif) |> 
  mutate(order = if_else(order == 1, 1, -1), 
         x_p = abs_x_p * order, x_c = abs_x_c * order, 
         r = if_else(r == "right", 1,0),
         correct = if_else((order == 1 & r == 1) | 
                             (order == -1 & r == 0), 1, 0)) 

d_dat
```



```{r asymetric fit nloptr, include=FALSE}
set.seed(1000)

correct_par_ini_asym_nloptr <- c(20, 3, .02, -.5, 0.5, 0.01, 0.6 ) 
correct_par_ini_asym_nloptr_lower <- c(0,  1, 0, -1, 0.0001, 0.0001, 0.001)
correct_par_ini_asym_nloptr_upper <- c(50, 10, .1, 0, 2, 0.5, 2)

d_fit_asym <- d_dat |>
  group_by(participant) |>
  nest() |>
  mutate(fit = map(data, function(d) {
        fit_psy_mu_noise(
          d$abs_x_p,
          d$abs_x_c,
          d$correct,
          create_psy_mu_fix_lapses_noise(),
          asym_naka_fun_mu,
          power_sigma_asym_naka_mu,
          correct_par_ini_asym_nloptr,
          correct_par_ini_asym_nloptr_lower,
          correct_par_ini_asym_nloptr_upper,
          "nloptr",
          samples = 800)
  } )) |>
  select(-data) |>
  unnest_wider(fit)

d_fit_asym |>
  select(participant, par) |>
  unnest(par) |>
  ggplot(aes(x = parn, y = par)) +
  facet_wrap(~parn, scales = "free") +
  geom_point(aes(color = participant),
             position = position_jitter(height = 0)) +
  geom_point(data = tibble(parn = paste0("p", seq_along(correct_par_ini_asym_nloptr_upper)),
                           par = correct_par_ini_asym_nloptr_upper), color = "red", shape = 2) +
  geom_point(data = tibble(parn = paste0("p", seq_along(correct_par_ini_asym_nloptr_lower)),
                           par = correct_par_ini_asym_nloptr_lower), color = "red", shape = 2) +
  theme()
```



```{r psy models together, include=FALSE}
d_prop<- d_fit_asym |>
  select(participant, prop) |>
  unnest(prop)

d_psy <- d_fit_asym |>
  select(participant, psy) |>
  unnest(psy)
```

## Plot fits of proportion correct from the models

```{r, plot fit models, fig.width=8, fig.height=20, echo=FALSE}
 ggplot() +
    facet_wrap(vars(participant, abs_x_p), ncol = 4, scales = "free_x") +
    geom_point(data = d_prop |> 
                 mutate(abs_x_p = abs(x_p)), size = .75,
                        aes(x = x_c - x_p, y = prop)) +
    geom_line(data = d_psy |> 
                mutate(abs_x_p = abs(x_p)),
              aes(x = x_c - x_p, y = prop)) +
  xlab("Contrast") +
  ylab("P correct")


```

```{r plot together the references, include=FALSE}
ggplot() +
  facet_wrap(vars(participant), ncol = 4) +
  geom_point(data = d_prop, size = .75,
             aes(x = x_c, y = prop, color = factor(x_p))) +
    geom_line(data = d_psy,
            aes(x = x_c, y = prop, color = factor(x_p)))
```

## Plot fits of the internal representation from the models
mu

```{r best model, echo=FALSE}

d_delta_asym <- d_fit_asym |>
  select(participant, mu) |> 
  unnest(mu)

p_d_delta_mu  <- ggplot() +
  facet_wrap(vars(participant), scales = "free") +
  geom_line(data= d_delta_asym, aes(x, y)) +
  xlab("Contrast") +
  ylab("mu")

p_d_delta_mu
```

sigma
```{r plot sd, echo=FALSE}
p_d_delta_sigma <- ggplot() +
  facet_wrap(vars(participant), scales = "free") +
  geom_line(data= d_delta_asym, aes(x, sigma)) +
  xlab("Contrast") +
  ylab("sigma")
p_d_delta_sigma
```


## Plot sensitivity (delta) from the models: 
```{r delta best model, echo=FALSE}
p_d_delta <- ggplot() +
  facet_wrap(vars(participant)) +
  geom_line(data= d_delta_asym,
            aes(x, delta)) +
  xlab("Contrast") +
  ylab("P correct")
p_d_delta
```
