---
title: "Magnitude estimation descriptive"
format: html
editor: source
---

## Preprocessing data ME:

Address scale inconsistencies, filter out outliers, and normalize the data.


Plot raw data
```{r plot raw data, echo=FALSE}
m_dat_raw |> 
  ggplot() + 
  facet_wrap(vars(participant), scales = "free_y") + 
  geom_point(aes(x = c, y = r), size = .85, alpha = .5) + 
  geom_smooth(aes(x = c, y = r),
              method = "loess", formula = "y ~ x", se = FALSE)
```


### Scales inconsistencies:

```{r plorbly trial, include=FALSE}
m_trial <- m_dat_raw |>  group_by(participant) |>
  select(participant, session, trial, r, c) |>
  mutate(c_log = log10(c),
         r_log = log10(r)) |> 
  group_by(participant, session) |> 
  arrange(trial, .by_group = TRUE) |> 
  mutate(trial = if_else(session == "01", trial, trial + 200)) |> 
  ungroup()

m_trial|> 
  ggplot(aes(x = trial, y = r)) +
  facet_wrap(vars(participant)) +
  geom_point()

```


```{r trial intervals, include=FALSE}
m_dat_bin_trial  <- m_trial |> 
  ungroup() |> 
  mutate(trial_int = cut_interval(trial, n = 10))  |> 
  group_by(participant, trial_int) |> 
  mutate(trial_center = mean(trial)) 

m_dat_bin_trial |> 
  group_by(participant, trial_center) |> 
  count()
```

```{r plot trial intervals, include=FALSE}
m_dat_bin_trial |> 
  ggplot(aes(trial_center, r)) +
  geom_point(size = .25, alpha = .25) +#, position = position_jitter(height = NULL)) +
  facet_wrap(vars(participant), scales = "free_y") +
  theme_bw()
```

```{r mean trial, include=FALSE}
m_summ_bin_trial <- m_dat_bin_trial |> 
  group_by(participant, trial_center) |> 
  nest() |> 
  mutate(
    model = map(data, ~ loess(r ~ c, data = ., span = 0.75)),
    augmented = map(model, ~ augment(., se_fit = TRUE))
  ) |>
  select(!model) |> 
  unnest(data, augmented) |> 
  mutate(r_new = r-.fitted) |> 
  summarise(m = mean(r_new), 
            sta_dev = sd(r_new),
            .groups = "keep") |> 
  rename(trial = trial_center) 
```

```{r mean and standard deviation trial, include=FALSE}
m_summ_bin_trial |>  
  ggplot(aes(x = trial, y = m)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin = m - sta_dev, ymax = m + sta_dev))+
  facet_wrap(vars(participant), scales = "free_y")
```


```{r mean and standard deviation trial with limits, echo=FALSE}
m_summ_bin_trial <- m_summ_bin_trial |>  
  ungroup() |> 
  group_by(participant) |> 
  mutate(mean_sta_dev = mean(sta_dev),
         mean_m = mean(m))
  
  
m_summ_bin_trial |>  
  ggplot(aes(x = trial, y = m)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin = m - sta_dev, ymax = m + sta_dev)) +
  facet_wrap(vars(participant), scales = "free_y") +
  geom_hline(aes(yintercept = mean_m + mean_sta_dev*3), color = "red", linetype = "dashed") +
  geom_hline(aes(yintercept = mean_m - mean_sta_dev*3), color = "red", linetype = "dashed")
```

filtering data removing scales inconsistencies

```{r filter scales inconsistencies, include=FALSE}
m_dat_filt <- m_dat_raw |>
  select(participant, session, trial, r, c) |>
  filter(!(participant== "s03" & session=="01" & trial < 40)) |>
  filter(!(participant== "s11" & session=="01" & trial < 40)) |>
  filter(!(participant == "s09" & session == "01"& trial < 40)) |> 
  mutate(c_log = log10(c),
         r_log = log10(r))
```


Plot filtered data :
```{r plot raw data filtered, echo=FALSE}
m_dat_raw |> 
  ggplot() + 
  facet_wrap(vars(participant), scales = "free_y") + 
  geom_point(aes(x = c, y = r), size = .85, alpha = .5) + 
  geom_point(data = m_dat_raw |> filter(trial < 40 & session == "01") |> 
               filter(participant %in% c("s03", "s09", "s11")),
             aes(x = c, y = r), color = "red", size = .85) +
  geom_smooth(aes(x = c, y = r),
              method = "loess", formula = "y ~ x", se = FALSE)
```



### Filter Outliers:


```{r mean responses outliers, include=FALSE}
m_mean_r_outliers <- m_dat_filt |> 
  group_by(participant) |> 
  summarise(m_r = mean(r))
```


```{r normalized responses outliers, include=FALSE}
m_dat_outliers <- m_dat_filt |> 
  left_join(m_mean_r_outliers, by = join_by(participant)) 
```



```{r intervals outliers, include=FALSE}
m_dat_bin_outliers  <- m_dat_outliers |> 
  ungroup() |> 
  mutate(c_int = cut_interval(c_log, n = 10))  |> 
  group_by(participant, c_int) |> 
  mutate(c_center = mean(c)) 

m_dat_bin_outliers |> 
  group_by(participant, c_center) |> 
  count()
```

Respuestas en cada intervalo:

```{r plot intervals outliers, include=FALSE}
m_dat_bin_outliers |> 
  ggplot(aes(c_center, r)) +
  geom_point(size = .25, alpha = .25, position = position_jitter(height = 0)) +
  facet_wrap(vars(participant), scales = "free_y") +
  theme_bw()
```

Mean of responses by participants

```{r mean outliers, include=FALSE}
m_summ_bin_outliers <- m_dat_bin_outliers |> 
  group_by(participant, c_center) |> 
  mutate(m = mean(r), 
            sta_dev = sd(r), 
            .groups = "keep") 

m_summ_bin_outliers |> 
  ggplot(aes(x = c_center, y = m)) +
  facet_wrap(vars(participant), scales = "free_y") +
  geom_point() +
  geom_line() 
```
Standard deviation

```{r standard deviation outliers, include=FALSE}
m_summ_bin_outliers |> 
  ggplot(aes(x = c_center, y = sta_dev)) +
  facet_wrap(vars(participant), scales = "free_y") +
  geom_point() +
  geom_line() 
```

```{r mean and standard deviation outliers, include=FALSE}
m_summ_bin_outliers |> 
  ggplot(aes(x = c_center, y = m)) +
  facet_wrap(vars(participant), scales = "free_y") +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin = m - sta_dev, ymax = m + sta_dev))
```




#### Identify outliers:

```{r identidy outliers, echo=FALSE, message=FALSE}

m_outliers <- m_summ_bin_outliers |> 
  group_by(participant) |> 
  nest() |> 
  mutate(
    model = map(data, ~ loess(r ~ c, data = ., span = 0.75)),
    augmented = map(model, ~ augment(., se_fit = TRUE))
  ) |> 
  unnest(data, augmented)|>
  select(!c(model, r1, c1)) |> 
  group_by(participant, c_center) |> 
  mutate(min = .fitted - sta_dev*3 - 0.5*m_r,     ##2.9 #m_r
         max = .fitted + sta_dev*3 + 0.5*m_r) |> 
  mutate(outlier = (r < min | (r > max)))
  

ggplotly(m_outliers|> 
  ggplot() + 
  facet_wrap(vars(participant), scales = "free_y") + 
  geom_point(aes(x = c, y = r, color = as_factor(outlier)), size = .85, alpha = .5) + 
  geom_smooth(aes(x = c, y = .fitted)) +
  geom_ribbon(aes(x = c, ymin = min, ymax = max), fill = "orange", alpha = 0.5))

```

Filter outliers:
```{r filter outliers, include=FALSE}
m_dat_no_outliers <- m_outliers |>
  filter(!outlier) 
```


### Zeros:

Take out some zeros for the fits

```{r zeros s05, include=FALSE}
zeros_s05 <- m_dat_no_outliers |> 
  filter(participant == "s05") |> 
  arrange(c) |> 
  filter(c < .01)

m_dat_some_zeros_s05 <- m_dat_no_outliers |> 
  filter(participant == "s05") |> 
  anti_join(zeros_s05)

m_dat_no_outliers |> 
  filter(participant == "s05") |>
  ggplot(aes(x = c, y = r)) +
  geom_point(alpha = .5) +
  geom_point(data = zeros_s05, aes(x = c, y = r), color = "red") +
  theme()


m_dat_no_outliers |> filter(participant == "s05") |> ungroup() |> filter(r == 0) |> arrange(c) |> count()
m_dat_no_outliers |> filter(participant == "s05") |> ungroup() |> arrange(c) |> count()
zeros_s05 |> ungroup() |> count()
  
```


```{r zeros s09, include=FALSE}
zeros_s09 <- m_dat_no_outliers |> 
  filter(participant == "s09") |> 
  arrange(c) |> 
  filter(c < .016)
  #filter(c < .017)

m_dat_some_zeros_s09 <- m_dat_no_outliers |> 
  filter(participant == "s09") |> 
  anti_join(zeros_s09)
  

m_dat_no_outliers |> 
  filter(participant == "s09") |>
  ggplot(aes(x = c, y = r)) +
  geom_point(alpha = .5) +
  geom_point(data = zeros_s09, aes(x = c, y = r), color = "red") +
  theme()


m_dat_no_outliers |> filter(participant == "s09") |> ungroup() |> filter(r == 0) |> arrange(c) |> count()
m_dat_no_outliers |> filter(participant == "s09") |> ungroup() |> arrange(c) |> count()

zeros_s09 |> ungroup() |> count()

```

```{r zeros s11, include=FALSE}
zeros_s11 <- m_dat_no_outliers |> 
  filter(participant == "s11") |> 
  arrange(c) |> 
  filter(c < .009)

m_dat_some_zeros_s11 <- m_dat_no_outliers |> 
  filter(participant == "s11") |> 
  anti_join(zeros_s11)
  

m_dat_no_outliers|> 
  filter(participant == "s11") |>
  ggplot(aes(x = c, y = r)) +
  geom_point(alpha = .5) +
  geom_point(data = zeros_s11, aes(x = c, y = r), color = "red") +
  theme()

m_dat_no_outliers |> filter(participant == "s11") |> ungroup() |> filter(r == 0) |> arrange(c) |> count()
m_dat_no_outliers |> filter(participant == "s11") |> ungroup() |> arrange(c) |> count()

zeros_s11 |> ungroup() |> count()

```

```{r zeros, include=FALSE}
m_dat_zeros <- m_dat_no_outliers |> 
  arrange(participant, c) |>
  filter(!(participant == "s05" & c < .01)) |> 
  filter(!(participant == "s09" & c < .016)) |> 
  filter(!(participant == "s11" & c < .009))

m_dat_no_outliers |> filter(participant == "s05")

```

Data without outliers:
```{r plot data without outliers, echo=FALSE}

m_mean_r <- m_dat_zeros |> 
  group_by(participant) |> 
  summarise(m_r = mean(r))

m_dat <- m_dat_zeros |>
  select(!m_r) |> 
  left_join(m_mean_r, by = join_by(participant)) |> 
  mutate(r_norm = r / m_r)



ggplot(m_dat) +
  facet_wrap(vars(participant), scale = "free_y") +
  geom_point(aes(x = c, y = r_norm), size = .5)
```

### Normalize data: 

Calculate mean and standard deviation

Create intervals and calculate the mean and standard deviation of each interval for each participant.

The intervals are created in c log, but the data is analyzed linear. This way we have the same amount of data in each interval, but the analysis is with raw data.

<!-- Para que los datos estén bien distribuidos (creo). -->

```{r intervals, include=FALSE}
m_dat_bin  <- m_dat |> 
  ungroup() |> 
  mutate(c_int = cut_interval(c_log, n = 10))  |> 
  group_by(participant, c_int) |> 
  mutate(c_center = mean(c)) 

m_dat_bin |> 
  group_by(participant, c_center) |> 
  count()
```


```{r plot intervals, echo=FALSE}
m_dat_bin |> 
  ggplot(aes(c_center, r)) +
  geom_point(size = .25, alpha = .25, position = position_jitter(height = NULL)) +
  facet_wrap(vars(participant), scales = "free_y") +
  theme_bw()
```

Calculate mean and sd of responses by participants.

<!-- dataframe for summarise of responses: mean, sd, normalized mean, normalized sd. -->

```{r mean, echo=FALSE}
m_summ_bin <- m_dat_bin |> 
  group_by(participant, c_center) |> 
  summarise(m = mean(r), 
            sta_dev = sd(r), 
            m_norm = mean(r_norm),
            sta_dev_norm = sd(r_norm),
            .groups = "keep") |> 
  rename(c = c_center) 

m_summ_bin_all <- m_dat_bin |> 
  mutate(participant = "all") |> 
  mutate(c_center = round(c_center, 3)) |> 
  group_by(participant, c_center) |> 
  summarise(m = mean(r), 
            sta_dev = sd(r), 
            m_norm = mean(r_norm),
            sta_dev_norm = sd(r_norm),
            .groups = "keep") |> 
  rename(c = c_center) 
```



Mean responses

```{r mean responses, echo=FALSE}
m_summ_bin |> 
  ggplot(aes(x = c, y = m)) +
  facet_wrap(vars(participant), scales = "free_y") +
  geom_point() +
  geom_line() 
```

Mean responses (normalized):
```{r normalized mean each participant, echo=FALSE}
m_summ_bin |> 
  ggplot(aes(x = c, y = m_norm)) +
  facet_wrap(vars(participant)) +
  geom_point(aes(color = participant)) +
  geom_line(aes(color = participant))
```

Standard deviation:

```{r standard deviation, echo=FALSE}
m_summ_bin |> 
  ggplot(aes(x = c, y = sta_dev)) +
  facet_wrap(vars(participant), scales = "free_y") +
  geom_point() +
  geom_line() +
  ylim(0, NA) 
```

Standard deviation (normalized):

```{r normalized standard deviation, echo=FALSE}
m_summ_bin |> 
  ggplot(aes(x = c, y = sta_dev_norm)) +
  facet_wrap(vars(participant), scales = "free_y") +
  geom_point(aes(color = participant)) +
  geom_line(aes(color = participant)) +
  xlim(0, NA) +
  ylim(0, NA) +
  theme(legend.position = "none")
```

Mean and standard deviation:

```{r mean and standard deviation, echo=FALSE}
m_summ_bin |>  
  ggplot(aes(x = c, y = m)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin = m - sta_dev, ymax = m + sta_dev))+
  facet_wrap(vars(participant), scales = "free_y")
```

Mean and standard deviation (normalized) :

```{r normalized mean and standard deviation, echo=FALSE}
m_summ_bin |>  
  ggplot(aes(x = c, y = m_norm)) +
  facet_wrap(vars(participant), scales = "free_y") +
  geom_hline(yintercept = 0, lty = 2) +
  geom_point(aes(color = participant)) +
  geom_line(aes(color = participant)) +
  geom_errorbar(aes(ymin = m_norm - sta_dev_norm, ymax = m_norm + sta_dev_norm, color = participant)) +
  theme(legend.position = "none") 
```


## All participants together:

Raw Data

```{r raw data all participants, echo=FALSE}
m_dat |> 
  ggplot() + 
  geom_point(aes(x = c, y = r_norm), size = .85, alpha = .5) + 
  geom_smooth(aes(x = c, y = r_norm),
                    method = "loess", formula = "y ~ x", se = FALSE)
```


Plot raw data log:

```{r raw data all participants log, include=FALSE}
m_dat |> 
  ggplot() + 
  geom_point(aes(x = c_log, y = r_norm), size = .85, alpha = .5) + 
  geom_smooth(aes(x = c_log, y = r_norm),
                    method = "loess", formula = "y ~ x", se = FALSE)
```

Calculate mean and standard deviation

Create intervals and calculate the mean and standard deviation of each interval for each participant.

The intervals are created in c log, but the data is analyzed linear. <!-- Para que los datos estén bien distribuidos (creo). -->

```{r data for all participants together, include=FALSE}
m_dat_bin_all  <- m_dat |> 
  ungroup() |> 
  mutate(c_int = cut_interval(c_log, n = 10))  |> 
  group_by(c_int) |> 
  mutate(c_center = mean(c)) 

m_dat_bin_all |> 
  group_by(c_center) |> 
  count()
```

Respuestas en cada intervalo

```{r intervals all participants together, echo=FALSE}
m_dat_bin_all |> 
  ggplot(aes(c_center, r)) +
  geom_point(size = .5, alpha = .5) 
```

<!-- ### dataframe for summarise of responses: mean, sd, normalized mean, normalized sd. -->

```{r summarise of responses, include=FALSE}
m_summ_bin_all <- m_dat_bin_all |> 
  group_by(c_center) |> 
  summarise(m = mean(r), 
            sta_dev = sd(r), 
            m_norm = mean(r_norm),
            sta_dev_norm = sd(r_norm),
            .groups = "keep") |> 
  rename(c = c_center) 

```

Mean responses normalized

```{r normalized mean responses all participants together, echo=FALSE}
m_summ_bin_all |> 
  ggplot(aes(x = c, y = m_norm)) +
  geom_point() +
  geom_line() 
```

Standard deviation (normalized):

```{r normalized standard deviation all participants together, echo=FALSE}
m_summ_bin_all |> 
  ggplot(aes(x = c, y = sta_dev_norm)) +
  geom_point() +
  geom_line() +
  xlim(0, NA) +
  ylim(0, NA)
```

Mean and standard deviation (normalized) :

```{r normalized mean responses and standard deviation all participants together, echo=FALSE}
m_summ_bin_all |>  
  ggplot(aes(x = c, y = m_norm)) +
  geom_hline(yintercept = 0, lty = 2) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin = m_norm - sta_dev_norm, ymax = m_norm + sta_dev_norm))
```



