---
title: "Power models"
format: html
editor: source
---

Power mu
$$
\Large \mu = p_1 \cdot x^{p_2} 
$$
## Model 2_1: 

Power mu, constant sigma
$$
\sigma = {p_3} 
$$

#### s01 {.hidden}

```{r power mu constant noise s01, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_1_s01 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s01", 
  power_fun_mu,
  constant_sigma_power_mu,
  rep(.0000001, 3), 
  c(80, 2.5, 30))

m_fit_2_1_s01$p
```


```{r power mu constant noise parameters s01, include=FALSE}
m_fit_2_1_s01$p_par
```



#### s02 {.hidden}

```{r power mu constant sigma s02, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_1_s02 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s02", 
  power_fun_mu,
  constant_sigma_power_mu,
  rep(.0000001, 3), 
  c(80, 2.5, 30))

m_fit_2_1_s02$p
```


```{r power mu constant sigma parameters s02, include=FALSE}
m_fit_2_1_s02$p_par
```



#### s03 {.hidden}

```{r power mu constant sigma s03, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_1_s03 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s03", 
  power_fun_mu,
  constant_sigma_power_mu,
  rep(.0000001, 3), 
  c(80, 2.5, 30))

m_fit_2_1_s03$p
```


```{r power mu constant sigma parameters s03, include=FALSE}
m_fit_2_1_s03$p_par
```


#### s04 {.hidden}

```{r power mu constant sigma s04, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_1_s04 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s04", 
  power_fun_mu,
  constant_sigma_power_mu,
  rep(.0000001, 3), 
  c(80, 2.5, 30))

m_fit_2_1_s04$p
```


```{r power mu constant sigma parameters s04, include=FALSE}
m_fit_2_1_s04$p_par
```


#### s05 {.hidden}


```{r power mu constant sigma s05, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_1_s05 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s05", 
  power_fun_mu,
  constant_sigma_power_mu,
  rep(.0000001, 3), 
  c(80, 2.5, 30))

m_fit_2_1_s05$p
```


```{r power mu constant sigma parameters s05, include=FALSE}
m_fit_2_1_s05$p_par
```

#### s06 {.hidden}

```{r power mu constant sigma s06, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_1_s06 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s06", 
  power_fun_mu,
  constant_sigma_power_mu,
  rep(.0000001, 3), 
  c(80, 2.5, 30))

m_fit_2_1_s06$p
```

```{r power mu constant sigma parameters s06, include=FALSE}
m_fit_2_1_s06$p_par
```

#### s07 {.hidden}

```{r power mu sigma constant s07, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_1_s07 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s07", 
  power_fun_mu,
  constant_sigma_power_mu,
  rep(.0000001, 3), 
  c(80, 2.5, 30))

m_fit_2_1_s07$p
```

```{r power mu constant sigma parameters s07, include=FALSE}
m_fit_2_1_s07$p_par
```

#### s08 {.hidden}

```{r power linear mu sigma constant s08, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_1_s08 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s08", 
  power_fun_mu,
  constant_sigma_power_mu,
  rep(.0000001, 3), 
  c(80, 2.5, 30))

m_fit_2_1_s08$p
```

```{r power mu constant sigma parameters s08, include=FALSE}
m_fit_2_1_s08$p_par
```

#### s09 {.hidden}


```{r power mu constant sigma s09, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_1_s09 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s09", 
  power_fun_mu,
  constant_sigma_power_mu,
  rep(.0000001, 3), 
  c(80, 2.5, 50))

m_fit_2_1_s09$p
```


```{r power mu constant sigma parameters s09, include=FALSE}
m_fit_2_1_s09$p_par
```


#### s10 {.hidden}


```{r power mu constant sigma s10, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_1_s10 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s10", 
  power_fun_mu,
  constant_sigma_power_mu,
  rep(.0000001, 3), 
  c(80, 2.5, 30))

m_fit_2_1_s10$p
```

```{r power mu constant sigma parameters s10, include=FALSE}
m_fit_2_1_s10$p_par
```


#### s11 {.hidden}


```{r power mu constant sigma, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_1_s11 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s11", 
  power_fun_mu,
  constant_sigma_power_mu,
  rep(.0000001, 3), 
  c(80, 2.5, 30))
m_fit_2_1_s11$p
```

```{r power mu constant sigma parameters s11, include=FALSE}
m_fit_2_1_s11$p_par
```



```{r power mu constant sigma fits, include=FALSE}
individual_fits_2_1 <- bind_rows(
  m_fit_2_1_s01$fit,
  m_fit_2_1_s02$fit,
  m_fit_2_1_s03$fit,
  m_fit_2_1_s04$fit,
  m_fit_2_1_s05$fit,
  m_fit_2_1_s06$fit,
  m_fit_2_1_s07$fit,
  m_fit_2_1_s08$fit,
  m_fit_2_1_s09$fit,
  m_fit_2_1_s10$fit,
  m_fit_2_1_s11$fit
)
```

```{r power mu constant sigma predictions, include=FALSE}
individual_preds_2_1 <- bind_rows(
  m_fit_2_1_s01$pred,
  m_fit_2_1_s02$pred,
  m_fit_2_1_s03$pred,
  m_fit_2_1_s04$pred,
  m_fit_2_1_s05$pred,
  m_fit_2_1_s06$pred,
  m_fit_2_1_s07$pred,
  m_fit_2_1_s08$pred,
  m_fit_2_1_s09$pred,
  m_fit_2_1_s10$pred,
  m_fit_2_1_s11$pred
)
```


```{r power mu constant sigma plot raw data, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_dat, aes(x = c, y = r_norm))+
    geom_line(data = individual_preds_2_1, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1.2)
```


```{r power mu constant sigma plot mean, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = m_norm)) +
        # geom_line(data = m_pred_model_2_1, 
        #       aes(x = x, y = mu), color = "blue", alpha = .5) +
    geom_line(data = individual_preds_2_1, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1) 



```


```{r power mu constant sigma sd, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
      # geom_line(data = m_pred_model_2_1,
      #       aes(x = x, y = sigma), color = "blue", alpha = .5) +
    geom_line(data = individual_preds_2_1,
            aes(x = x, y = sigma), color = "navajowhite3", linewidth = 1) +

  
  ylim(0, NA) 

```

```{r power mu constant sigma delta, include=FALSE}
ggplot() +
  facet_wrap(vars(participant)) +
  #geom_line(data= d_delta, aes(x, delta_d)) +
  geom_line(data = individual_preds_2_1, 
            aes(x, delta_m), color = "aquamarine4", linewidth = 0.9) 
```

## Model 2_2: 
Power mu, poisson sigma

$$
\sigma = \sqrt{\mu} + {p_3}
$$

#### s01 {.hidden}

```{r power mu poisson sigma s01, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_2_s01 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s01", 
  power_fun_mu,
  poisson_sigma_power_mu,
  rep(.0000001, 3), 
  c(250, 5, .1))

m_fit_2_2_s01$p
```


```{r power mu poisson sigma parameters s01, include=FALSE}
m_fit_2_2_s01$p_par
```



#### s02 {.hidden}

<!-- p1 se va mucho -->

```{r power mu poisson sigma s02, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_2_s02 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s02", 
  power_fun_mu,
  poisson_sigma_power_mu,
  # rep(.0000001, 3), 
  # c(250, 5, .1))
  rep(.0000001, 3), 
  c(148, 10, .1))

m_fit_2_2_s02$p
```


```{r power mu poisson sigma parameters s02, include=FALSE}
m_fit_2_2_s02$p_par
```


#### s03 {.hidden}


```{r power mu poisson sigma s03, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_2_s03 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s03", 
  power_fun_mu,
  poisson_sigma_power_mu,
  # rep(.0000001, 3), 
  # c(250, 5, .1))
  rep(.0000001, 3), 
  c(500, 10, .1))

m_fit_2_2_s03$p
```


```{r power mu poisson sigma parameters s03, include=FALSE}
m_fit_2_2_s03$p_par
```

#### s04 {.hidden}

```{r power mu poisson sigma s04, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_2_s04 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s04", 
  power_fun_mu,
  poisson_sigma_power_mu,
  rep(.0000001, 3), 
  c(250, 5, .1))


m_fit_2_2_s04$p
```


```{r power mu poisson sigma parameters s04, include=FALSE}
m_fit_2_2_s04$p_par
```


#### s05 {.hidden}


```{r power mu poisson sigma s05, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_2_s05 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s05", 
  power_fun_mu,
  poisson_sigma_power_mu,
  rep(.0000001, 3), 
  c(500, 5, .1))

m_fit_2_2_s05$p
```


```{r power mu poisson sigma parameters s05, include=FALSE}
m_fit_2_2_s05$p_par
```


#### s06 {.hidden}

```{r power mu sigma poisson s06, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_2_s06 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s06", 
  power_fun_mu,
  poisson_sigma_power_mu,
  rep(.0000001, 3), 
  c(250, 5, .1))

m_fit_2_2_s06$p
```

```{r power mu poisson sigma parameters s06, include=FALSE}
m_fit_2_2_s06$p_par
```


#### s07 {.hidden}

```{r power mu poisson sigma s07, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_2_s07 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s07", 
  power_fun_mu,
  poisson_sigma_power_mu,
  rep(.0000001, 3), 
  c(50, 2, .1))

m_fit_2_2_s07$p
```

```{r power mu poisson sigma parameters s07, include=FALSE}
m_fit_2_2_s07$p_par
```

#### s08 {.hidden}

```{r power mu poisson sigma, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_2_s08 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s08", 
  power_fun_mu,
  poisson_sigma_power_mu,
  rep(.0000001, 3), 
  c(148, 5, .1))

m_fit_2_2_s08$p
```

```{r power mu poisson sigma parameters s08, include=FALSE}
m_fit_2_2_s08$p_par
```

#### s09 {.hidden}


```{r power mu poisson sigma s09, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_2_s09 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s09", 
  power_fun_mu,
  poisson_sigma_power_mu,
  rep(.0000001, 3), 
  c(250, 5, 2))

m_fit_2_2_s09$p
```


```{r power mu poisson sigma parameters s09, include=FALSE}
m_fit_2_2_s09$p_par
```


#### s10 {.hidden}

```{r power mu poisson sigma s10, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_2_s10 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s10", 
  power_fun_mu,
  poisson_sigma_power_mu,
  rep(.0000001, 3), 
  c(250, 5, .1))

m_fit_2_2_s10$p
```

```{r power mu poisson sigma parameters s10, include=FALSE}
m_fit_2_2_s10$p_par
```

#### s11 {.hidden}

```{r power mu poisson sigma s11, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_2_s11 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s11", 
  power_fun_mu,
  poisson_sigma_power_mu,
  rep(.0000001, 3), 
  c(250, 5, .1))

m_fit_2_2_s11$p
```

```{r power mu poisson sigma parameters s11, include=FALSE}
m_fit_2_2_s11$p_par
```



```{r power mu poisson sigma fits, include=FALSE}
individual_fits_2_2 <- bind_rows(
  m_fit_2_2_s01$fit,
  m_fit_2_2_s02$fit,
  m_fit_2_2_s03$fit,
  m_fit_2_2_s04$fit,
  m_fit_2_2_s05$fit,
  m_fit_2_2_s06$fit,
  m_fit_2_2_s07$fit,
  m_fit_2_2_s08$fit,
  m_fit_2_2_s09$fit,
  m_fit_2_2_s10$fit,
  m_fit_2_2_s11$fit
)
```

```{r power mu poisson sigma predictions, include=FALSE}
individual_preds_2_2 <- bind_rows(
  m_fit_2_2_s01$pred,
  m_fit_2_2_s02$pred,
  m_fit_2_2_s03$pred,
  m_fit_2_2_s04$pred,
  m_fit_2_2_s05$pred,
  m_fit_2_2_s06$pred,
  m_fit_2_2_s07$pred,
  m_fit_2_2_s08$pred,
  m_fit_2_2_s09$pred,
  m_fit_2_2_s10$pred,
  m_fit_2_2_s11$pred
)
```


```{r power mu poisson sigma plot raw data, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_dat, aes(x = c, y = r_norm))+
    geom_line(data = individual_preds_2_2, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1.2)
```


```{r power mu poisson sigma plot mean, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = m_norm)) +
        # geom_line(data = m_pred_model_2_2, 
        #       aes(x = x, y = mu), color = "blue", alpha = .5) +
    geom_line(data = individual_preds_2_2, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1) 



```


```{r power mu poisson sigma sd, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
      # geom_line(data = m_pred_model_2_2,
      #       aes(x = x, y = sigma), color = "blue", alpha = .5) +
    geom_line(data = individual_preds_2_2,
            aes(x = x, y = sigma), color = "navajowhite3", linewidth = 1) +

  
  ylim(0, NA) 

```

```{r power mu poisson sigma delta, include=FALSE}
ggplot() +
  facet_wrap(vars(participant)) +
  #geom_line(data= d_delta, aes(x, delta_d)) +
  geom_line(data = individual_preds_2_2, 
            aes(x, delta_m), color = "aquamarine4", linewidth = 0.9) 
```

## Model 2_3: 
Power mu, super poisson sigma

$$
\sigma = \sqrt{\mu + (p_3 \mu)^2} + {p_4}
$$

#### s01 {.hidden}

```{r power mu super poisson sigma s01, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_3_s01 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s01", 
  power_fun_mu,
  super_poisson_sigma_power_mu,
  rep(.0000001, 4),
  c(250, 5, 0.1, 0.1))

m_fit_2_3_s01$p

```

```{r power mu super poisson sigma parameters s01, include=FALSE}
m_fit_2_3_s01$p_par
```


#### s02 {.hidden}

```{r power mu super poisson sigma s02, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_3_s02 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s02", 
  power_fun_mu,
  super_poisson_sigma_power_mu,
  # rep(.0000001, 4),
  # c(100000, 5, 10, 0.1))

  rep(.0000001, 4),
  c(152, 5, 2, 0.1)) #c(152, 5, 0.5, 0.1))

m_fit_2_3_s02$p
```


```{r power mu super poisson sigma parameters s02, include=FALSE}
m_fit_2_3_s02$p_par
```


#### s03 {.hidden}

```{r power mu super poisson sigma s03, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_3_s03 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s03", 
  power_fun_mu,
  super_poisson_sigma_power_mu,
  rep(.0000001, 4),
  c(500, 5, 0.1, 0.1))

m_fit_2_3_s03$p
```


```{r power mu super poisson sigma parameters s03, include=FALSE}
m_fit_2_3_s03$p_par
```

#### s04 {.hidden}

```{r power mu super poisson sigma s04, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_3_s04 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s04", 
  power_fun_mu,
  super_poisson_sigma_power_mu,
  rep(.0000001, 4),
  c(300, 5, 0.1, 0.1))

m_fit_2_3_s04$p
```


```{r power mu super poisson sigma parameters s04, include=FALSE}
m_fit_2_3_s04$p_par
```

#### s05 {.hidden}


```{r power mu super poisson sigma s05, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_3_s05 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s05", 
  power_fun_mu,
  super_poisson_sigma_power_mu,
  rep(.0000001, 4),
  c(500, 5, 0.1, 0.1))

m_fit_2_3_s05$p
```


```{r power mu super poisson sigma parameters s05, include=FALSE}
m_fit_2_3_s05$p_par
```

#### s06 {.hidden}

```{r power mu super poisson sigma s06, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_3_s06 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s06", 
  power_fun_mu,
  super_poisson_sigma_power_mu,
  rep(.0000001, 4),
  c(250, 5, 0.1, 0.1))

m_fit_2_3_s06$p
```

```{r power mu super poisson sigma parameters s06, include=FALSE}
m_fit_2_3_s06$p_par
```


#### s07 {.hidden}

```{r power mu super poisson sigma s07, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_3_s07 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s07", 
  power_fun_mu,
  super_poisson_sigma_power_mu,
  rep(.0000001, 4),
  c(250, 5, 0.1, 0.1))

m_fit_2_3_s07$p
```

```{r power mu super poisson sigma parameters s07, include=FALSE}
m_fit_2_3_s07$p_par
```


#### s08 {.hidden}

```{r power mu super poisson sigma s08, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_3_s08 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s08", 
  power_fun_mu,
  super_poisson_sigma_power_mu,
  rep(.0000001, 4),
  c(152, 5, 0.1, 0.1))

m_fit_2_3_s08$p
```

```{r power mu super poisson sigma parameters s08, include=FALSE}
m_fit_2_3_s08$p_par
```


#### s09 {.hidden}


```{r power mu super poisson sigma s09, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_3_s09 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s09", 
  power_fun_mu,
  super_poisson_sigma_power_mu,
  rep(.0000001, 4),
  c(250, 5, 5, 0.1))

m_fit_2_3_s09$p
```


```{r power mu super poisson sigma parameters s09, include=FALSE}
m_fit_2_3_s09$p_par
```

#### s10 {.hidden}


```{r power mu supper poisson sigma s10, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_3_s10 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s10",
  power_fun_mu,
  super_poisson_sigma_power_mu,
  rep(.0000001, 4),
  c(250, 5, 0.1, 0.1))

m_fit_2_3_s10$p
```

```{r power mu super poisson sigma parameters s10, include=FALSE}
m_fit_2_3_s10$p_par
```

#### s11 {.hidden}


```{r power mu super poisson sigma s11, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_3_s11 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s11", 
  power_fun_mu,
  super_poisson_sigma_power_mu,
  rep(.0000001, 4),
  c(250, 5, 0.1, 0.1))

m_fit_2_3_s11$p
```

```{r power mu super poisson sigma parameters s11, include=FALSE}
m_fit_2_3_s11$p_par
```



```{r power mu super poisson sigma fits, include=FALSE}
individual_fits_2_3 <- bind_rows(
  m_fit_2_3_s01$fit,
  m_fit_2_3_s02$fit,
  m_fit_2_3_s03$fit,
  m_fit_2_3_s04$fit,
  m_fit_2_3_s05$fit,
  m_fit_2_3_s06$fit,
  m_fit_2_3_s07$fit,
  m_fit_2_3_s08$fit,
  m_fit_2_3_s09$fit,
  m_fit_2_3_s10$fit,
  m_fit_2_3_s11$fit
)
```

```{r power mu super poisson sigma predictions, include=FALSE}
individual_preds_2_3 <- bind_rows(
  m_fit_2_3_s01$pred,
  m_fit_2_3_s02$pred,
  m_fit_2_3_s03$pred,
  m_fit_2_3_s04$pred,
  m_fit_2_3_s05$pred,
  m_fit_2_3_s06$pred,
  m_fit_2_3_s07$pred,
  m_fit_2_3_s08$pred,
  m_fit_2_3_s09$pred,
  m_fit_2_3_s10$pred,
  m_fit_2_3_s11$pred
)
```


```{r power mu super poisson sigma plot raw data, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_dat, aes(x = c, y = r_norm))+
    geom_line(data = individual_preds_2_3, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1.2)
```


```{r power mu super poisson sigma plot mean, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = m_norm)) +
        # geom_line(data = m_pred_model_2_3, 
        #       aes(x = x, y = mu), color = "blue", alpha = .5) +
    geom_line(data = individual_preds_2_3, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1) 



```


```{r power mu super poisson sigma sd, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
      # geom_line(data = m_pred_model_2_3,
      #       aes(x = x, y = sigma), color = "blue", alpha = .5) +
    geom_line(data = individual_preds_2_3,
            aes(x = x, y = sigma), color = "navajowhite3", linewidth = 1) +

  
  ylim(0, NA) 

```

```{r power mu super poisson sigma delta, include=FALSE}
ggplot() +
  facet_wrap(vars(participant)) +
  #geom_line(data= d_delta, aes(x, delta_d)) +
  geom_line(data = individual_preds_2_3, 
            aes(x, delta_m), color = "aquamarine4", linewidth = 0.9) 
```

## Model 2_4: 
Power mu, multiplicative sigma

$$
\sigma = p_3 \cdot \mu + {p_4}
$$

#### s01 {.hidden}
```{r power mu multiplicative sigma s01, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_4_s01 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s01", 
  power_fun_mu,
  mult_sigma_power_mu,
  rep(.0000001, 4),
  c(100, 2, 4, 8))

m_fit_2_4_s01$p

```

```{r power mu multiplicative sigma parameters s01, include=FALSE}
m_fit_2_4_s01$p_par
```

#### s02 {.hidden}

```{r power mu multiplicative sigma s02, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_4_s02 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s02", 
  power_fun_mu,
  mult_sigma_power_mu,
  c(0.0001, 0.0001, 0.0001, 0.00001),
  c(53, 50, 2, 8)) #c(53, 50, 2.5, 8))

m_fit_2_4_s02$p
```


```{r power mu multiplicative sigma s02 parameters, include=FALSE}
m_fit_2_4_s02$p_par
```

#### s03 {.hidden}


```{r power mu multiplicative sigma s03, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_4_s03 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s03", 
  power_fun_mu,
  mult_sigma_power_mu,
  rep(.0000001, 4),
  c(150, 50, 4, 8))

m_fit_2_4_s03$p
```


```{r power mu multiplicative sigma s03 parameters, include=FALSE}
m_fit_2_4_s03$p_par
```


#### s04 {.hidden}

```{r power mu multiplicative sigma s04, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_4_s04 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s04", 
  power_fun_mu,
  mult_sigma_power_mu,
  rep(.0000001, 4),
  c(100, 50, 4, 8))

m_fit_2_4_s04$p
```


```{r power mu multiplicative sigma s04 parameters, include=FALSE}
m_fit_2_4_s04$p_par
```

#### s05 {.hidden}


```{r power mu multiplicative sigma s05, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_4_s05 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s05", 
  power_fun_mu,
  mult_sigma_power_mu,
  rep(.0000001, 4),
  c(200, 50, 4, 8))

m_fit_2_4_s05$p
```


```{r power mu multiplicative sigma s05 parameters, include=FALSE}
m_fit_2_4_s05$p_par
```


#### s06 {.hidden}

```{r power mu multiplicative sigma s06, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_4_s06 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s06", 
  power_fun_mu,
  mult_sigma_power_mu,
  rep(.0000001, 4),
  c(100, 50, 4, 8))

m_fit_2_4_s06$p
```

```{r power mu multiplicative sigma s06 parameters, include=FALSE}
m_fit_2_4_s06$p_par
```

#### s07 {.hidden}

```{r power mu multiplicative sigma s07, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_4_s07 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s07", 
  power_fun_mu,
  mult_sigma_power_mu,
  rep(.0000001, 4),
  c(100, 50, 4, 8))

m_fit_2_4_s07$p
```

```{r power mu multiplicative sigma s07 parameters, include=FALSE}
m_fit_2_4_s07$p_par
```


#### s08 {.hidden}

```{r power mu multiplicative sigma s08, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_4_s08 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s08", 
  power_fun_mu,
  mult_sigma_power_mu,
  rep(.0000001, 4),
  c(53, 50, 4, 8))

m_fit_2_4_s08$p
```

```{r power mu multiplicative sigma s08 parameters, include=FALSE}
m_fit_2_4_s08$p_par
```


#### s09 {.hidden}

```{r power mu multiplicative sigma s09, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_4_s09 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s09", 
  power_fun_mu,
  mult_sigma_power_mu,
  rep(.0000001, 4),
  c(100, 50, 4, 8))

m_fit_2_4_s09$p
```


```{r power mu multiplicative sigma s09 parameters, include=FALSE}
m_fit_2_4_s09$p_par
```


#### s10 {.hidden}


```{r power mu multiplicative sigma s10, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_4_s10 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s10",
  power_fun_mu,
  mult_sigma_power_mu,
  rep(.0000001, 4),
  c(100, 50, 4, 8))

m_fit_2_4_s10$p
```

```{r power mu multiplicative sigma s10 parameters, include=FALSE}
m_fit_2_4_s10$p_par
```


#### s11 {.hidden}


```{r power mu multiplicative sigma s11, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_4_s11 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s11", 
  power_fun_mu,
  mult_sigma_power_mu,
  rep(.0000001, 4),
  c(100, 50, 4, 8))

m_fit_2_4_s11$p
```

```{r power mu multiplicative sigma s11 parameters, include=FALSE}
m_fit_2_4_s11$p_par
```



```{r power mu multiplicative sigma fits, include=FALSE}
individual_fits_2_4 <- bind_rows(
  m_fit_2_4_s01$fit,
  m_fit_2_4_s02$fit,
  m_fit_2_4_s03$fit,
  m_fit_2_4_s04$fit,
  m_fit_2_4_s05$fit,
  m_fit_2_4_s06$fit,
  m_fit_2_4_s07$fit,
  m_fit_2_4_s08$fit,
  m_fit_2_4_s09$fit,
  m_fit_2_4_s10$fit,
  m_fit_2_4_s11$fit
)
```

```{r power mu multiplicative sigma predictions, include=FALSE}
individual_preds_2_4 <- bind_rows(
  m_fit_2_4_s01$pred,
  m_fit_2_4_s02$pred,
  m_fit_2_4_s03$pred,
  m_fit_2_4_s04$pred,
  m_fit_2_4_s05$pred,
  m_fit_2_4_s06$pred,
  m_fit_2_4_s07$pred,
  m_fit_2_4_s08$pred,
  m_fit_2_4_s09$pred,
  m_fit_2_4_s10$pred,
  m_fit_2_4_s11$pred
)
```


```{r power mu multiplicative sigma plot raw data, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_dat, aes(x = c, y = r_norm))+
    geom_line(data = individual_preds_2_4, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1.2)
```


```{r power mu multiplicative sigma plot mean, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = individual_preds_2_4, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1) 



```


```{r power mu multiplicative sigma sd, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = individual_preds_2_4,
            aes(x = x, y = sigma), color = "navajowhite3", linewidth = 1) +

  
  ylim(0, NA) 

```

```{r power mu multiplicative sigma delta, include=FALSE}
ggplot() +
  facet_wrap(vars(participant)) +
  #geom_line(data= d_delta, aes(x, delta_d)) +
  geom_line(data = individual_preds_2_4, 
            aes(x, delta_m), color = "aquamarine4", linewidth = 0.9) 
```

## Model 2_5: 
Power mu, power sigma

$$
\sigma = p_3 \cdot (\mu)^{p_5} + {p_4}
$$

#### s01 {.hidden}

```{r power mu power sigma s01, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_5_s01 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s01", 
  power_fun_mu,
  power_sigma_power_mu,
  rep(.0000001, 5),
  c(250, 3, 1, .5, 3))

m_fit_2_5_s01$p

```

```{r power mu power sigma parameters s01, include=FALSE}
m_fit_2_5_s01$p_par
```


#### s02 {.hidden}

```{r power mu power sigma s02, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_5_s02 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s02", 
  power_fun_mu,
  power_sigma_power_mu,
  rep(.0000001, 5),
  c(68, 3, 2, .5, 3)) #c(68, 3, 5, .5, 3))

m_fit_2_5_s02$p
```


```{r power mu power sigma parameters s02, include=FALSE}
m_fit_2_5_s02$p_par
```


#### s03 {.hidden}

```{r power mu power sigma s03, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_5_s03 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s03", 
  power_fun_mu,
  power_sigma_power_mu,
  rep(.0000001, 5),
  c(68, 3, 1, .5, 3))

m_fit_2_5_s03$p
```


```{r power mu power sigma parameters s03, include=FALSE}
m_fit_2_5_s03$p_par
```



#### s04 {.hidden}

```{r power mu power sigma s04, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_5_s04 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s04", 
  power_fun_mu,
  power_sigma_power_mu,
  rep(.0000001, 5),
  c(250, 3, 1, .5, 3))

m_fit_2_5_s04$p
```


```{r power mu power sigma parameters s04, include=FALSE}
m_fit_2_5_s04$p_par
```

#### s05 {.hidden}


```{r power mu power sigma s05, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_5_s05 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s05", 
  power_fun_mu,
  power_sigma_power_mu,
  rep(.0000001, 5),
  c(250, 3, 1, .5, 3))

m_fit_2_5_s05$p
```


```{r power mu power sigma s05 parameters, include=FALSE}
m_fit_2_5_s05$p_par
```


#### s06 {.hidden}

```{r power mu power sigma s06, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_5_s06 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s06", 
  power_fun_mu,
  power_sigma_power_mu,
  rep(.0000001, 5),
  c(250, 3, 1, .5, 3))

m_fit_2_5_s06$p
```

```{r power mu power sigma s06 parameters, include=FALSE}
m_fit_2_5_s06$p_par
```

#### s07 {.hidden}

```{r power mu power sigma s07, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_5_s07 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s07", 
  power_fun_mu,
  power_sigma_power_mu,
  rep(.0000001, 5),
  c(250, 3, 1, .5, 3))

m_fit_2_5_s07$p
```

```{r power mu power sigma s07 parameters, include=FALSE}
m_fit_2_5_s07$p_par
```

#### s08 {.hidden}

```{r power mu power sigma s08, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_5_s08 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s08", 
  power_fun_mu,
  power_sigma_power_mu,
  rep(.0000001, 5),
  c(250, 3, 1, .5, 3))

m_fit_2_5_s08$p
```

```{r power mu power sigma s08 parameters, include=FALSE}
m_fit_2_5_s08$p_par
```


#### s09 {.hidden}


```{r power mu power sigma s09, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_5_s09 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s09", 
  power_fun_mu,
  power_sigma_power_mu,
  rep(.0000001, 5),
  c(250, 3, 3, .5, 3))

m_fit_2_5_s09$p
```


```{r power mu power sigma s09 parameters, include=FALSE}
m_fit_2_5_s09$p_par
```

#### s10 {.hidden}

```{r power mu power sigma s10, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_5_s10 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s10",
  power_fun_mu,
  power_sigma_power_mu,
  rep(.0000001, 5),
  c(250, 3, 1, .5, 3))

m_fit_2_5_s10$p
```

```{r power mu power sigma s10 parameters, include=FALSE}
m_fit_2_5_s10$p_par
```



#### s11 {.hidden}


```{r power mu power sigma s11, fig.width=15, fig.height=4, include=FALSE}
m_fit_2_5_s11 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s11", 
  power_fun_mu,
  power_sigma_power_mu,
  rep(.0000001, 5),
  c(250, 3, 1, .5, 3))

m_fit_2_5_s11$p
```

```{r power mu power sigma s11 parameters, include=FALSE}
m_fit_2_5_s11$p_par
```



```{r power mu power sigma fits, include=FALSE}
individual_fits_2_5 <- bind_rows(
  m_fit_2_5_s01$fit,
  m_fit_2_5_s02$fit,
  m_fit_2_5_s03$fit,
  m_fit_2_5_s04$fit,
  m_fit_2_5_s05$fit,
  m_fit_2_5_s06$fit,
  m_fit_2_5_s07$fit,
  m_fit_2_5_s08$fit,
  m_fit_2_5_s09$fit,
  m_fit_2_5_s10$fit,
  m_fit_2_5_s11$fit
)
```

```{r power mu power sigma predictions, include=FALSE}
individual_preds_2_5 <- bind_rows(
  m_fit_2_5_s01$pred,
  m_fit_2_5_s02$pred,
  m_fit_2_5_s03$pred,
  m_fit_2_5_s04$pred,
  m_fit_2_5_s05$pred,
  m_fit_2_5_s06$pred,
  m_fit_2_5_s07$pred,
  m_fit_2_5_s08$pred,
  m_fit_2_5_s09$pred,
  m_fit_2_5_s10$pred,
  m_fit_2_5_s11$pred
)
```


```{r power mu power sigma plot raw data, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_dat, aes(x = c, y = r_norm))+
    geom_line(data = individual_preds_2_5, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1.2)
```


```{r power mu power sigma plot mean, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = individual_preds_2_5, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1) 


```


```{r power mu power sigma sd, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = individual_preds_2_5,
            aes(x = x, y = sigma), color = "navajowhite3", linewidth = 1) +

  
  ylim(0, NA) 

```

```{r power mu power sigma delta, include=FALSE}
ggplot() +
  facet_wrap(vars(participant)) +
  geom_line(data = individual_preds_2_5, 
            aes(x, delta_m), color = "aquamarine4", linewidth = 0.9) 
```

### MODELS:

```{r linear mu all models model 2 fits, include=FALSE}
individual_fits_2 <- bind_rows(
  individual_fits_2_1 |>  mutate(model = "2_1"),
  individual_fits_2_2 |>  mutate(model = "2_2"),
  individual_fits_2_3 |>  mutate(model = "2_3"),
  individual_fits_2_4 |>  mutate(model = "2_4"),
  individual_fits_2_5 |>  mutate(model = "2_5"))
  
```

```{r linealr mu all models model 2 predictions, include=FALSE}
individual_preds_2 <- bind_rows(
  individual_preds_2_1 |>  mutate(model = "2_1"),
  individual_preds_2_2 |>  mutate(model = "2_2"),
  individual_preds_2_3 |>  mutate(model = "2_3"),
  individual_preds_2_4 |>  mutate(model = "2_4"),
  individual_preds_2_5 |>  mutate(model = "2_5"))
```


### Plot models and raw data
```{r linear mu all models model 2 plot raw data, echo=FALSE}
ggplotly(ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_dat, aes(x = c, y = r_norm), alpha = .3) +
    geom_line(data = individual_preds_2, 
              aes(x = x, y = mu, color = model)))
```


### Plot models and mean 
```{r linear mu all models model 2 plot mean, echo=FALSE}
ggplotly(ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = m_norm), alpha = .3) +
    geom_line(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = individual_preds_2, 
              aes(x = x, y = mu, color = model)))
```


### Plot models and standard deviation 
```{r linear mu all models model 1 sd, echo=FALSE}
ggplotly(ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = sta_dev_norm), alpha = .3) +
    geom_line(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = individual_preds_2, 
              aes(x = x, y = sigma, color = model)))
```


### Plot models and delta
```{r linear mu all models model 2 delta, echo=FALSE}
ggplotly(ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_line(data = individual_preds_2, 
              aes(x = x, y = delta_m, color = model)))
```


```{r}
individual_fits_2 |> select(par, model) |> unnest(par) |> 
  filter(!participant %in% c("s02", "s08")) |>
  filter(parn=="p1") |> 
  group_by(model) |> 
  summarise(mean_p1 = mean(par))
```

