---
title: "Linear Models"
format: html
editor: source
---


Linear Mu:
$$
\Large \mu = x*{p_1}
$$

## Model 1_1: 
Linear mu and constant sigma

$$
\sigma = {p_2} 
$$

#### s01 {.hidden}

```{r linear mu constant noise s01, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_1_s01 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s01", 
  linear_fun_mu,
  constant_sigma_lineal_mu,
  c(20,  .1), 
  c(35, 20))

m_fit_1_1_s01$p
```


```{r linear mu constant noise parameters s01, include=FALSE}
m_fit_1_1_s01$p_par
```



#### s02 {.hidden}

```{r linear mu constant sigma s02, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_1_s02 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s02", 
  linear_fun_mu,
  constant_sigma_lineal_mu,
  c(20, .1), 
  c(35, 20))

m_fit_1_1_s02$p
```


```{r linear mu and constant sigma s02 parameters, include=FALSE}
m_fit_1_1_s02$p_par
```



#### s03 {.hidden}


```{r lineal mu constant sigma s03, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_1_s03 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s03", 
  linear_fun_mu,
  constant_sigma_lineal_mu,
  c(20, .1), 
  c(35,  20))

m_fit_1_1_s03$p
```


```{r lineal mu constant sigma s03 parameters, include=FALSE}
m_fit_1_1_s03$p_par
```





#### s04 {.hidden}

```{r lineal mu constant sigma s04, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_1_s04 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s04", 
  linear_fun_mu,
  constant_sigma_lineal_mu,
  c(20, .1), 
  c(35, 20))

m_fit_1_1_s04$p
```


```{r linear mu constant sigma s04 parameters, include=FALSE}
m_fit_1_1_s04$p_par
```



#### s05 {.hidden}

```{r linear mu constant sigma s05, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_1_s05 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s05", 
  linear_fun_mu,
  constant_sigma_lineal_mu,
  c(20, .1), 
  c(35,  20))

m_fit_1_1_s05$p
```


```{r linear mu constant sigma s05 parameters, include=FALSE}
m_fit_1_1_s05$p_par
```


#### s06 {.hidden}

```{r linear mu constant sigma s06, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_1_s06 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s06", 
  linear_fun_mu,
  constant_sigma_lineal_mu,
  c(20, .1), 
  c(35,  20))

m_fit_1_1_s06$p
```

```{r linear mu constant sigma s06 parameters, include=FALSE}
m_fit_1_1_s06$p_par
```



#### s07 {.hidden}

```{r linear mu sigma constant s07, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_1_s07 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s07", 
  linear_fun_mu,
  constant_sigma_lineal_mu,
  c(20,  .1), 
  c(35, 20))

m_fit_1_1_s07$p
```

```{r linear mu constant sigma s07 parameters, include=FALSE}
m_fit_1_1_s07$p_par
```



#### s08 {.hidden}

```{r linear mu sigma constant s08, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_1_s08 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s08", 
  linear_fun_mu,
  constant_sigma_lineal_mu,
  c(20, .1), 
  c(35, 20))

m_fit_1_1_s08$p
```

```{r linear mu constant sigma s08 parameters, include=FALSE}
m_fit_1_1_s08$p_par
```


#### s09 {.hidden}


```{r linear mu constant sigma s09, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_1_s09 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s09", 
  linear_fun_mu,
  constant_sigma_lineal_mu,
  c(5,  .1), 
  c(35, 50))

m_fit_1_1_s09$p
```


```{r linear mu constant sigma s09 parameters, include=FALSE}
m_fit_1_1_s09$p_par
```





#### s10 {.hidden}


```{r linear mu constant sigma s10, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_1_s10 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s10", 
  linear_fun_mu,
  constant_sigma_lineal_mu,
  c(20, .1), 
  c(35, 20))

m_fit_1_1_s10$p
```

```{r linear mu constant sigma s10 parameters, include=FALSE}
m_fit_1_1_s10$p_par
```



#### s11 {.hidden}

```{r linear mu constant sigma, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_1_s11 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s11", 
  linear_fun_mu,
  constant_sigma_lineal_mu,
  c(20, .1), 
  c(35, 20))

m_fit_1_1_s11$p
```

```{r linear mu constant sigma s11 parameters, include=FALSE}
m_fit_1_1_s11$p_par
```



```{r linear mu constant sigma fits, include=FALSE}
individual_fits_1_1 <- bind_rows(
  m_fit_1_1_s01$fit,
  m_fit_1_1_s02$fit,
  m_fit_1_1_s03$fit,
  m_fit_1_1_s04$fit,
  m_fit_1_1_s05$fit,
  m_fit_1_1_s06$fit,
  m_fit_1_1_s07$fit,
  m_fit_1_1_s08$fit,
  m_fit_1_1_s09$fit,
  m_fit_1_1_s10$fit,
  m_fit_1_1_s11$fit
)
```

```{r linear mu constant sigma predictions, include=FALSE}
individual_preds_1_1 <- bind_rows(
  m_fit_1_1_s01$pred,
  m_fit_1_1_s02$pred,
  m_fit_1_1_s03$pred,
  m_fit_1_1_s04$pred,
  m_fit_1_1_s05$pred,
  m_fit_1_1_s06$pred,
  m_fit_1_1_s07$pred,
  m_fit_1_1_s08$pred,
  m_fit_1_1_s09$pred,
  m_fit_1_1_s10$pred,
  m_fit_1_1_s11$pred
)
```


```{r linear mu constant sigma plot raw data, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_dat, aes(x = c, y = r_norm))+
    geom_line(data = individual_preds_1_1, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1.2)
```


```{r linear mu constant sigma plot mean, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = individual_preds_1_1, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1) 



```


```{r linear mu constant sigma sd, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = individual_preds_1_1,
            aes(x = x, y = sigma), color = "navajowhite3", linewidth = 1) +

  
  ylim(0, NA) 

```

```{r linear mu constant sigma delta, include=FALSE}
ggplot() +
  facet_wrap(vars(participant)) +
  geom_line(data = individual_preds_1_1, 
            aes(x, delta_m), color = "aquamarine4", linewidth = 0.9) 
```


## Model 1_2: 
Linear mu, poisson sigma


$$
\sigma = \sqrt{\mu} + p_2
$$

#### s01 {.hidden}

```{r linear mu poisson sigma s01, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_2_s01 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s01", 
  linear_fun_mu,
  poisson_sigma_lineal_mu,
  c(10,.0000001), 
  c(30, .1))

m_fit_1_2_s01$p
```


```{r linear mu poisson sigma s01 parameters, include=FALSE}
m_fit_1_2_s01$p_par
```



#### s02 {.hidden}

```{r linear mu poisson sigma s02, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_2_s02 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s02", 
  linear_fun_mu,
  poisson_sigma_lineal_mu,
  c(10,.0000001), 
  c(500, .1))

m_fit_1_2_s02$p
```


```{r linear mu poisson sigma s02 parameters, include=FALSE}
m_fit_1_2_s02$p_par
```



#### s03 {.hidden}


```{r linear mu poisson sigma s03, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_2_s03 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s03", 
  linear_fun_mu,
  poisson_sigma_lineal_mu,
  c(10,.0000001), 
  c(30, .1))

m_fit_1_2_s03$p
```


```{r linear mu poisson sigma s03 parameters, include=FALSE}
m_fit_1_2_s03$p_par
```



#### s04 {.hidden}

```{r linear mu poisson sigma s04, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_2_s04 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s04", 
  linear_fun_mu,
  poisson_sigma_lineal_mu,
  c(10,.0000001), 
  c(30, .1))

m_fit_1_2_s04$p
```


```{r linear mu poisson sigma s04 parameters, include=FALSE}
m_fit_1_2_s04$p_par
```



#### s05 {.hidden}


```{r linear mu poisson sigma s05, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_2_s05 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s05", 
  linear_fun_mu,
  poisson_sigma_lineal_mu,
  c(10,.0000001), 
  c(30, .1))

m_fit_1_2_s05$p
```


```{r linear mu poisson sigma s05 parameters, include=FALSE}
m_fit_1_2_s05$p_par
```


#### s06 {.hidden}

```{r linear mu sigma poisson s06, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_2_s06 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s06", 
  linear_fun_mu,
  poisson_sigma_lineal_mu,
  c(10,.0000001), 
  c(30, .1))

m_fit_1_2_s06$p
```

```{r linear mu poisson sigma s06 parameters, include=FALSE}
m_fit_1_2_s06$p_par
```



#### s07 {.hidden}

```{r linear mu poisson sigma s07, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_2_s07 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s07", 
  linear_fun_mu,
  poisson_sigma_lineal_mu,
  c(10,.0000001), 
  c(30, .1))

m_fit_1_2_s07$p
```

```{r linear mu poisson sigma s07 parameters, include=FALSE}
m_fit_1_2_s07$p_par
```



#### s08 {.hidden}

```{r linear mu poisson sigma, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_2_s08 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s08", 
  linear_fun_mu,
  poisson_sigma_lineal_mu,
  c(10,.0000001), 
  c(30, .1))

m_fit_1_2_s08$p
```

```{r linear mu poisson sigma s08 parameters, include=FALSE}
m_fit_1_2_s08$p_par
```


#### s09 {.hidden}


```{r linear mu poisson sigma s09, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_2_s09 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s09", 
  linear_fun_mu,
  poisson_sigma_lineal_mu,
  c(10,.0000001), 
  c(60, 1))

m_fit_1_2_s09$p
```


```{r linear mu poisson sigma s09 parameters, include=FALSE}
m_fit_1_2_s09$p_par
```


#### s10 {.hidden}

```{r linear mu poisson sigma s10, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_2_s10 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s10", 
  linear_fun_mu,
  poisson_sigma_lineal_mu,
  c(10,.0000001), 
  c(30, .1))

m_fit_1_2_s10$p
```

```{r linear mu poisson sigma s10 parameters, include=FALSE}
m_fit_1_2_s10$p_par
```



#### s11 {.hidden}


```{r linear mu poisson sigma s11, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_2_s11 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s11", 
  linear_fun_mu,
  poisson_sigma_lineal_mu,
  c(10,.0000001), 
  c(30, .1))

m_fit_1_2_s11$p
```

```{r linear mu poisson sigma s11 parameters, include=FALSE}
m_fit_1_2_s11$p_par
```



```{r linear mu poisson sigma fits, include=FALSE}
individual_fits_1_2 <- bind_rows(
  m_fit_1_2_s01$fit,
  m_fit_1_2_s02$fit,
  m_fit_1_2_s03$fit,
  m_fit_1_2_s04$fit,
  m_fit_1_2_s05$fit,
  m_fit_1_2_s06$fit,
  m_fit_1_2_s07$fit,
  m_fit_1_2_s08$fit,
  m_fit_1_2_s09$fit,
  m_fit_1_2_s10$fit,
  m_fit_1_2_s11$fit
)
```

```{r linear mu poisson sigma predictions, include=FALSE}
individual_preds_1_2 <- bind_rows(
  m_fit_1_2_s01$pred,
  m_fit_1_2_s02$pred,
  m_fit_1_2_s03$pred,
  m_fit_1_2_s04$pred,
  m_fit_1_2_s05$pred,
  m_fit_1_2_s06$pred,
  m_fit_1_2_s07$pred,
  m_fit_1_2_s08$pred,
  m_fit_1_2_s09$pred,
  m_fit_1_2_s10$pred,
  m_fit_1_2_s11$pred
)
```


```{r linear mu poisson sigma plot raw data, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_dat, aes(x = c, y = r_norm))+
    geom_line(data = individual_preds_1_2, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1.2)
```


```{r linear mu poisson sigma plot mean, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = m_norm)) +
        ## geom_line(data = m_pred_model_1_2, 
        ##       aes(x = x, y = mu), color = "blue", alpha = .5) +
    geom_line(data = individual_preds_1_2, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1) 



```


```{r linear mu poisson sigma sd, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
      ## geom_line(data = m_pred_model_1_2,
      ##       aes(x = x, y = sigma), color = "blue", alpha = .5) +
    geom_line(data = individual_preds_1_2,
            aes(x = x, y = sigma), color = "navajowhite3", linewidth = 1) +

  
  ylim(0, NA) 

```

```{r linear mu poisson sigma delta, include=FALSE}
ggplot() +
  facet_wrap(vars(participant)) +
  ## geom_line(data= d_delta, aes(x, delta_d)) +
  geom_line(data = individual_preds_1_2, 
            aes(x, delta_m), color = "aquamarine4", linewidth = 0.9) 
```


## Model 1_3: 
Linear mu, super poisson sigma

$$
\sigma = \sqrt{\mu + (p_2 \mu)^2} + p_3
$$

#### s01 {.hidden}
```{r linear mu super poisson sigma s01, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_3_s01 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s01", 
  linear_fun_mu,
  super_poisson_sigma_lineal_mu,
  c(.0000001,.0000001,.0000001),
  c(30, .025, .25))

m_fit_1_3_s01$p

```

```{r linear mu super poisson sigma s01 parameters, include=FALSE}
m_fit_1_3_s01$p_par
```


#### s02 {.hidden}

<!-- Nada bien, bajar p2 a 0.3, pero llega a bounds -->

```{r linear mu super poisson sigma s02, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_3_s02 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s02", 
  linear_fun_mu,
  super_poisson_sigma_lineal_mu,
  c(.0000001,.0000001,.0000001),
  c(30, 2, .25))

m_fit_1_3_s02$p
```


```{r linear mu super poisson sigma s02 parameters, include=FALSE}
m_fit_1_3_s02$p_par
```



#### s03 {.hidden}


```{r linear mu super poisson sigma s03, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_3_s03 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s03", 
  linear_fun_mu,
  super_poisson_sigma_lineal_mu,
  c(.0000001,.0000001,.0000001),
  c(30, .025, .25))

m_fit_1_3_s03$p
```


```{r linear mu super poisson sigma s03 parameters, include=FALSE}
m_fit_1_3_s03$p_par
```



#### s04 {.hidden}

```{r linear mu super poisson sigma s04, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_3_s04 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s04", 
  linear_fun_mu,
  super_poisson_sigma_lineal_mu,
  c(.0000001,.0000001,.0000001),
  c(30, .025, .25))

m_fit_1_3_s04$p
```


```{r linear mu super poisson sigma s04 parameters, include=FALSE}
m_fit_1_3_s04$p_par
```



#### s05 {.hidden}

```{r linear mu super poisson sigma s05, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_3_s05 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s05", 
  linear_fun_mu,
  super_poisson_sigma_lineal_mu,
  c(.0000001,.0000001,.0000001),
  c(30, .025, .25))

m_fit_1_3_s05$p
```


```{r linear mu super poisson sigma s05 parameters, include=FALSE}
m_fit_1_3_s05$p_par
```


#### s06 {.hidden}

```{r linear mu super poisson sigma s06, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_3_s06 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s06", 
  linear_fun_mu,
  super_poisson_sigma_lineal_mu,
  c(.0000001,.0000001,.0000001),
  c(30, .025, .25))

m_fit_1_3_s06$p
```

```{r linear mu super poisson sigma s06 parameters, include=FALSE}
m_fit_1_3_s06$p_par
```



#### s07 {.hidden}

```{r linear mu super poisson sigma s07, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_3_s07 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s07", 
  linear_fun_mu,
  super_poisson_sigma_lineal_mu,
  c(.0000001,.0000001,.0000001),
  c(30, .025, .25))

m_fit_1_3_s07$p
```

```{r linear mu super poisson sigma s07 parameters, include=FALSE}
m_fit_1_3_s07$p_par
```



#### s08 {.hidden}

```{r linear mu super poisson sigma s08, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_3_s08 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s08", 
  linear_fun_mu,
  super_poisson_sigma_lineal_mu,
  c(.0000001,.0000001,.0000001),
  c(30, .025, .25))

m_fit_1_3_s08$p
```

```{r linear mu super poisson sigma s08 parameters, include=FALSE}
m_fit_1_3_s08$p_par
```


#### s09 {.hidden}


```{r linear mu super poisson sigma s09, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_3_s09 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s09", 
  linear_fun_mu,
  super_poisson_sigma_lineal_mu,
  c(.0000001,.0000001,.0000001),
  c(60, 2, 3))

m_fit_1_3_s09$p
```


```{r linear mu super poisson sigma s09 parameters, include=FALSE}
m_fit_1_3_s09$p_par
```



#### s10 {.hidden}


```{r linear mu supper poisson sigma s10, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_3_s10 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s10",
  linear_fun_mu,
  super_poisson_sigma_lineal_mu,
  c(.0000001,.0000001,.0000001),
  c(30, .025, .25))

m_fit_1_3_s10$p
```

```{r linear mu super poisson sigma s10 parameters, include=FALSE}
m_fit_1_3_s10$p_par
```



#### s11 {.hidden}


```{r linear mu super poisson sigma s11, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_3_s11 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s11", 
  linear_fun_mu,
  super_poisson_sigma_lineal_mu,
  c(.0000001,.0000001,.0000001),
  c(30, .025, .25))

m_fit_1_3_s11$p
```

```{r linear mu super poisson sigma s11 parameters, include=FALSE}
m_fit_1_3_s11$p_par
```



```{r linear mu super poisson sigma fits, include=FALSE}
individual_fits_1_3 <- bind_rows(
  m_fit_1_3_s01$fit,
  m_fit_1_3_s02$fit,
  m_fit_1_3_s03$fit,
  m_fit_1_3_s04$fit,
  m_fit_1_3_s05$fit,
  m_fit_1_3_s06$fit,
  m_fit_1_3_s07$fit,
  m_fit_1_3_s08$fit,
  m_fit_1_3_s09$fit,
  m_fit_1_3_s10$fit,
  m_fit_1_3_s11$fit
)
```

```{r linear mu super poisson sigma predictions, include=FALSE}
individual_preds_1_3 <- bind_rows(
  m_fit_1_3_s01$pred,
  m_fit_1_3_s02$pred,
  m_fit_1_3_s03$pred,
  m_fit_1_3_s04$pred,
  m_fit_1_3_s05$pred,
  m_fit_1_3_s06$pred,
  m_fit_1_3_s07$pred,
  m_fit_1_3_s08$pred,
  m_fit_1_3_s09$pred,
  m_fit_1_3_s10$pred,
  m_fit_1_3_s11$pred
)
```


```{r linear mu super poisson sigma plot raw data, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_dat, aes(x = c, y = r_norm))+
    geom_line(data = individual_preds_1_3, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1.2)
```


```{r linear mu super poisson sigma plot mean, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = individual_preds_1_3, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1) 



```


```{r linear mu super poisson sigma sd, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = individual_preds_1_3,
            aes(x = x, y = sigma), color = "navajowhite3", linewidth = 1) +

  
  ylim(0, NA) 

```

```{r linear mu super poisson sigma delta, include=FALSE}
ggplot() +
  facet_wrap(vars(participant)) +
  geom_line(data = individual_preds_1_3, 
            aes(x, delta_m), color = "aquamarine4", linewidth = 0.9) 
```

## Model 1_4: 
Linear mu, multiplicative sigma

$$
\sigma = p_2 \cdot \mu + {p_3}
$$

#### s01 {.hidden}
```{r linear mu multiplicative sigma s01, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_4_s01 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s01", 
  linear_fun_mu,
  mult_sigma_lineal_mu,
  rep(.0000001, 3),
  c(35, 5, .3))

m_fit_1_4_s01$p

```

```{r linear mu multiplicative sigma s01 parameters, include=FALSE}
m_fit_1_4_s01$p_par
```


#### s02 {.hidden}

```{r linear mu multiplicative sigma s02, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_4_s02 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s02", 
  linear_fun_mu,
  mult_sigma_lineal_mu,
  rep(.0000001, 3),
  c(35, 5, .3))

m_fit_1_4_s02$p
```


```{r linear mu multiplicative sigma s02 parameters, include=FALSE}
m_fit_1_4_s02$p_par
```



#### s03 {.hidden}

```{r linear mu multiplicative sigma s03, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_4_s03 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s03", 
  linear_fun_mu,
  mult_sigma_lineal_mu,
  rep(.0000001, 3),
  c(35, 5, .3))

m_fit_1_4_s03$p
```


```{r linear mu multiplicative sigma s03 parameters, include=FALSE}
m_fit_1_4_s03$p_par
```


#### s04 {.hidden}

```{r linear mu multiplicative sigma s04, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_4_s04 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s04", 
  linear_fun_mu,
  mult_sigma_lineal_mu,
  rep(.0000001, 3),
  c(35, 5, .3))

m_fit_1_4_s04$p
```


```{r linear mu multiplicative sigma s04 parameters, include=FALSE}
m_fit_1_4_s04$p_par
```



#### s05 {.hidden}


```{r linear mu multiplicative sigma s05, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_4_s05 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s05", 
  linear_fun_mu,
  mult_sigma_lineal_mu,
  rep(.0000001, 3),
  c(35, 5, .3))

m_fit_1_4_s05$p
```


```{r linear mu multiplicative sigma s05 parameters, include=FALSE}
m_fit_1_4_s05$p_par
```


#### s06 {.hidden}

```{r linear mu multiplicative sigma s06, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_4_s06 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s06", 
  linear_fun_mu,
  mult_sigma_lineal_mu,
  rep(.0000001, 3),
  c(35, 5, .3))

m_fit_1_4_s06$p
```

```{r linear mu multiplicative sigma s06 parameters, include=FALSE}
m_fit_1_4_s06$p_par
```



#### s07 {.hidden}

```{r linear mu multiplicative sigma s07, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_4_s07 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s07", 
  linear_fun_mu,
  mult_sigma_lineal_mu,
  rep(.0000001, 3),
  c(35, 5, .3))

m_fit_1_4_s07$p
```

```{r linear mu multiplicative sigma s07 parameters, include=FALSE}
m_fit_1_4_s07$p_par
```



#### s08 {.hidden}

```{r linear mu multiplicative sigma s08, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_4_s08 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s08", 
  linear_fun_mu,
  mult_sigma_lineal_mu,
  rep(.0000001, 3),
  c(35, 5, .3))

m_fit_1_4_s08$p
```

```{r linear mu multiplicative sigma s08 parameters, include=FALSE}
m_fit_1_4_s08$p_par
```


#### s09 {.hidden}


```{r linear mu multiplicative sigma s09, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_4_s09 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s09", 
  linear_fun_mu,
  mult_sigma_lineal_mu,
  rep(.0000001, 3),
  c(35, 5, .3))

m_fit_1_4_s09$p
```


```{r linear mu multiplicative sigma s09 parameters, include=FALSE}
m_fit_1_4_s09$p_par
```


#### s10 {.hidden}


```{r linear mu multiplicative sigma s10, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_4_s10 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s10",
  linear_fun_mu,
  mult_sigma_lineal_mu,
  rep(.0000001, 3),
  c(35, 5, .3))

m_fit_1_4_s10$p
```

```{r linear mu multiplicative sigma s10 parameters, include=FALSE}
m_fit_1_4_s10$p_par
```



#### s11 {.hidden}


```{r linear mu multiplicative sigma s11, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_4_s11 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s11", 
  linear_fun_mu,
  mult_sigma_lineal_mu,
  rep(.0000001, 3),
  c(35, 5, .3))

m_fit_1_4_s11$p
```

```{r linear mu multiplicative sigma s11 parameters, include=FALSE}
m_fit_1_4_s11$p_par
```



```{r linear mu multiplicative sigma fits, include=FALSE}
individual_fits_1_4 <- bind_rows(
  m_fit_1_4_s01$fit,
  m_fit_1_4_s02$fit,
  m_fit_1_4_s03$fit,
  m_fit_1_4_s04$fit,
  m_fit_1_4_s05$fit,
  m_fit_1_4_s06$fit,
  m_fit_1_4_s07$fit,
  m_fit_1_4_s08$fit,
  m_fit_1_4_s09$fit,
  m_fit_1_4_s10$fit,
  m_fit_1_4_s11$fit
)
```

```{r linear mu multiplicative sigma predictions, include=FALSE}
individual_preds_1_4 <- bind_rows(
  m_fit_1_4_s01$pred,
  m_fit_1_4_s02$pred,
  m_fit_1_4_s03$pred,
  m_fit_1_4_s04$pred,
  m_fit_1_4_s05$pred,
  m_fit_1_4_s06$pred,
  m_fit_1_4_s07$pred,
  m_fit_1_4_s08$pred,
  m_fit_1_4_s09$pred,
  m_fit_1_4_s10$pred,
  m_fit_1_4_s11$pred
)
```


```{r linear mu multiplicative sigma plot raw data, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_dat, aes(x = c, y = r_norm))+
    geom_line(data = individual_preds_1_4, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1.2)
```


```{r linear mu multiplicative sigma plot mean, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = individual_preds_1_4, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1) 

```


```{r linear mu multiplicative sigma sd, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = individual_preds_1_4,
            aes(x = x, y = sigma), color = "navajowhite3", linewidth = 1) +

  
  ylim(0, NA) 

```

```{r linear mu multiplicative sigma delta, include=FALSE}
ggplot() +
  facet_wrap(vars(participant)) +
  geom_line(data = individual_preds_1_4, 
            aes(x, delta_m), color = "aquamarine4", linewidth = 0.9) 
```

## Model 1_5: 
Linear mu, power sigma


$$
\sigma = p_2 \cdot (\mu)^{p_4} + {p_3}
$$

#### s01 {.hidden}
```{r linear mu power sigma s01, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_5_s01 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s01", 
  linear_fun_mu,
  power_sigma_lineal_mu,
  rep(.0000001, 4),
  c(30, 3, .1, 1))

m_fit_1_5_s01$p

```

```{r linear mu power sigma s01 parameters, include=FALSE}
m_fit_1_5_s01$p_par
```


#### s02 {.hidden}

<!-- Se va demasiado p2 -->

```{r linear mu power sigma s02, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_5_s02 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s02", 
  linear_fun_mu,
  power_sigma_lineal_mu,
  rep(.0000001, 4),
  c(30, 2, .1, 2))

m_fit_1_5_s02$p
```


```{r linear mu power sigma s02 parameters, include=FALSE}
m_fit_1_5_s02$p_par
```



#### s03 {.hidden}


```{r linear mu power sigma s03, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_5_s03 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s03", 
  linear_fun_mu,
  power_sigma_lineal_mu,
  rep(.0000001, 4),
  c(30, 3, .1, 1))

m_fit_1_5_s03$p
```


```{r linear mu power sigma s03 parameters, include=FALSE}
m_fit_1_5_s03$p_par
```



#### s04 {.hidden}

```{r linear mu power sigma s04, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_5_s04 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s04", 
  linear_fun_mu,
  power_sigma_lineal_mu,
  rep(.0000001, 4),
  c(30, 3, .1, 1))

m_fit_1_5_s04$p
```


```{r linear mu power sigma s04 parameters, include=FALSE}
m_fit_1_5_s04$p_par
```



#### s05 {.hidden}


```{r linear mu power sigma s05, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_5_s05 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s05", 
  linear_fun_mu,
  power_sigma_lineal_mu,
  rep(.0000001, 4),
  c(30, 3, .1, 1))

m_fit_1_5_s05$p
```


```{r linear mu power sigma s05 parameters, include=FALSE}
m_fit_1_5_s05$p_par
```


#### s06 {.hidden}

```{r linear mu power sigma s06, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_5_s06 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s06", 
  linear_fun_mu,
  power_sigma_lineal_mu,
  rep(.0000001, 4),
  c(30, 3, .1, 1))

m_fit_1_5_s06$p
```

```{r linear mu power sigma s06 parameters, include=FALSE}
m_fit_1_5_s06$p_par
```



#### s07 {.hidden}

```{r linear mu power sigma s07, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_5_s07 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s07", 
  linear_fun_mu,
  power_sigma_lineal_mu,
  rep(.0000001, 4),
  c(30, 3, .1, 1))

m_fit_1_5_s07$p
```

```{r linear mu power sigma s07 parameters, include=FALSE}
m_fit_1_5_s07$p_par
```



#### s08 {.hidden}

Se va demasiado

```{r linear mu power sigma s08, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_5_s08 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s08", 
  linear_fun_mu,
  power_sigma_lineal_mu,
  rep(.0000001, 4),
  c(30, 2, .1, 10))

m_fit_1_5_s08$p
```

```{r linear mu power sigma s08 parameters, include=FALSE}
m_fit_1_5_s08$p_par
```


#### s09 {.hidden}


```{r linear mu power sigma s09, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_5_s09 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s09", 
  linear_fun_mu,
  power_sigma_lineal_mu,
  rep(.0000001, 4),
  c(30, 3, .1, 2))

m_fit_1_5_s09$p
```


```{r linear mu power sigma s09 parameters, include=FALSE}
m_fit_1_5_s09$p_par
```


#### s10 {.hidden}

```{r linear mu power sigma s10, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_5_s10 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s10",
  linear_fun_mu,
  power_sigma_lineal_mu,
  rep(.0000001, 4),
  c(30, 3, .1, 1))

m_fit_1_5_s10$p
```

```{r linear mu power sigma s10 parameters, include=FALSE}
m_fit_1_5_s10$p_par
```



#### s11 {.hidden}

```{r linear mu power sigma s11, fig.width=15, fig.height=4, include=FALSE}
m_fit_1_5_s11 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s11", 
  linear_fun_mu,
  power_sigma_lineal_mu,
  rep(.0000001, 4),
  c(30, 3, .1, 1))

m_fit_1_5_s11$p
```

```{r linear mu power sigma s11 parameters, include=FALSE}
m_fit_1_5_s11$p_par
```



```{r linear mu power sigma fits, include=FALSE}
individual_fits_1_5 <- bind_rows(
  m_fit_1_5_s01$fit,
  m_fit_1_5_s02$fit,
  m_fit_1_5_s03$fit,
  m_fit_1_5_s04$fit,
  m_fit_1_5_s05$fit,
  m_fit_1_5_s06$fit,
  m_fit_1_5_s07$fit,
  m_fit_1_5_s08$fit,
  m_fit_1_5_s09$fit,
  m_fit_1_5_s10$fit,
  m_fit_1_5_s11$fit
)
```

```{r linear mu power sigma predictions, include=FALSE}
individual_preds_1_5 <- bind_rows(
  m_fit_1_5_s01$pred,
  m_fit_1_5_s02$pred,
  m_fit_1_5_s03$pred,
  m_fit_1_5_s04$pred,
  m_fit_1_5_s05$pred,
  m_fit_1_5_s06$pred,
  m_fit_1_5_s07$pred,
  m_fit_1_5_s08$pred,
  m_fit_1_5_s09$pred,
  m_fit_1_5_s10$pred,
  m_fit_1_5_s11$pred
)
```


```{r linear mu power sigma plot raw data, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_dat, aes(x = c, y = r_norm))+
    geom_line(data = individual_preds_1_5, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1.2)
```


```{r linear mu power sigma plot mean, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = individual_preds_1_5, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1) 



```


```{r linear mu power sigma sd, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = individual_preds_1_5,
            aes(x = x, y = sigma), color = "navajowhite3", linewidth = 1) +

  
  ylim(0, NA) 

```

```{r linear mu power sigma delta, include=FALSE}
ggplot() +
  facet_wrap(vars(participant)) +
  geom_line(data = individual_preds_1_5, 
            aes(x, delta_m), color = "aquamarine4", linewidth = 0.9) 
```

### MODELS:

```{r linear mu all models fits, include=FALSE}
individual_fits_1 <- bind_rows(
  individual_fits_1_1 |>  mutate(model = "1_1"),
  individual_fits_1_2 |>  mutate(model = "1_2"),
  individual_fits_1_3 |>  mutate(model = "1_3"),
  individual_fits_1_4 |>  mutate(model = "1_4"),
  individual_fits_1_5 |>  mutate(model = "1_5"))
  
```

```{r linealr mu all models predictions, include=FALSE}
individual_preds_1 <- bind_rows(
  individual_preds_1_1 |>  mutate(model = "1_1"),
  individual_preds_1_2 |>  mutate(model = "1_2"),
  individual_preds_1_3 |>  mutate(model = "1_3"),
  individual_preds_1_4 |>  mutate(model = "1_4"),
  individual_preds_1_5 |>  mutate(model = "1_5"))
```


### Plot models and raw data
```{r linear mu all models plot raw data, echo=FALSE}
ggplotly(ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_dat, aes(x = c, y = r_norm), alpha = .3) +
    geom_line(data = individual_preds_1, 
              aes(x = x, y = mu, color = model)))
```

### Plot models and mean 
```{r linear mu all models plot mean, echo=FALSE}
ggplotly(ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = m_norm), alpha = .3) +
    geom_line(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = individual_preds_1, 
              aes(x = x, y = mu, color = model)))
```

### Plot models and standard deviation 
```{r linear mu all models sd, echo=FALSE}
ggplotly(ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = sta_dev_norm), alpha = .3) +
    geom_line(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = individual_preds_1, 
              aes(x = x, y = sigma, color = model)))
```

### Plot models and delta
```{r linear mu all models delta, echo=FALSE}
ggplotly(ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_line(data = individual_preds_1, 
              aes(x = x, y = delta_m, color = model)))
```



