---
title: "Asymmetric Naka Rushton"
format: html
editor: source
---

Asymmetric Naka- Rushton 

$$
\Large \mu = \frac{p_1 \cdot x^{p_2}}{x^{p_2 + p_4} + p_3^{p_2 + p_4}}
$$

## Model 4_1: 

Asymmetric Naka Rushton mu and constant sigma
$$
\sigma = {p_5} 
$$

#### s01 {.hidden}

```{r asym naka mu constant noise s01, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_1_s01 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s01", 
  asym_naka_fun_mu,
  constant_sigma_asym_naka_mu,
  c(2,  2.49, .00001,  -1.5,    .0001), 
  c(40, 10,      .1,  .5,     40))

m_fit_4_1_s01$p
```


```{r asym naka mu constant noise parameters s01, include=FALSE}
m_fit_4_1_s01$p_par
```


#### s02 {.hidden}

```{r asym naka mu constant sigma s02, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_1_s02 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s02", 
  asym_naka_fun_mu,
  constant_sigma_asym_naka_mu,
  c(2,  2.49, .00001,  -1.5,    .0001), 
  c(50, 10,      .1,  .5,     40))

m_fit_4_1_s02$p
```


```{r asym naka mu constant sigma parameters s02, include=FALSE}
m_fit_4_1_s02$p_par
```

#### s03 {.hidden}


```{r asym naka mu constant sigma s03, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_1_s03 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s03", 
  asym_naka_fun_mu,
  constant_sigma_asym_naka_mu,
  c(2,  2.49, .00001,  -1.5,    .0001), 
  c(40, 10,      .1,  .5,     40))

m_fit_4_1_s03$p
```


```{r asym naka mu constant sigma parameters s03, include=FALSE}
m_fit_4_1_s03$p_par
```

#### s04 {.hidden}

```{r asym naka mu constant sigma s04, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_1_s04 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s04", 
  asym_naka_fun_mu,
  constant_sigma_asym_naka_mu,
  c(2,  2.49, .00001,  -1.5,    .0001), 
  c(40, 10,      .1,  .5,     40))

m_fit_4_1_s04$p
```


```{r asym naka mu constant sigma parameters s04, include=FALSE}
m_fit_4_1_s04$p_par
```


#### s05 {.hidden}


```{r asym naka mu constant sigma s05, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_1_s05 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s05", 
  asym_naka_fun_mu,
  constant_sigma_asym_naka_mu,
  c(2,  2.49, .00001,  -1.5,    .0001), 
  c(40, 10,      .1,  .5,     40))

m_fit_4_1_s05$p
```


```{r asym naka mu constant sigma parameters s05, include=FALSE}
m_fit_4_1_s05$p_par
```


#### s06 {.hidden}

```{r asym naka mu constant sigma s06, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_1_s06 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s06", 
  asym_naka_fun_mu,
  constant_sigma_asym_naka_mu,
  c(2,  2.49, .00001,  -1.5,    .0001), 
  c(40, 10,      .1,  .5,     40))

m_fit_4_1_s06$p
```

```{r asym naka mu constant sigma parameters s06, include=FALSE}
m_fit_4_1_s06$p_par
```


#### s07 {.hidden}

```{r asym naka mu constant sigma s07, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_1_s07 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s07", 
  asym_naka_fun_mu,
  constant_sigma_asym_naka_mu,
  c(2,  2.49, .00001,  -1.5,    .0001), 
  c(40, 10,      .1,  .5,     40))

m_fit_4_1_s07$p
```

```{r asym naka mu constant sigma parameters s07, include=FALSE}
m_fit_4_1_s07$p_par
```

#### s08 {.hidden}

```{r asym naka mu constant sigma s08, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_1_s08 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s08", 
  asym_naka_fun_mu,
  constant_sigma_asym_naka_mu,
  c(2,  2.49, .00001,  -1.5,    .0001), 
  c(40, 10,      .1,  .5,     40))

m_fit_4_1_s08$p
```

```{r asym naka mu constant sigma parameters s08, include=FALSE}
m_fit_4_1_s08$p_par
```

#### s09 {.hidden}

```{r asym naka mu constant sigma s09, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_1_s09 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s09", 
  asym_naka_fun_mu,
  constant_sigma_asym_naka_mu,
  c(2,  2.49, .00001,  -1.5,    .0001), 
  c(40, 10,      .1,  .5,     70))

m_fit_4_1_s09$p
```


```{r asym naka mu constant sigma parameters s09, include=FALSE}
m_fit_4_1_s09$p_par
```

#### s10 {.hidden}


```{r asym naka mu constant sigma s10, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_1_s10 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s10", 
  asym_naka_fun_mu,
  constant_sigma_asym_naka_mu,
  c(2,  2.49, .00001,  -1.5,    .0001), 
  c(40, 10,      .1,  .5,     40))

m_fit_4_1_s10$p
```

```{r asym naka mu constant sigma parameters s10, include=FALSE}
m_fit_4_1_s10$p_par
```

#### s11 {.hidden}

```{r asym naka mu constant sigma s11, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_1_s11 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s11", 
  asym_naka_fun_mu,
  constant_sigma_asym_naka_mu,
  c(2,  2.49, .00001,  -1.5,    .0001), 
  c(40, 10,      .1,  .5,     40))
m_fit_4_1_s11$p
```

```{r asym naka mu constant sigma parameters s11, include=FALSE}
m_fit_4_1_s11$p_par
```



```{r asym naka mu constant sigma fits, include=FALSE}
individual_fits_4_1 <- bind_rows(
  m_fit_4_1_s01$fit,
  m_fit_4_1_s02$fit,
  m_fit_4_1_s03$fit,
  m_fit_4_1_s04$fit,
  m_fit_4_1_s05$fit,
  m_fit_4_1_s06$fit,
  m_fit_4_1_s07$fit,
  m_fit_4_1_s08$fit,
  m_fit_4_1_s09$fit,
  m_fit_4_1_s10$fit,
  m_fit_4_1_s11$fit
)
```

```{r asym naka mu constant sigma preds, include=FALSE}
individual_preds_4_1 <- bind_rows(
  m_fit_4_1_s01$pred,
  m_fit_4_1_s02$pred,
  m_fit_4_1_s03$pred,
  m_fit_4_1_s04$pred,
  m_fit_4_1_s05$pred,
  m_fit_4_1_s06$pred,
  m_fit_4_1_s07$pred,
  m_fit_4_1_s08$pred,
  m_fit_4_1_s09$pred,
  m_fit_4_1_s10$pred,
  m_fit_4_1_s11$pred
)
```


```{r asym naka mu constant sigma plot raw data, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_dat, aes(x = c, y = r_norm))+
    geom_line(data = individual_preds_4_1, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1.2)
```


```{r asym naka mu constant sigma plot mean, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = individual_preds_4_1, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1) 



```


```{r asym naka mu constant sigma sd, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = individual_preds_4_1,
            aes(x = x, y = sigma), color = "navajowhite3", linewidth = 1) +

  
  ylim(0, NA) 

```

```{r asym naka mu constant sigma delta, include=FALSE}
ggplot() +
  facet_wrap(vars(participant)) +
  geom_line(data = individual_preds_4_1, 
            aes(x, delta_m), color = "aquamarine4", linewidth = 0.9) 
```
## Model 4_2: 
Aymmetric Naka Rushton mu, poisson sigma
$$
\sigma = \sqrt{\mu} + p_5
$$

#### s01 {.hidden}

```{r asym naka mu poisson sigma s01, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_2_s01 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s01", 
  asym_naka_fun_mu,
  poisson_sigma_asym_naka_mu,
  c(2,  1.5, .00001,  -1.5,    .0001), 
  c(40, 10,      .1,  .5,     10))

m_fit_4_2_s01$p
```


```{r asym naka mu poisson sigma parameters s01, include=FALSE}
m_fit_4_2_s01$p_par
```

#### s02 {.hidden}

<!-- p1 se va mucho -->

```{r asym naka mu poisson sigma s02, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_2_s02 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s02", 
  asym_naka_fun_mu,
  poisson_sigma_asym_naka_mu,
  c(2,  1.5, .00001,  -1.5,    .0001), 
  c(40, 10,      .1,  .5,     10))

m_fit_4_2_s02$p
```


```{r asym naka mu poisson sigma parameters s02, include=FALSE}
m_fit_4_2_s02$p_par
```

#### s03 {.hidden}


```{r asym naka mu poisson sigma s03, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_2_s03 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s03", 
  asym_naka_fun_mu,
  poisson_sigma_asym_naka_mu,
  c(2,  1.5, .00001,  -1.5,    .0001), 
  c(40, 10,      .1,  .5,     10))

m_fit_4_2_s03$p
```


```{r asym naka mu poisson sigma parameters s03, include=FALSE}
m_fit_4_2_s03$p_par
```

#### s04 {.hidden}

```{r asym naka mu poisson sigma s04, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_2_s04 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s04", 
  asym_naka_fun_mu,
  poisson_sigma_asym_naka_mu,
  c(2,  1.5, .00001,  -1.5,    .0001), 
  c(40, 10,      .1,  .5,     10))


m_fit_4_2_s04$p
```


```{r asym naka mu poisson sigma parameters s04, include=FALSE}
m_fit_4_2_s04$p_par
```

#### s05 {.hidden}

```{r asym naka mu poisson sigma s05, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_2_s05 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s05", 
  asym_naka_fun_mu,
  poisson_sigma_asym_naka_mu,
  c(2,  1.5, .00001,  -1.5,    .0001), 
  c(70, 10,      .1,  .5,     10))

m_fit_4_2_s05$p
```


```{r asym naka mu poisson noise parameters s05, include=FALSE}
m_fit_4_2_s05$p_par
```


#### s06 {.hidden}

```{r asym naka mu poisson sigma s06, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_2_s06 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s06", 
  asym_naka_fun_mu,
  poisson_sigma_asym_naka_mu,
  c(2,  1.5, .00001,  -1.5,    .0001), 
  c(40, 10,      .1,  .5,     10))

m_fit_4_2_s06$p
```

```{r asym naka mu poisson sigma parameters s06, include=FALSE}
m_fit_4_2_s06$p_par
```


#### s07 {.hidden}

```{r asym naka mu poisson sigma s07, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_2_s07 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s07", 
  asym_naka_fun_mu,
  poisson_sigma_asym_naka_mu,
  c(2,  1.5, .00001,  -1.5,    .0001), 
  c(40, 10,      .1,  .5,     10))

m_fit_4_2_s07$p
```

```{r asym naka mu poisson sigma parameters s07, include=FALSE}
m_fit_4_2_s07$p_par
```

#### s08 {.hidden}

```{r asym naka mu poisson sigma s08, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_2_s08 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s08", 
  asym_naka_fun_mu,
  poisson_sigma_asym_naka_mu,
  c(2,  1.5, .00001,  -1.5,    .0001), 
  c(70, 10,      .1,  .5,     10))

m_fit_4_2_s08$p
```

```{r asym naka mu poisson sigma parameters s08, include=FALSE}
m_fit_4_2_s08$p_par
```

#### s09 {.hidden}


```{r asym naka mu poisson sigma s09, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_2_s09 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s09", 
  asym_naka_fun_mu,
  poisson_sigma_asym_naka_mu,
  c(2,  .1, .00001,  -1.5,    .0001), 
  c(40, 20,      .1,  .5,     10))

m_fit_4_2_s09$p
```

<!-- No soy capaz de poner bien p2 -->
```{r asym naka mu poisson sigma parameters s09, include=FALSE}
m_fit_4_2_s09$p_par
```

#### s10 {.hidden}


```{r, asym naka mu poisson sigma s10, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_2_s10 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s10", 
  asym_naka_fun_mu,
  poisson_sigma_asym_naka_mu,
  c(2,  1.5, .00001,  -1.5,    .0001), 
  c(40, 10,      .1,  .5,     10))

m_fit_4_2_s10$p
```

```{r asym naka mu poisson sigma parameters s10, include=FALSE}
m_fit_4_2_s10$p_par
```


#### s11 {.hidden}

```{r asym naka mu poisson sigma s11, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_2_s11 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s11", 
  asym_naka_fun_mu,
  poisson_sigma_asym_naka_mu,
  c(2,  1.5, .00001,  -1.5,    .0001), 
  c(40, 10,      .1,  .5,     10))

m_fit_4_2_s11$p
```

```{r asym naka mu poisson sigma parameters s11, include=FALSE}
m_fit_4_2_s11$p_par
```



```{r asym naka mu poisson sigma fits, include=FALSE}
individual_fits_4_2 <- bind_rows(
  m_fit_4_2_s01$fit,
  m_fit_4_2_s02$fit,
  m_fit_4_2_s03$fit,
  m_fit_4_2_s04$fit,
  m_fit_4_2_s05$fit,
  m_fit_4_2_s06$fit,
  m_fit_4_2_s07$fit,
  m_fit_4_2_s08$fit,
  m_fit_4_2_s09$fit,
  m_fit_4_2_s10$fit,
  m_fit_4_2_s11$fit
)
```

```{r asym naka mu poisson sigma preds, include=FALSE}
individual_preds_4_2 <- bind_rows(
  m_fit_4_2_s01$pred,
  m_fit_4_2_s02$pred,
  m_fit_4_2_s03$pred,
  m_fit_4_2_s04$pred,
  m_fit_4_2_s05$pred,
  m_fit_4_2_s06$pred,
  m_fit_4_2_s07$pred,
  m_fit_4_2_s08$pred,
  m_fit_4_2_s09$pred,
  m_fit_4_2_s10$pred,
  m_fit_4_2_s11$pred
)
```


```{r asym naka mu poisson sigma plot raw data, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_dat, aes(x = c, y = r_norm))+
    geom_line(data = individual_preds_4_2, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1.2)
```


```{r asym naka mu poisson sigma plot mean, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = individual_preds_4_2, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1) 



```


```{r asym naka mu poisson sigma sd, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = individual_preds_4_2,
            aes(x = x, y = sigma), color = "navajowhite3", linewidth = 1) +

  
  ylim(0, NA) 

```

```{r asym naka mu poisson sigma delta, include=FALSE}
ggplot() +
  facet_wrap(vars(participant)) +
  geom_line(data = individual_preds_4_2, 
            aes(x, delta_m), color = "aquamarine4", linewidth = 0.9) 
```

## Model 4_3: 
Asymmetric Naka- Rushton mu, super poisson sigma
$$
\sigma = \sqrt{\mu + (p_5 \mu)^2} + p_6
$$

#### s01 {.hidden}
```{r asym naka mu super poisson sigma s01, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_3_s01 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s01", 
  asym_naka_fun_mu,
  super_poisson_sigma_asym_naka_mu,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.00001),
  c(40, 10,      .1,  .5,     10, 0.3))

m_fit_4_3_s01$p

```

```{r asym naka mu super poisson sigma parameters s01, include=FALSE}
m_fit_4_3_s01$p_par
```

#### s02 {.hidden}

```{r asym naka mu super poisson sigma s02, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_3_s02 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s02", 
  asym_naka_fun_mu,
  super_poisson_sigma_asym_naka_mu,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.00001),
  c(40, 10,      .1,  .5,     10, 0.3))

m_fit_4_3_s02$p
```


```{r asym naka mu super poisson sigma parameters s02, include=FALSE}
m_fit_4_3_s02$p_par
```


#### s03 {.hidden}


```{r asym naka mu super poisson sigma s03, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_3_s03 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s03", 
  asym_naka_fun_mu,
  super_poisson_sigma_asym_naka_mu,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.00001),
  c(40, 10,      .1,  .5,     10, 0.3))

m_fit_4_3_s03$p
```


```{r asym naka mu super poisson sigma parameters s03, include=FALSE}
m_fit_4_3_s03$p_par
```

#### s04 {.hidden}

```{r asym naka mu super poisson sigma s04, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_3_s04 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s04", 
  asym_naka_fun_mu,
  super_poisson_sigma_asym_naka_mu,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.00001),
  c(40, 10,      .1,  .5,     10, 0.3))

m_fit_4_3_s04$p
```


```{r asym naka mu super poisson sigma parameters s04, include=FALSE}
m_fit_4_3_s04$p_par
```

#### s05 {.hidden}


```{r asym naka mu super poisson sigma s05, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_3_s05 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s05", 
  asym_naka_fun_mu,
  super_poisson_sigma_asym_naka_mu,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.00001),
  c(50, 10,      .1,  .5,     10, 0.3))

m_fit_4_3_s05$p
```


```{r asym naka mu super poisson sigma parameters s05, include=FALSE}
m_fit_4_3_s05$p_par
```

#### s06 {.hidden}

```{r asym naka mu super poisson sigma s06, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_3_s06 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s06", 
  asym_naka_fun_mu,
  super_poisson_sigma_asym_naka_mu,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.00001),
  c(40, 10,      .1,  .5,     10, 0.3))

m_fit_4_3_s06$p
```

```{r asym naka mu super poisson sigma parameters s06, include=FALSE}
m_fit_4_3_s06$p_par
```

#### s07 {.hidden}

```{r, asym naka mu super poisson sigma s07, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_3_s07 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s07", 
  asym_naka_fun_mu,
  super_poisson_sigma_asym_naka_mu,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.00001),
  c(40, 10,      .1,  .5,     10, 0.3))

m_fit_4_3_s07$p
```

```{r asym naka mu super poisson sigma parameters s07, include=FALSE}
m_fit_4_3_s07$p_par
```

#### s08 {.hidden}

```{r asym naka mu super poisson sigma s08, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_3_s08 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s08", 
  asym_naka_fun_mu,
  super_poisson_sigma_asym_naka_mu,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.00001),
  c(50, 10,      .1,  .5,     10, 0.3))

m_fit_4_3_s08$p
```

```{r asym naka mu super poisson sigma parameters s08, include=FALSE}
m_fit_4_3_s08$p_par
```

#### s09 {.hidden}

```{r asym naka mu super poisson sigma s09, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_3_s09 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s09", 
  asym_naka_fun_mu,
  super_poisson_sigma_asym_naka_mu,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.00001),
  c(40, 10,      .1,  .5,     10, 0.3))

m_fit_4_3_s09$p
```


```{r asym naka mu super poisson sigma parameters s09, include=FALSE}
m_fit_4_3_s09$p_par
```

#### s10 {.hidden}


```{r asym naka mu super poisson sigma s10, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_3_s10 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s10",
  asym_naka_fun_mu,
  super_poisson_sigma_asym_naka_mu,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.00001),
  c(40, 10,      .1,  .5,     10, 0.3))

m_fit_4_3_s10$p
```

```{r asym naka mu super poisson sigma parameters s10, include=FALSE}
m_fit_4_3_s10$p_par
```

#### s11 {.hidden}

```{r asym naka mu super poisson sigma s11, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_3_s11 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s11", 
  asym_naka_fun_mu,
  super_poisson_sigma_asym_naka_mu,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.00001),
  c(40, 10,      .1,  .5,     10, 0.3))

m_fit_4_3_s11$p
```

```{r asym naka mu super poisson sigma parameters s11, include=FALSE}
m_fit_4_3_s11$p_par
```



```{r asym naka mu super poisson sigma fits, include=FALSE}
individual_fits_4_3 <- bind_rows(
  m_fit_4_3_s01$fit,
  m_fit_4_3_s02$fit,
  m_fit_4_3_s03$fit,
  m_fit_4_3_s04$fit,
  m_fit_4_3_s05$fit,
  m_fit_4_3_s06$fit,
  m_fit_4_3_s07$fit,
  m_fit_4_3_s08$fit,
  m_fit_4_3_s09$fit,
  m_fit_4_3_s10$fit,
  m_fit_4_3_s11$fit
)
```

```{r asym naka mu super poisson sigma preds, include=FALSE}
individual_preds_4_3 <- bind_rows(
  m_fit_4_3_s01$pred,
  m_fit_4_3_s02$pred,
  m_fit_4_3_s03$pred,
  m_fit_4_3_s04$pred,
  m_fit_4_3_s05$pred,
  m_fit_4_3_s06$pred,
  m_fit_4_3_s07$pred,
  m_fit_4_3_s08$pred,
  m_fit_4_3_s09$pred,
  m_fit_4_3_s10$pred,
  m_fit_4_3_s11$pred
)
```


```{r asym naka mu super poisson sigma plot raw data, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_dat, aes(x = c, y = r_norm))+
    geom_line(data = individual_preds_4_3, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1.2)
```


```{r asym naka mu super poisson sigma plot mean, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = individual_preds_4_3, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1) 



```


```{r asym naka mu super poisson sigma sd, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = individual_preds_4_3,
            aes(x = x, y = sigma), color = "navajowhite3", linewidth = 1) +

  
  ylim(0, NA) 

```

```{r asym naka mu super poisson sigma delta, include=FALSE}
ggplot() +
  facet_wrap(vars(participant)) +
  geom_line(data = individual_preds_4_3, 
            aes(x, delta_m), color = "aquamarine4", linewidth = 0.9) 
```

## Model 4_4: 
Asymmetric Naka Rushton mu, multiplicative sigma
$$
\sigma = p_5 \cdot \mu + {p_6}
$$

#### s01 {.hidden}
```{r asym naka mu mult sigma s01, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_4_s01 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s01", 
  asym_naka_fun_mu,
  mult_sigma_asym_naka_mu,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.001),
  c(40, 10,      .1,  .5,     10, 3))

m_fit_4_4_s01$p

```

```{r asym naka mu mult sigma parameters s01, include=FALSE}
m_fit_4_4_s01$p_par
```

#### s02 {.hidden}

```{r asym naka mu mult sigma s02, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_4_s02 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s02", 
  asym_naka_fun_mu,
  mult_sigma_asym_naka_mu,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.001),
  c(40, 10,      .1,  .5,     10, 3))

m_fit_4_4_s02$p
```


```{r asym naka mu mult sigma parameters s02, include=FALSE}
m_fit_4_4_s02$p_par
```

#### s03 {.hidden}

```{r asym naka mu mult sigma s03, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_4_s03 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s03", 
  asym_naka_fun_mu,
  mult_sigma_asym_naka_mu,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.001),
  c(40, 10,      .1,  .5,     10, 3))

m_fit_4_4_s03$p
```


```{r asym naka mu mult sigma parameters s03, include=FALSE}
m_fit_4_4_s03$p_par
```

#### s04 {.hidden}

```{r asym naka mu mult sigma s04, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_4_s04 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s04", 
  asym_naka_fun_mu,
  mult_sigma_asym_naka_mu,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.001),
  c(40, 10,      .1,  .5,     10, 3))

m_fit_4_4_s04$p
```


```{r asym naka mu mult sigma parameters s04, include=FALSE}
m_fit_4_4_s04$p_par
```

#### s05 {.hidden}


```{r asym naka mu mult sigma s05, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_4_s05 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s05", 
  asym_naka_fun_mu,
  mult_sigma_asym_naka_mu,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.001),
  c(40, 10,      .1,  .5,     10, 3))

m_fit_4_4_s05$p
```


```{r asym naka mu mult sigma parameters s05, include=FALSE}
m_fit_4_4_s05$p_par
```


#### s06 {.hidden}

```{r asym naka mu mult sigma s06, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_4_s06 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s06", 
  asym_naka_fun_mu,
  mult_sigma_asym_naka_mu,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.001),
  c(40, 10,      .1,  .5,     10, 3))

m_fit_4_4_s06$p
```

```{r asym naka mu mult sigma parameters s06, include=FALSE}
m_fit_4_4_s06$p_par
```

#### s07 {.hidden}

```{r asym naka mu mult sigma s07, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_4_s07 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s07", 
  asym_naka_fun_mu,
  mult_sigma_asym_naka_mu,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.001),
  c(40, 10,      .1,  .5,     10, 3))

m_fit_4_4_s07$p
```

```{r asym naka mu mult sigma parameters s07, include=FALSE}
m_fit_4_4_s07$p_par
```

#### s08 {.hidden}

```{r asym naka mu mult sigma s08, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_4_s08 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s08", 
  asym_naka_fun_mu,
  mult_sigma_asym_naka_mu,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.001),
  c(50, 10,      .1,  .5,     10, 3))

m_fit_4_4_s08$p
```

```{r asym naka mu mult sigma parameters s08, include=FALSE}
m_fit_4_4_s08$p_par
```

#### s09 {.hidden}


```{r asym naka mu mult sigma s09, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_4_s09 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s09", 
  asym_naka_fun_mu,
  mult_sigma_asym_naka_mu,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.001),
  c(40, 10,      .1,  .5,     10, 3))

m_fit_4_4_s09$p
```


```{r asym naka mu mult sigma parameters s09, include=FALSE}
m_fit_4_4_s09$p_par
```

#### s10 {.hidden}

```{r asym naka mu mult sigma s10, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_4_s10 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s10",
  asym_naka_fun_mu,
  mult_sigma_asym_naka_mu,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.001),
  c(40, 15,      .1,  .5,     10, 0.5))

m_fit_4_4_s10$p
```

```{r asym naka mu mult sigma parameters s10, include=FALSE}
m_fit_4_4_s10$p_par
```

#### s11 {.hidden}

```{r asym naka mu mult sigma s11, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_4_s11 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s11", 
  asym_naka_fun_mu,
  mult_sigma_asym_naka_mu,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.001),
  c(40, 10,      .1,  .5,     10, 3))

m_fit_4_4_s11$p
```

```{r asym naka mu mult sigma parameters s11, include=FALSE}
m_fit_4_4_s11$p_par
```



```{r asym naka mu mult sigma fits, include=FALSE}
individual_fits_4_4 <- bind_rows(
  m_fit_4_4_s01$fit,
  m_fit_4_4_s02$fit,
  m_fit_4_4_s03$fit,
  m_fit_4_4_s04$fit,
  m_fit_4_4_s05$fit,
  m_fit_4_4_s06$fit,
  m_fit_4_4_s07$fit,
  m_fit_4_4_s08$fit,
  m_fit_4_4_s09$fit,
  m_fit_4_4_s10$fit,
  m_fit_4_4_s11$fit
)
```

```{r asym naka mu mult sigma preds, include=FALSE}
individual_preds_4_4 <- bind_rows(
  m_fit_4_4_s01$pred,
  m_fit_4_4_s02$pred,
  m_fit_4_4_s03$pred,
  m_fit_4_4_s04$pred,
  m_fit_4_4_s05$pred,
  m_fit_4_4_s06$pred,
  m_fit_4_4_s07$pred,
  m_fit_4_4_s08$pred,
  m_fit_4_4_s09$pred,
  m_fit_4_4_s10$pred,
  m_fit_4_4_s11$pred
)
```


```{r asym naka mu mult sigma plot raw data, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_dat, aes(x = c, y = r_norm))+
    geom_line(data = individual_preds_4_4, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1.2)
```


```{r asym naka mu mult sigma plot mean, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = individual_preds_4_4, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1) 



```


```{r asym naka mu mult sigma sd, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = individual_preds_4_4,
            aes(x = x, y = sigma), color = "navajowhite3", linewidth = 1) +

  
  ylim(0, NA) 

```

```{r asym naka mu mult sigma delta, include=FALSE}
ggplot() +
  facet_wrap(vars(participant)) +
  geom_line(data = individual_preds_4_4, 
            aes(x, delta_m), color = "aquamarine4", linewidth = 0.9) 
```

## Model 4_5: 
Asymmetric Naka- Rushton mu, power sigma
$$
\sigma = p_5 \cdot (\mu)^{p_7} + {p_6}
$$


#### s01 {.hidden}

```{r asym naka mu power sigma s01, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_5_s01 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s01", 
  asym_naka_fun_mu,
  power_sigma_asym_naka_mu,
  c(20,  2, .009,  -1.3,    .05,  .000001,  .001), 
  c(35, 8,  .03,  -.5,      1,    .1,   1))

m_fit_4_5_s01$p

```

```{r asym naka mu power sigma parameters s01, include=FALSE}
m_fit_4_5_s01$p_par
```

#### s02 {.hidden}

```{r asym naka mu power sigma s02, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_5_s02 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s02", 
  asym_naka_fun_mu,
  power_sigma_asym_naka_mu,
  c(.01,  1, .01,  -1,    .05,  .00001,  .001), 
  c(20, 6,  .1,  0,      1,    .2,   1))

m_fit_4_5_s02$p
```


```{r asym naka mu power sigma parameters s02, include=FALSE}
m_fit_4_5_s02$p_par
```

#### s03 {.hidden}

```{r asym naka mu power sigma s03, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_5_s03 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s03", 
  asym_naka_fun_mu,
  power_sigma_asym_naka_mu,
  c(1,  1, .0005,  -1,    .05,  .00001,  .001), 
  c(20, 10,  .05,  0,      1,    .07,   1))

m_fit_4_5_s03$p
```


```{r asym naka mu power sigma parameters s03, include=FALSE}
m_fit_4_5_s03$p_par
```

#### s04 {.hidden}

```{r asym naka mu power sigma s04, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_5_s04 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s04", 
  asym_naka_fun_mu,
  power_sigma_asym_naka_mu,
  c(.01,  1, .005,  -1,    .05,  .00001,  .001), 
  c(25, 10,  .2,  0,      1,    .2,   2))

m_fit_4_5_s04$p
```


```{r asym naka mu power sigma parameters s04, include=FALSE}
m_fit_4_5_s04$p_par
```

#### s05 {.hidden}

```{r asym naka mu power sigma s05, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_5_s05 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s05", 
  asym_naka_fun_mu,
  power_sigma_asym_naka_mu,
  c(10,  1, .01,  -1.5,    .05,  .00001,  .001) , 
  c(40, 6,  .1,  -.25,      1,    .2,   2))

m_fit_4_5_s05$p
```


```{r asym naka mu power sigma parameters s05, include=FALSE}
m_fit_4_5_s05$p_par
```


#### s06 {.hidden}

```{r asym naka mu power sigma s06, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_5_s06 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s06", 
  asym_naka_fun_mu,
  power_sigma_asym_naka_mu,
  c(.01,  1, .005,  -1.5,    .05,  .0001,  .001), 
  c(10, 10,  .1,  0,      1,    .2,   2))

m_fit_4_5_s06$p
```

```{r asym naka mu power sigma parameters s06, include=FALSE}
m_fit_4_5_s06$p_par
```

#### s07 {.hidden}

```{r asym naka mu power sigma s07, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_5_s07 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s07", 
  asym_naka_fun_mu,
  power_sigma_asym_naka_mu,
  c(.01,  1, .005,  -1.5,    .05,  .00001,  .001), 
  c(10, 5,  .1,  0,      .5,    .2,   2))

m_fit_4_5_s07$p
```

```{r asym naka mu power sigma parameters s07, include=FALSE}
m_fit_4_5_s07$p_par
```


#### s08 {.hidden}

```{r asym naka mu power sigma s08, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_5_s08 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s08", 
  asym_naka_fun_mu,
  power_sigma_asym_naka_mu,
  c(.01,  1, .01,  -1.5,    .05,  .00001,  .001), 
  c(40, 6,  .1,  0,      1,    .2,   1))

m_fit_4_5_s08$p
```

```{r asym naka mu power sigma parameters s08, include=FALSE}
m_fit_4_5_s08$p_par
```


#### s09 {.hidden}

```{r asym naka mu power sigma s09, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_5_s09 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s09", 
  asym_naka_fun_mu,
  power_sigma_asym_naka_mu,
  c(.01,  1, .01,  -1.5,    .05,  .0001,  .001), 
  c(80, 30,  .1,  0,      2,    .2,   1.5))

m_fit_4_5_s09$p
```


```{r asym naka mu power sigma parameters s09, include=FALSE}
m_fit_4_5_s09$p_par
```

#### s10 {.hidden}

```{r asym naka mu power sigma s10, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_5_s10 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s10",
  asym_naka_fun_mu,
  power_sigma_asym_naka_mu,
  c(.01,  1, .01,  -1,    .05,  .000001,  .001), 
  c(30, 15,  .2,  0,      1,    .002,   2))

m_fit_4_5_s10$p
```

```{r asym naka mu power sigma parameters s10, include=FALSE}
m_fit_4_5_s10$p_par
```


#### s11 {.hidden}

```{r asym naka mu power sigma s11, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_5_s11 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s11", 
  asym_naka_fun_mu,
  power_sigma_asym_naka_mu,
  c(.01,  1, .005,  -1,    .0005,  .00001,  0.1), 
  c(25, 30,  .2,  0,      2,    .15,   2))

m_fit_4_5_s11$p
```

```{r asym naka mu power sigma parameters s11, include=FALSE}
m_fit_4_5_s11$p_par
```



```{r asym naka mu power sigma fits, include=FALSE}
individual_fits_4_5 <- bind_rows(
  m_fit_4_5_s01$fit,
  m_fit_4_5_s02$fit,
  m_fit_4_5_s03$fit,
  m_fit_4_5_s04$fit,
  m_fit_4_5_s05$fit,
  m_fit_4_5_s06$fit,
  m_fit_4_5_s07$fit,
  m_fit_4_5_s08$fit,
  m_fit_4_5_s09$fit,
  m_fit_4_5_s10$fit,
  m_fit_4_5_s11$fit
)
```

```{r asym naka mu power sigma preds, include=FALSE}
individual_preds_4_5 <- bind_rows(
  m_fit_4_5_s01$pred,
  m_fit_4_5_s02$pred,
  m_fit_4_5_s03$pred,
  m_fit_4_5_s04$pred,
  m_fit_4_5_s05$pred,
  m_fit_4_5_s06$pred,
  m_fit_4_5_s07$pred,
  m_fit_4_5_s08$pred,
  m_fit_4_5_s09$pred,
  m_fit_4_5_s10$pred,
  m_fit_4_5_s11$pred
)
```


```{r asym naka mu power sigma plot raw data, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_dat, aes(x = c, y = r_norm))+
    geom_line(data = individual_preds_4_5, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1.2)
```


```{r asym naka mu power sigma plot mean, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = individual_preds_4_5, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1) 



```


```{r asym naka mu power sigma sd, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = individual_preds_4_5,
            aes(x = x, y = sigma), color = "navajowhite3", linewidth = 1) +

  
  ylim(0, NA) 

```

```{r asym naka mu power sigma delta, include=FALSE}
ggplot() +
  facet_wrap(vars(participant)) +
  geom_line(data = individual_preds_4_5, 
            aes(x, delta_m), color = "aquamarine4", linewidth = 0.9) 
```




### MODELS:

```{r linear mu all models model 4 fits, include=FALSE}
individual_fits_4 <- bind_rows(
  individual_fits_4_1 |>  mutate(model = "4_1"),
  individual_fits_4_2 |>  mutate(model = "4_2"),
  individual_fits_4_3 |>  mutate(model = "4_3"),
  individual_fits_4_4 |>  mutate(model = "4_4"),
  individual_fits_4_5 |>  mutate(model = "4_5"))
  
```

```{r linealr mu all models model 4 predictions, include=FALSE}
individual_preds_4 <- bind_rows(
  individual_preds_4_1 |>  mutate(model = "4_1"),
  individual_preds_4_2 |>  mutate(model = "4_2"),
  individual_preds_4_3 |>  mutate(model = "4_3"),
  individual_preds_4_4 |>  mutate(model = "4_4"),
  individual_preds_4_5 |>  mutate(model = "4_5"))
```


### Plot models and raw data
```{r linear mu all models model 4 plot raw data, echo=FALSE}
ggplotly(ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_dat, aes(x = c, y = r_norm), alpha = .3) +
    geom_line(data = individual_preds_4, 
              aes(x = x, y = mu, color = model)))
```

### Plot models and mean 
```{r linear mu all models model 4 plot mean, echo=FALSE}
ggplotly(ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = m_norm), alpha = .3) +
    geom_line(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = individual_preds_4, 
              aes(x = x, y = mu, color = model)))
```

### Plot models and standard deviation 
```{r linear mu all models model 4 sd, echo=FALSE}
ggplotly(ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = sta_dev_norm), alpha = .3) +
    geom_line(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = individual_preds_4 |> 
                filter(model %in% c("4_2", "4_5")), 
              aes(x = x, y = sigma, color = model)))
```

### Plot models and delta
```{r linear mu all models model 4 delta, echo=FALSE}
ggplotly(ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_line(data = individual_preds_4, 
              aes(x = x, y = delta_m, color = model)))
```

