---
title: "Symetric Naka Rushton"
format: html
editor: source
---

Symmetric Naka- Rushton 
$$
\Large \mu = \frac{p_1 \cdot x^{p_2}}{x^{p_2} + p_3^{p_2}}
$$ 

## Model 3_1: 

Symmetric Naka Rushton mu and constant sigma

$$
\sigma = {p_4} 
$$

#### s01 {.hidden}

```{r sym naka mu constant noise s01, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_1_s01 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s01", 
  sym_naka_fun_mu,
  constant_sigma_sym_naka_mu,
  rep(.0000001, 4), 
  c(200, 2.5, 10, 30))

m_fit_3_1_s01$p
```


```{r sym naka mu constant noise parameters s01, include=FALSE}
m_fit_3_1_s01$p_par
```


#### s02 {.hidden}

```{r sym naka mu constant sigma s02, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_1_s02 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s02", 
  sym_naka_fun_mu,
  constant_sigma_sym_naka_mu,
  rep(.0000001, 4), 
  c(40, 5, .5, 30))

m_fit_3_1_s02$p
```


```{r sym naka mu constant sigma parameters s02, include=FALSE}
m_fit_3_1_s02$p_par
```


#### s03 {.hidden}


```{r sym naka mu constant sigma s03, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_1_s03 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s03", 
  sym_naka_fun_mu,
  constant_sigma_sym_naka_mu,
  rep(.0000001, 4), 
  c(40, 5, .5, 30))

m_fit_3_1_s03$p
```


```{r sym naka mu constant sigma parameters s03, include=FALSE}
m_fit_3_1_s03$p_par
```


#### s04 {.hidden}

```{r sym naka mu constant sigma s04, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_1_s04 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s04", 
  sym_naka_fun_mu,
  constant_sigma_sym_naka_mu,
  rep(.0000001, 4), 
  c(40, 5, .5, 30))

m_fit_3_1_s04$p
```


```{r sym naka mu constant sigma parameters s04, include=FALSE}
m_fit_3_1_s04$p_par
```

#### s05 {.hidden}

```{r sym naka mu constant sigma s05, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_1_s05 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s05", 
  sym_naka_fun_mu,
  constant_sigma_sym_naka_mu,
  rep(.0000001, 4), 
  c(40, 5, .5, 30))

m_fit_3_1_s05$p
```


```{r sym naka mu constant sigma parameters s05, include=FALSE}
m_fit_3_1_s05$p_par
```


#### s06 {.hidden}

```{r sym naka mu constant sigma s06, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_1_s06 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s06", 
  sym_naka_fun_mu,
  constant_sigma_sym_naka_mu,
  rep(.0000001, 4), 
  c(40, 5, .5, 30))

m_fit_3_1_s06$p
```

```{r sym naka mu constant sigma parameters s06, include=FALSE}
m_fit_3_1_s06$p_par
```


#### s07 {.hidden}

```{r sym naka mu sigma constant s07, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_1_s07 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s07", 
  sym_naka_fun_mu,
  constant_sigma_sym_naka_mu,
  rep(.0000001, 4), 
  c(40, 5, .5, 30))

m_fit_3_1_s07$p
```

```{r sym naka mu constant sigma parameters s07, include=FALSE}
m_fit_3_1_s07$p_par
```

#### s08 {.hidden}

```{r sym naka mu sigma constant s08, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_1_s08 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s08", 
  sym_naka_fun_mu,
  constant_sigma_sym_naka_mu,
  rep(.0000001, 4), 
  c(40, 5, .5, 30))

m_fit_3_1_s08$p
```

```{r sym naka mu constant sigma parameters s08, include=FALSE}
m_fit_3_1_s08$p_par
```

#### s09 {.hidden}


```{r sym naka mu constant sigma s09, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_1_s09 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s09", 
  sym_naka_fun_mu,
  constant_sigma_sym_naka_mu,
  rep(.0000001, 4), 
  c(40, 5, .5, 60))

m_fit_3_1_s09$p
```


```{r sym naka mu constant sigma parameters s09, include=FALSE}
m_fit_3_1_s09$p_par
```

#### s10 {.hidden}


```{r sym naka mu constant sigma s10, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_1_s10 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s10", 
  sym_naka_fun_mu,
  constant_sigma_sym_naka_mu,
  rep(.0000001, 4), 
  c(40, 5, .5, 30))

m_fit_3_1_s10$p
```

```{r sym naka mu constant sigma parameters s10, include=FALSE}
m_fit_3_1_s10$p_par
```


#### s11 {.hidden}


```{r sym naka mu constant sigma s11, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_1_s11 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s11", 
  sym_naka_fun_mu,
  constant_sigma_sym_naka_mu,
  rep(.0000001, 4), 
  c(40, 5, .5, 30))
m_fit_3_1_s11$p
```

```{r sym naka mu constant sigma parameters s11, include=FALSE}
m_fit_3_1_s11$p_par
```



```{r sym naka mu constant sigma fits, include=FALSE}
individual_fits_3_1 <- bind_rows(
  m_fit_3_1_s01$fit,
  m_fit_3_1_s02$fit,
  m_fit_3_1_s03$fit,
  m_fit_3_1_s04$fit,
  m_fit_3_1_s05$fit,
  m_fit_3_1_s06$fit,
  m_fit_3_1_s07$fit,
  m_fit_3_1_s08$fit,
  m_fit_3_1_s09$fit,
  m_fit_3_1_s10$fit,
  m_fit_3_1_s11$fit
)
```

```{r sym naka mu constant sigma predictions, include=FALSE}
individual_preds_3_1 <- bind_rows(
  m_fit_3_1_s01$pred,
  m_fit_3_1_s02$pred,
  m_fit_3_1_s03$pred,
  m_fit_3_1_s04$pred,
  m_fit_3_1_s05$pred,
  m_fit_3_1_s06$pred,
  m_fit_3_1_s07$pred,
  m_fit_3_1_s08$pred,
  m_fit_3_1_s09$pred,
  m_fit_3_1_s10$pred,
  m_fit_3_1_s11$pred
)
```


```{r sym naka mu constant sigma plot raw data, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_dat, aes(x = c, y = r_norm))+
    geom_line(data = individual_preds_3_1, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1.2)
```


```{r sym naka mu constant sigma plot mean, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = m_norm)) +
        # geom_line(data = m_pred_model_3_1, 
        #       aes(x = x, y = mu), color = "blue", alpha = .5) +
    geom_line(data = individual_preds_3_1, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1) 



```


```{r sym naka mu constant sigma sd, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
      # geom_line(data = m_pred_model_3_1,
      #       aes(x = x, y = sigma), color = "blue", alpha = .5) +
    geom_line(data = individual_preds_3_1,
            aes(x = x, y = sigma), color = "navajowhite3", linewidth = 1) +

  
  ylim(0, NA) 

```

```{r sym naka mu constant sigma delta, include=FALSE}
ggplot() +
  facet_wrap(vars(participant)) +
  #geom_line(data= d_delta, aes(x, delta_d)) +
  geom_line(data = individual_preds_3_1, 
            aes(x, delta_m), color = "aquamarine4", linewidth = 0.9) 
```


## Model 3_2: 
Symmetric Naka Rushton mu, poisson sigma

$$
\sigma = \sqrt{\mu} + {p_4}
$$ 

#### s01 {.hidden}

```{r sym naka mu poisson sigma s01, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_2_s01 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s01", 
  sym_naka_fun_mu,
  poisson_sigma_sym_naka_mu,
  rep(.0000001, 4), 
  c(10, 11, .2, 50))

m_fit_3_2_s01$p
```


```{r sym naka mu poisson sigma parameters s01, include=FALSE}
m_fit_3_2_s01$p_par
```



#### s02 {.hidden}

<!-- p1 se va mucho -->

```{r sym naka mu poisson sigma s02, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_2_s02 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s02", 
  sym_naka_fun_mu,
  poisson_sigma_sym_naka_mu,
  rep(.0000001, 4), 
  c(10, 11, .2, 50))

m_fit_3_2_s02$p
```


```{r sym naka mu poisson sigma parameters s02, include=FALSE}
m_fit_3_2_s02$p_par
```



#### s03 {.hidden}


```{r sym naka mu poisson sigma s03, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_2_s03 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s03", 
  sym_naka_fun_mu,
  poisson_sigma_sym_naka_mu,
  rep(.0000001, 4), 
  c(10, 11, .2, 50))

m_fit_3_2_s03$p
```


```{r sym naka mu poisson sigma parameters s03, include=FALSE}
m_fit_3_2_s03$p_par
```

#### s04 {.hidden}

```{r sym naka mu poisson sigma s04, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_2_s04 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s04", 
  sym_naka_fun_mu,
  poisson_sigma_sym_naka_mu,
  rep(.0000001, 4), 
  c(10, 11, .2, 50))


m_fit_3_2_s04$p
```


```{r sym naka mu poisson sigma parameters s04, include=FALSE}
m_fit_3_2_s04$p_par
```

#### s05 {.hidden}


```{r sym naka mu poisson sigma s05, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_2_s05 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s05", 
  sym_naka_fun_mu,
  poisson_sigma_sym_naka_mu,
  rep(.0000001, 4), 
  c(10, 11, .2, 50))

m_fit_3_2_s05$p
```


```{r sym naka mu poisson sigma parameters s05, include=FALSE}
m_fit_3_2_s05$p_par
```


#### s06 {.hidden}

```{r sym naka mu poisson sigma s06, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_2_s06 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s06", 
  sym_naka_fun_mu,
  poisson_sigma_sym_naka_mu,
  rep(.0000001, 4), 
  c(10, 11, .2, 50))

m_fit_3_2_s06$p
```

```{r sym naka mu poisson sigma parameters s06, include=FALSE}
m_fit_3_2_s06$p_par
```


#### s07 {.hidden}

```{r sym naka mu poisson sigma s07, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_2_s07 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s07", 
  sym_naka_fun_mu,
  poisson_sigma_sym_naka_mu,
  rep(.0000001, 4), 
  c(10, 11, .2, 50))

m_fit_3_2_s07$p
```

```{r sym naka mu poisson sigma parameters s07, include=FALSE}
m_fit_3_2_s07$p_par
```

#### s08 {.hidden}

```{r sym naka mu poisson sigma s08, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_2_s08 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s08", 
  sym_naka_fun_mu,
  poisson_sigma_sym_naka_mu,
  rep(.0000001, 4), 
  c(10, 11, .2, 50))

m_fit_3_2_s08$p
```

```{r sym naka mu poisson sigma parameters s08, include=FALSE}
m_fit_3_2_s08$p_par
```


#### s09 {.hidden}


```{r sym naka mu poisson sigma s09, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_2_s09 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s09", 
  sym_naka_fun_mu,
  poisson_sigma_sym_naka_mu,
  rep(.0000001, 4), 
  c(10, 11, .2, 50))

m_fit_3_2_s09$p
```


```{r sym naka mu poisson sigma parameters s09, include=FALSE}
m_fit_3_2_s09$p_par
```

#### s10 {.hidden}


```{r sym naka mu poisson sigma s10, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_2_s10 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s10", 
  sym_naka_fun_mu,
  poisson_sigma_sym_naka_mu,
  rep(.0000001, 4), 
  c(10, 11, .2, 50))

m_fit_3_2_s10$p
```

```{r sym naka mu poisson sigma parameters s10, include=FALSE}
m_fit_3_2_s10$p_par
```

#### s11 {.hidden}


```{r sym naka mu poisson sigma s11, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_2_s11 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s11", 
  sym_naka_fun_mu,
  poisson_sigma_sym_naka_mu,
  rep(.0000001, 4), 
  c(10, 11, .2, 50))

m_fit_3_2_s11$p
```

```{r sym naka mu poisson sigma parameters s11, include=FALSE}
m_fit_3_2_s11$p_par
```



```{r sym naka mu poisson sigma fits, include=FALSE}
individual_fits_3_2 <- bind_rows(
  m_fit_3_2_s01$fit,
  m_fit_3_2_s02$fit,
  m_fit_3_2_s03$fit,
  m_fit_3_2_s04$fit,
  m_fit_3_2_s05$fit,
  m_fit_3_2_s06$fit,
  m_fit_3_2_s07$fit,
  m_fit_3_2_s08$fit,
  m_fit_3_2_s09$fit,
  m_fit_3_2_s10$fit,
  m_fit_3_2_s11$fit
)
```

```{r sym naka mu poisson sigma predictions, include=FALSE}
individual_preds_3_2 <- bind_rows(
  m_fit_3_2_s01$pred,
  m_fit_3_2_s02$pred,
  m_fit_3_2_s03$pred,
  m_fit_3_2_s04$pred,
  m_fit_3_2_s05$pred,
  m_fit_3_2_s06$pred,
  m_fit_3_2_s07$pred,
  m_fit_3_2_s08$pred,
  m_fit_3_2_s09$pred,
  m_fit_3_2_s10$pred,
  m_fit_3_2_s11$pred
)
```


```{r sym naka mu poisson sigma plot raw data, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_dat, aes(x = c, y = r_norm))+
    geom_line(data = individual_preds_3_2, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1.2)
```


```{r sym naka mu poisson sigma plot mean, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = individual_preds_3_2, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1) 



```


```{r sym naka mu poisson sigma sd, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = individual_preds_3_2,
            aes(x = x, y = sigma), color = "navajowhite3", linewidth = 1) +

  
  ylim(0, NA) 

```

```{r sym naka mu poisson sigma delta, include=FALSE}
ggplot() +
  facet_wrap(vars(participant)) +
  geom_line(data = individual_preds_3_2, 
            aes(x, delta_m), color = "aquamarine4", linewidth = 0.9) 
```

## Model 3_3: 
Symmetric Naka- Rushton mu, super poisson sigma

$$
\sigma = \sqrt{\mu + (p_4 \mu)^2} + p_5
$$

#### s01 {.hidden}

```{r sym naka mu super poisson sigma s01, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_3_s01 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s01", 
  sym_naka_fun_mu,
  super_poisson_sigma_sym_naka_mu,
  rep(.0000001, 5),
  c(6, 11, .2, 2.5, 0.2))

m_fit_3_3_s01$p

```

```{r sym naka mu super poisson sigma parameters s01, include=FALSE}
m_fit_3_3_s01$p_par
```

#### s02 {.hidden}

```{r sym naka mu super poisson sigma s02, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_3_s02 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s02", 
  sym_naka_fun_mu,
  super_poisson_sigma_sym_naka_mu,
  rep(.0000001, 5),
  c(6, 11, .2, 2.5, 0.2))

m_fit_3_3_s02$p
```


```{r sym naka mu super poisson sigma parameters s02, include=FALSE}
m_fit_3_3_s02$p_par
```

#### s03 {.hidden}


```{r sym naka mu super poisson sigma s03, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_3_s03 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s03", 
  sym_naka_fun_mu,
  super_poisson_sigma_sym_naka_mu,
  rep(.0000001, 5),
  c(6, 11, .2, 2.5, 0.2))

m_fit_3_3_s03$p
```


```{r sym naka mu super poisson sigma parameters s03, include=FALSE}
m_fit_3_3_s03$p_par
```


#### s04 {.hidden}

```{r sym naka mu super poisson sigma s04, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_3_s04 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s04", 
  sym_naka_fun_mu,
  super_poisson_sigma_sym_naka_mu,
  rep(.0000001, 5),
  c(6, 11, .2, 2.5, 0.2))

m_fit_3_3_s04$p
```


```{r sym naka mu super poisson sigma parameters s04, include=FALSE}
m_fit_3_3_s04$p_par
```

#### s05 {.hidden}


```{r sym naka mu super poisson sigma s05, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_3_s05 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s05", 
  sym_naka_fun_mu,
  super_poisson_sigma_sym_naka_mu,
  rep(.0000001, 5),
  c(6, 11, .2, 2.5, 0.2))

m_fit_3_3_s05$p
```


```{r sym naka mu super poisson sigma parameters s05, include=FALSE}
m_fit_3_3_s05$p_par
```


#### s06 {.hidden}

```{r sym naka mu super poisson sigma s06, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_3_s06 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s06", 
  sym_naka_fun_mu,
  super_poisson_sigma_sym_naka_mu,
  rep(.0000001, 5),
  c(6, 11, .2, 2.5, 0.2))

m_fit_3_3_s06$p
```

```{r sym naka mu super poisson sigma parameters s06, include=FALSE}
m_fit_3_3_s06$p_par
```

#### s07 {.hidden}

```{r sym naka mu super poisson sigma s07, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_3_s07 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s07", 
  sym_naka_fun_mu,
  super_poisson_sigma_sym_naka_mu,
  rep(.0000001, 5),
  c(6, 11, .2, 2.5, 0.2))

m_fit_3_3_s07$p
```

```{r sym naka mu super poisson sigma parameters s07, include=FALSE}
m_fit_3_3_s07$p_par
```


#### s08 {.hidden}

```{r sym naka mu super poisson sigma s08, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_3_s08 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s08", 
  sym_naka_fun_mu,
  super_poisson_sigma_sym_naka_mu,
  rep(.0000001, 5),
  c(6, 11, .2, 2.5, 0.2))

m_fit_3_3_s08$p
```

```{r sym naka mu super poisson sigma parameters s08, include=FALSE}
m_fit_3_3_s08$p_par
```


#### s09 {.hidden}


```{r sym naka mu super poisson sigma s09, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_3_s09 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s09", 
  sym_naka_fun_mu,
  super_poisson_sigma_sym_naka_mu,
  rep(.0000001, 5),
  c(6, 11, .2, 2.5, 0.2))

m_fit_3_3_s09$p
```


```{r sym naka mu super poisson sigma parameters s09, include=FALSE}
m_fit_3_3_s09$p_par
```



#### s10 {.hidden}


```{r sym naka mu super poisson sigma s10, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_3_s10 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s10",
  sym_naka_fun_mu,
  super_poisson_sigma_sym_naka_mu,
  rep(.0000001, 5),
  c(6, 11, .2, 2.5, 0.2))

m_fit_3_3_s10$p
```

```{r sym naka mu super poisson sigma parameters s10, include=FALSE}
m_fit_3_3_s10$p_par
```


#### s11 {.hidden}

```{r sym naka mu super poisson sigma s11, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_3_s11 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s11", 
  sym_naka_fun_mu,
  super_poisson_sigma_sym_naka_mu,
  rep(.0000001, 5),
  c(6, 11, .2, 2.5, 0.2))

m_fit_3_3_s11$p
```

```{r sym naka mu super poisson sigma parameters s11, include=FALSE}
m_fit_3_3_s11$p_par
```



```{r sym naka mu super poisson sigma fits, include=FALSE}
individual_fits_3_3 <- bind_rows(
  m_fit_3_3_s01$fit,
  m_fit_3_3_s02$fit,
  m_fit_3_3_s03$fit,
  m_fit_3_3_s04$fit,
  m_fit_3_3_s05$fit,
  m_fit_3_3_s06$fit,
  m_fit_3_3_s07$fit,
  m_fit_3_3_s08$fit,
  m_fit_3_3_s09$fit,
  m_fit_3_3_s10$fit,
  m_fit_3_3_s11$fit
)
```

```{r sym naka mu super poisson sigma predictions, include=FALSE}
individual_preds_3_3 <- bind_rows(
  m_fit_3_3_s01$pred,
  m_fit_3_3_s02$pred,
  m_fit_3_3_s03$pred,
  m_fit_3_3_s04$pred,
  m_fit_3_3_s05$pred,
  m_fit_3_3_s06$pred,
  m_fit_3_3_s07$pred,
  m_fit_3_3_s08$pred,
  m_fit_3_3_s09$pred,
  m_fit_3_3_s10$pred,
  m_fit_3_3_s11$pred
)
```


```{r sym naka mu super poisson sigma plot raw data, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_dat, aes(x = c, y = r_norm))+
    geom_line(data = individual_preds_3_3, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1.2)
```


```{r sym naka mu super poisson sigma plot mean, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = individual_preds_3_3, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1) 

```


```{r sym naka mu super poisson sigma sd, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = individual_preds_3_3,
            aes(x = x, y = sigma), color = "navajowhite3", linewidth = 1) +

  
  ylim(0, NA) 

```

```{r sym naka mu super poisson sigma delta, include=FALSE}
ggplot() +
  facet_wrap(vars(participant)) +
  geom_line(data = individual_preds_3_3, 
            aes(x, delta_m), color = "aquamarine4", linewidth = 0.9) 
```

## Model 3_4: 
Symmetric Naka Rushton mu, multiplicative sigma

$$
\sigma = p_4 \cdot \mu + {p_5}
$$

#### s01 {.hidden}
```{r sym naka mu mult sigma s01, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_4_s01 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s01", 
  sym_naka_fun_mu,
  mult_sigma_sym_naka_mu,
  rep(.0000001, 5),
  c(6, 10, .2, 2, 0.4))

m_fit_3_4_s01$p

```

```{r sym naka mu mult sigma parameters s01, include=FALSE}
m_fit_3_4_s01$p_par
```

#### s02 {.hidden}

```{r, sym naka mu mult sigma s02, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_4_s02 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s02", 
  sym_naka_fun_mu,
  mult_sigma_sym_naka_mu,
  rep(.0000001, 5),
  c(6, 10, .2, 2, 0.4))

m_fit_3_4_s02$p
```


```{r sym naka mu mult sigma parameters s02, include=FALSE}
m_fit_3_4_s02$p_par
```

#### s03 {.hidden}


```{r sym naka mu mult sigma s03, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_4_s03 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s03", 
  sym_naka_fun_mu,
  mult_sigma_sym_naka_mu,
  rep(.0000001, 5),
  c(6, 10, .2, 2, 0.4))

m_fit_3_4_s03$p
```


```{r sym naka mu mult sigma parameters s03, include=FALSE}
m_fit_3_4_s03$p_par
```


#### s04 {.hidden}

```{r sym naka mu mult sigma s04, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_4_s04 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s04", 
  sym_naka_fun_mu,
  mult_sigma_sym_naka_mu,
  rep(.0000001, 5),
  c(6, 10, .2, 2, 0.4))

m_fit_3_4_s04$p
```


```{r sym naka mu mult sigma parameters s04, include=FALSE}
m_fit_3_4_s04$p_par
```

#### s05 {.hidden}


```{r sym naka mu mult sigma s05, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_4_s05 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s05", 
  sym_naka_fun_mu,
  mult_sigma_sym_naka_mu,
  rep(.0000001, 5),
  c(6, 10, .2, 2, 0.4))

m_fit_3_4_s05$p
```


```{r sym naka mu mult sigma parameters s05, include=FALSE}
m_fit_3_4_s05$p_par
```


#### s06 {.hidden}

```{r sym naka mu mult sigma s06, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_4_s06 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s06", 
  sym_naka_fun_mu,
  mult_sigma_sym_naka_mu,
  rep(.0000001, 5),
  c(6, 10, .2, 2, 0.4))

m_fit_3_4_s06$p
```

```{r sym naka mu mult sigma parameters s06, include=FALSE}
m_fit_3_4_s06$p_par
```

#### s07 {.hidden}

```{r sym naka mu mult sigma s07, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_4_s07 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s07", 
  sym_naka_fun_mu,
  mult_sigma_sym_naka_mu,
  rep(.0000001, 5),
  c(6, 10, .2, 2, 0.4))

m_fit_3_4_s07$p
```

```{r sym naka mu mult sigma parameters s07, include=FALSE}
m_fit_3_4_s07$p_par
```


#### s08 {.hidden}

```{r sym naka mu mult sigma s08, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_4_s08 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s08", 
  sym_naka_fun_mu,
  mult_sigma_sym_naka_mu,
  rep(.0000001, 5),
  c(6, 10, .2, 2, 0.4))

m_fit_3_4_s08$p
```

```{r sym naka mu mult sigma parameters s08, include=FALSE}
m_fit_3_4_s08$p_par
```


#### s09 {.hidden}


```{r sym naka mu mult sigma s09, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_4_s09 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s09", 
  sym_naka_fun_mu,
  mult_sigma_sym_naka_mu,
  rep(.0000001, 5),
  c(6, 10, .2, 2, 0.4))

m_fit_3_4_s09$p
```


```{r sym naka mu mult sigma parameters s09, include=FALSE}
m_fit_3_4_s09$p_par
```

#### s10 {.hidden}


```{r sym naka mu mult sigma s10, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_4_s10 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s10",
  sym_naka_fun_mu,
  mult_sigma_sym_naka_mu,
  rep(.0000001, 5),
  c(6, 10, .2, 2, 0.4))

m_fit_3_4_s10$p
```

```{r sym naka mu mult sigma parameters s10, include=FALSE}
m_fit_3_4_s10$p_par
```

#### s11 {.hidden}


```{r sym naka mu mult sigma s11, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_4_s11 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s11", 
  sym_naka_fun_mu,
  mult_sigma_sym_naka_mu,
  rep(.0000001, 5),
  c(6, 10, .2, 2, 0.4))

m_fit_3_4_s11$p
```

```{r sym naka mu mult sigma parameters s11, include=FALSE}
m_fit_3_4_s11$p_par
```



```{r sym naka mu mult sigma fits, include=FALSE}
individual_fits_3_4 <- bind_rows(
  m_fit_3_4_s01$fit,
  m_fit_3_4_s02$fit,
  m_fit_3_4_s03$fit,
  m_fit_3_4_s04$fit,
  m_fit_3_4_s05$fit,
  m_fit_3_4_s06$fit,
  m_fit_3_4_s07$fit,
  m_fit_3_4_s08$fit,
  m_fit_3_4_s09$fit,
  m_fit_3_4_s10$fit,
  m_fit_3_4_s11$fit
)
```

```{r sym naka mu mult sigma predictions, include=FALSE}
individual_preds_3_4 <- bind_rows(
  m_fit_3_4_s01$pred,
  m_fit_3_4_s02$pred,
  m_fit_3_4_s03$pred,
  m_fit_3_4_s04$pred,
  m_fit_3_4_s05$pred,
  m_fit_3_4_s06$pred,
  m_fit_3_4_s07$pred,
  m_fit_3_4_s08$pred,
  m_fit_3_4_s09$pred,
  m_fit_3_4_s10$pred,
  m_fit_3_4_s11$pred
)
```


```{r sym naka mu mult sigma plot raw data, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_dat, aes(x = c, y = r_norm))+
    geom_line(data = individual_preds_3_4, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1.2)
```


```{r sym naka mu mult sigma plot mean, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = individual_preds_3_4, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1) 



```


```{r sym naka mu mult sigma sd, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = individual_preds_3_4,
            aes(x = x, y = sigma), color = "navajowhite3", linewidth = 1) +

  
  ylim(0, NA) 

```

```{r sym naka mu mult sigma delta, include=FALSE}
ggplot() +
  facet_wrap(vars(participant)) +
  geom_line(data = individual_preds_3_4, 
            aes(x, delta_m), color = "aquamarine4", linewidth = 0.9) 
```

## Model 3_5: 
Symmetric Naka- Rushton mu, power sigma

$$
\sigma = p_4 \cdot (\mu)^{p_6} + {p_5}
$$


#### s01 {.hidden}

```{r sym naka mu power sigma s01, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_5_s01 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s01", 
  sym_naka_fun_mu,
  power_sigma_sym_naka_mu,
  rep(.0000001, 6),
  c(8, 10, .2, 2, .2, 1.5))

m_fit_3_5_s01$p

```

```{r sym naka mu power sigma parameters s01, include=FALSE}
m_fit_3_5_s01$p_par
```

#### s02 {.hidden}

```{r sym naka mu power sigma s02, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_5_s02 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s02", 
  sym_naka_fun_mu,
  power_sigma_sym_naka_mu,
  rep(.0000001, 6),
  c(8, 10, .2, 2, .2, 1.5))

m_fit_3_5_s02$p
```


```{r sym naka mu power sigma parameters s02, include=FALSE}
m_fit_3_5_s02$p_par
```

#### s03 {.hidden}

```{r sym naka mu power sigma s03, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_5_s03 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s03", 
  sym_naka_fun_mu,
  power_sigma_sym_naka_mu,
  rep(.0000001, 6),
  c(8, 10, .2, 2, .2, 1.5))

m_fit_3_5_s03$p
```


```{r sym naka mu power sigma parameters s03, include=FALSE}
m_fit_3_5_s03$p_par
```

#### s04 {.hidden}

```{r sym naka mu power sigma s04, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_5_s04 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s04", 
  sym_naka_fun_mu,
  power_sigma_sym_naka_mu,
  rep(.0000001, 6),
  c(8, 10, .2, 2, .2, 1.5))

m_fit_3_5_s04$p
```


```{r sym naka mu power sigma parameters s04, include=FALSE}
m_fit_3_5_s04$p_par
```

#### s05 {.hidden}


```{r sym naka mu power sigma s05, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_5_s05 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s05", 
  sym_naka_fun_mu,
  power_sigma_sym_naka_mu,
  rep(.0000001, 6),
  c(8, 10, .2, 2, .2, 1.5))

m_fit_3_5_s05$p
```


```{r sym naka mu power sigma parameters s05, include=FALSE}
m_fit_3_5_s05$p_par
```

#### s06 {.hidden}

```{r sym naka mu power sigma s06, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_5_s06 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s06", 
  sym_naka_fun_mu,
  power_sigma_sym_naka_mu,
  rep(.0000001, 6),
  c(8, 10, .2, 2, .2, 1.5))

m_fit_3_5_s06$p
```

```{r sym naka mu power sigma parameters s06, include=FALSE}
m_fit_3_5_s06$p_par
```

#### s07 {.hidden}

```{r sym naka mu power sigma s07, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_5_s07 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s07", 
  sym_naka_fun_mu,
  power_sigma_sym_naka_mu,
  rep(.0000001, 6),
  c(8, 10, .2, 2, .2, 1.5))

m_fit_3_5_s07$p
```

```{r sym naka mu power sigma parameters s07, include=FALSE}
m_fit_3_5_s07$p_par
```

#### s08 {.hidden}

```{r sym naka mu power sigma s08, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_5_s08 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s08", 
  sym_naka_fun_mu,
  power_sigma_sym_naka_mu,
  rep(.0000001, 6),
  c(8, 10, .2, 2, .2, 1.5))

m_fit_3_5_s08$p
```

```{r sym naka mu power sigma parameters s08, include=FALSE}
m_fit_3_5_s08$p_par
```


#### s09 {.hidden}


```{r sym naka mu power sigma s09, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_5_s09 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s09", 
  sym_naka_fun_mu,
  power_sigma_sym_naka_mu,
  rep(.0000001, 6),
  c(8, 10, .2, 2, .2, 1.5))

m_fit_3_5_s09$p
```


```{r sym naka mu power sigma parameters s09, include=FALSE}
m_fit_3_5_s09$p_par
```

#### s10 {.hidden}


```{r sym naka mu power sigma s10, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_5_s10 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s10",
  sym_naka_fun_mu,
  power_sigma_sym_naka_mu,
  rep(.0000001, 6),
  c(8, 10, .2, 2, .2, 1.5))

m_fit_3_5_s10$p
```

```{r sym naka mu power sigma parameters s10, include=FALSE}
m_fit_3_5_s10$p_par
```

#### s11 {.hidden}


```{r sym naka mu power sigma s11, fig.width=15, fig.height=4, include=FALSE}
m_fit_3_5_s11 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s11", 
  sym_naka_fun_mu,
  power_sigma_sym_naka_mu,
  rep(.0000001, 6),
  c(8, 10, .2, 2, .2, 1.5))

m_fit_3_5_s11$p
```

```{r sym naka mu power sigma parameters s11, include=FALSE}
m_fit_3_5_s11$p_par
```



```{r sym naka mu power sigma fits, include=FALSE}
individual_fits_3_5 <- bind_rows(
  m_fit_3_5_s01$fit,
  m_fit_3_5_s02$fit,
  m_fit_3_5_s03$fit,
  m_fit_3_5_s04$fit,
  m_fit_3_5_s05$fit,
  m_fit_3_5_s06$fit,
  m_fit_3_5_s07$fit,
  m_fit_3_5_s08$fit,
  m_fit_3_5_s09$fit,
  m_fit_3_5_s10$fit,
  m_fit_3_5_s11$fit
)
```

```{r sym naka mu power sigma predictions, include=FALSE}
individual_preds_3_5 <- bind_rows(
  m_fit_3_5_s01$pred,
  m_fit_3_5_s02$pred,
  m_fit_3_5_s03$pred,
  m_fit_3_5_s04$pred,
  m_fit_3_5_s05$pred,
  m_fit_3_5_s06$pred,
  m_fit_3_5_s07$pred,
  m_fit_3_5_s08$pred,
  m_fit_3_5_s09$pred,
  m_fit_3_5_s10$pred,
  m_fit_3_5_s11$pred
)
```


```{r sym naka mu power sigma plot raw data, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_dat, aes(x = c, y = r_norm))+
    geom_line(data = individual_preds_3_5, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1.2)
```


```{r sym naka mu power sigma plot mean, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = individual_preds_3_5, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1) 



```


```{r sym naka mu power sigma sd, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = individual_preds_3_5,
            aes(x = x, y = sigma), color = "navajowhite3", linewidth = 1) +

  
  ylim(0, NA) 

```

```{r sym naka mu power sigma delta, include=FALSE}
ggplot() +
  facet_wrap(vars(participant)) +
  geom_line(data = individual_preds_3_5, 
            aes(x, delta_m), color = "aquamarine4", linewidth = 0.9) 
```
### MODELS:

```{r linear mu all models model 3 fits, include=FALSE}
individual_fits_3 <- bind_rows(
  individual_fits_3_1 |>  mutate(model = "3_1"),
  individual_fits_3_2 |>  mutate(model = "3_2"),
  individual_fits_3_3 |>  mutate(model = "3_3"),
  individual_fits_3_4 |>  mutate(model = "3_4"),
  individual_fits_3_5 |>  mutate(model = "3_5"))
  
```

```{r linealr mu all models model 3 predictions, include=FALSE}
individual_preds_3 <- bind_rows(
  individual_preds_3_1 |>  mutate(model = "3_1"),
  individual_preds_3_2 |>  mutate(model = "3_2"),
  individual_preds_3_3 |>  mutate(model = "3_3"),
  individual_preds_3_4 |>  mutate(model = "3_4"),
  individual_preds_3_5 |>  mutate(model = "3_5"))
```


### Plot models and raw data
```{r linear mu all models model 3 plot raw data, echo=FALSE}
ggplotly(ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_dat, aes(x = c, y = r_norm), alpha = .3) +
    geom_line(data = individual_preds_3, 
              aes(x = x, y = mu, color = model)))
```

### Plot models and mean 
```{r linear mu all models model 3 plot mean, echo=FALSE}
ggplotly(ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = m_norm), alpha = .3) +
    geom_line(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = individual_preds_3, 
              aes(x = x, y = mu, color = model)))
```

### Plot models and standard deviation 
```{r linear mu all models model 3 sd, echo=FALSE}
ggplotly(ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = sta_dev_norm), alpha = .3) +
    geom_line(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = individual_preds_3, 
              aes(x = x, y = sigma, color = model)))
```

### Plot models and delta
```{r linear mu all models model 3 delta, echo=FALSE}
ggplotly(ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_line(data = individual_preds_3, 
              aes(x = x, y = delta_m, color = model)))
```


