---
title: "Untitled"
editor: source
---

POISSON VS MODULATED POISSON WITH SCALAR

#POISSON WITH Q

#### s01 {.hidden}

```{r asym naka mu poisson sigma s01, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_2_s01_1 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s01", 
  asym_naka_fun_mu,
  poisson_sigma_asym_naka_mu_q,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.001), 
  c(40, 10,      .1,  .5,     10, 3))

m_fit_4_2_s01_1$p
```

```{r asym naka mu poisson sigma parameters s01, include=FALSE}
m_fit_4_2_s01_1$p_par
```

#### s02 {.hidden}

<!-- p1 se va mucho -->

```{r asym naka mu poisson sigma s02, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_2_s02_1 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s02", 
  asym_naka_fun_mu,
  poisson_sigma_asym_naka_mu_q,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.0001), 
  c(40, 10,      .1,  .5,     10, 3))

m_fit_4_2_s02_1$p
```

```{r asym naka mu poisson sigma parameters s02, include=FALSE}
m_fit_4_2_s02_1$p_par
```

#### s03 {.hidden}

```{r asym naka mu poisson sigma s03, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_2_s03_1 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s03", 
  asym_naka_fun_mu,
  poisson_sigma_asym_naka_mu_q,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.0001), 
  c(40, 10,      .1,  .5,     10, 3))

m_fit_4_2_s03_1$p
```

```{r asym naka mu poisson sigma parameters s03, include=FALSE}
m_fit_4_2_s03_1$p_par
```

#### s04 {.hidden}

```{r asym naka mu poisson sigma s04, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_2_s04_1 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s04", 
  asym_naka_fun_mu,
  poisson_sigma_asym_naka_mu_q,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.0001), 
  c(40, 10,      .1,  .5,     10, 3))


m_fit_4_2_s04_1$p
```

```{r asym naka mu poisson sigma parameters s04, include=FALSE}
m_fit_4_2_s04_1$p_par
```

#### s05 {.hidden}

```{r asym naka mu poisson sigma s05, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_2_s05_1 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s05", 
  asym_naka_fun_mu,
  poisson_sigma_asym_naka_mu_q,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.0001), 
  c(70, 10,      .1,  .5,     10, 3))

m_fit_4_2_s05_1$p
```

```{r asym naka mu poisson noise parameters s05, include=FALSE}
m_fit_4_2_s05_1$p_par
```

#### s06 {.hidden}

```{r asym naka mu poisson sigma s06, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_2_s06_1 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s06", 
  asym_naka_fun_mu,
  poisson_sigma_asym_naka_mu_q,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.0001), 
  c(40, 10,      .1,  .5,     10, 3))

m_fit_4_2_s06_1$p
```

```{r asym naka mu poisson sigma parameters s06, include=FALSE}
m_fit_4_2_s06_1$p_par
```

#### s07 {.hidden}

```{r asym naka mu poisson sigma s07, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_2_s07_1 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s07", 
  asym_naka_fun_mu,
  poisson_sigma_asym_naka_mu_q,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.0001), 
  c(40, 10,      .1,  .5,     10, 3))

m_fit_4_2_s07_1$p
```

```{r asym naka mu poisson sigma parameters s07, include=FALSE}
m_fit_4_2_s07_1$p_par
```

#### s08 {.hidden}

```{r asym naka mu poisson sigma s08, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_2_s08_1 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s08", 
  asym_naka_fun_mu,
  poisson_sigma_asym_naka_mu_q,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.0001), 
  c(70, 10,      .1,  .5,     10, 3))

m_fit_4_2_s08_1$p
```

```{r asym naka mu poisson sigma parameters s08, include=FALSE}
m_fit_4_2_s08_1$p_par
```

#### s09 {.hidden}

```{r asym naka mu poisson sigma s09, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_2_s09_1 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s09", 
  asym_naka_fun_mu,
  poisson_sigma_asym_naka_mu_q,
  c(2,  .1, .00001,  -1.5,    .0001, 0.0001), 
  c(40, 20,      .1,  .5,     10, 3))

m_fit_4_2_s09_1$p
```

<!-- No soy capaz de poner bien p2 -->

```{r asym naka mu poisson sigma parameters s09, include=FALSE}
m_fit_4_2_s09_1$p_par
```

#### s10 {.hidden}

```{r, asym naka mu poisson sigma s10, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_2_s10_1 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s10", 
  asym_naka_fun_mu,
  poisson_sigma_asym_naka_mu_q,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.0001), 
  c(40, 10,      .1,  .5,     10, 3))

m_fit_4_2_s10_1$p
```

```{r asym naka mu poisson sigma parameters s10, include=FALSE}
m_fit_4_2_s10_1$p_par
```

#### s11 {.hidden}

```{r asym naka mu poisson sigma s11, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_2_s11_1 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s11", 
  asym_naka_fun_mu,
  poisson_sigma_asym_naka_mu_q,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.0001), 
  c(40, 10,      .1,  .5,     10, 3))

m_fit_4_2_s11_1$p
```

```{r asym naka mu poisson sigma parameters s11, include=FALSE}
m_fit_4_2_s11_1$p_par
```

```{r asym naka mu poisson sigma fits, include=FALSE}
individual_fits_4_2_1 <- bind_rows(
  m_fit_4_2_s01_1$fit,
  m_fit_4_2_s02_1$fit,
  m_fit_4_2_s03_1$fit,
  m_fit_4_2_s04_1$fit,
  m_fit_4_2_s05_1$fit,
  m_fit_4_2_s06_1$fit,
  m_fit_4_2_s07_1$fit,
  m_fit_4_2_s08_1$fit,
  m_fit_4_2_s09_1$fit,
  m_fit_4_2_s10_1$fit,
  m_fit_4_2_s11_1$fit
)
```

```{r asym naka mu poisson sigma preds, include=FALSE}
individual_preds_4_2_1 <- bind_rows(
  m_fit_4_2_s01_1$pred,
  m_fit_4_2_s02_1$pred,
  m_fit_4_2_s03_1$pred,
  m_fit_4_2_s04_1$pred,
  m_fit_4_2_s05_1$pred,
  m_fit_4_2_s06_1$pred,
  m_fit_4_2_s07_1$pred,
  m_fit_4_2_s08_1$pred,
  m_fit_4_2_s09_1$pred,
  m_fit_4_2_s10_1$pred,
  m_fit_4_2_s11_1$pred
)
```

```{r asym naka mu poisson sigma plot raw data, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_dat, aes(x = c, y = r_norm))+
    geom_line(data = individual_preds_4_2_1, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1.2)
```

```{r asym naka mu poisson sigma plot mean, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = individual_preds_4_2_1, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1) 



```

```{r asym naka mu poisson sigma sd, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = individual_preds_4_2_1,
            aes(x = x, y = sigma), color = "navajowhite3", linewidth = 1) +

  
  ylim(0, NA) 

```

```{r asym naka mu poisson sigma plot raw data, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_dat, aes(x = c, y = r_norm))+
    geom_line(data = individual_preds_4_2, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1.2)
```


```{r asym naka mu poisson sigma plot mean, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = individual_preds_4_2, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1) 



```


```{r asym naka mu poisson sigma sd, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = individual_preds_4_2,
            aes(x = x, y = sigma), color = "navajowhite3", linewidth = 1) +

  
  ylim(0, NA) 

```

```{r asym naka mu poisson sigma delta, include=FALSE}
ggplot() +
  facet_wrap(vars(participant)) +
  geom_line(data = individual_preds_4_2, 
            aes(x, delta_m), color = "aquamarine4", linewidth = 0.9) 
```
JUSTO MODULATED POISSON

## Model 4_3:

Asymmetric Naka- Rushton mu, super poisson sigma 
$$
\sigma = \sqrt{\mu + (p_5 \mu)^2} + p_6
$$



MODULATED POISSON WITH G

## Model 4_3:

Asymmetric Naka- Rushton mu, super poisson sigma 
$$
\sigma = \sqrt{\mu + (p_5 \mu)^2} + p_6
$$

#### s01 {.hidden}

```{r asym naka mu super poisson sigma s01, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_3_s01_1 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s01", 
  asym_naka_fun_mu,
  super_poisson_sigma_asym_naka_mu_q,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.00001, 0.0001),
  c(40, 10,      .1,  .5,     10, 0.3, 4))

m_fit_4_3_s01_1$p

```

```{r asym naka mu super poisson sigma parameters s01, include=FALSE}
m_fit_4_3_s01_1$p_par
```

#### s02 {.hidden}

```{r asym naka mu super poisson sigma s02, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_3_s02_1 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s02", 
  asym_naka_fun_mu,
  super_poisson_sigma_asym_naka_mu_q,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.00001, 0.0001),
  c(40, 10,      .1,  .5,     10, 0.3, 4))

m_fit_4_3_s02_1$p
```

```{r asym naka mu super poisson sigma parameters s02, include=FALSE}
m_fit_4_3_s02_1$p_par
```

#### s03 {.hidden}

```{r asym naka mu super poisson sigma s03, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_3_s03_1 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s03", 
  asym_naka_fun_mu,
  super_poisson_sigma_asym_naka_mu_q,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.00001, 0.0001),
  c(40, 10,      .1,  .5,     10, 0.3, 4))

m_fit_4_3_s03_1$p
```

```{r asym naka mu super poisson sigma parameters s03, include=FALSE}
m_fit_4_3_s03_1$p_par
```

#### s04 {.hidden}

```{r asym naka mu super poisson sigma s04, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_3_s04_1 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s04", 
  asym_naka_fun_mu,
  super_poisson_sigma_asym_naka_mu_q,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.00001, 0.0001),
  c(40, 10,      .1,  .5,     10, 0.3, 4))

m_fit_4_3_s04_1$p
```

```{r asym naka mu super poisson sigma parameters s04, include=FALSE}
m_fit_4_3_s04_1$p_par
```

#### s05 {.hidden}

```{r asym naka mu super poisson sigma s05, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_3_s05_1 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s05", 
  asym_naka_fun_mu,
  super_poisson_sigma_asym_naka_mu_q,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.00001, 0.0001),
  c(50, 10,      .1,  .5,     10, 0.3, 4))

m_fit_4_3_s05_1$p
```

```{r asym naka mu super poisson sigma parameters s05, include=FALSE}
m_fit_4_3_s05_1$p_par
```

#### s06 {.hidden}

```{r asym naka mu super poisson sigma s06, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_3_s06_1 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s06", 
  asym_naka_fun_mu,
  super_poisson_sigma_asym_naka_mu_q,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.00001, 0.0001),
  c(40, 10,      .1,  .5,     10, 0.3, 4))

m_fit_4_3_s06_1$p
```

```{r asym naka mu super poisson sigma parameters s06, include=FALSE}
m_fit_4_3_s06_1$p_par
```

#### s07 {.hidden}

```{r, asym naka mu super poisson sigma s07, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_3_s07_1 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s07", 
  asym_naka_fun_mu,
  super_poisson_sigma_asym_naka_mu_q,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.00001, 0.0001),
  c(40, 10,      .1,  .5,     10, 0.3, 4))

m_fit_4_3_s07_1$p
```

```{r asym naka mu super poisson sigma parameters s07, include=FALSE}
m_fit_4_3_s07_1$p_par
```

#### s08 {.hidden}

```{r asym naka mu super poisson sigma s08, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_3_s08_1 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s08", 
  asym_naka_fun_mu,
  super_poisson_sigma_asym_naka_mu_q,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.00001, 0.0001),
  c(50, 10,      .1,  .5,     10, 0.3, 4))

m_fit_4_3_s08_1$p
```

```{r asym naka mu super poisson sigma parameters s08, include=FALSE}
m_fit_4_3_s08_1$p_par
```

#### s09 {.hidden}

```{r asym naka mu super poisson sigma s09, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_3_s09_1 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s09", 
  asym_naka_fun_mu,
  super_poisson_sigma_asym_naka_mu_q,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.00001, 0.0001),
  c(40, 10,      .1,  .5,     10, 0.3, 4))

m_fit_4_3_s09_1$p
```

```{r asym naka mu super poisson sigma parameters s09, include=FALSE}
m_fit_4_3_s09_1$p_par
```

#### s10 {.hidden}

```{r asym naka mu super poisson sigma s10, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_3_s10_1 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s10",
  asym_naka_fun_mu,
  super_poisson_sigma_asym_naka_mu_q,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.00001, 0.0001),
  c(40, 10,      .1,  .5,     10, 0.3, 4))

m_fit_4_3_s10_1$p
```

```{r asym naka mu super poisson sigma parameters s10, include=FALSE}
m_fit_4_3_s10_1$p_par
```

#### s11 {.hidden}

```{r asym naka mu super poisson sigma s11, fig.width=15, fig.height=4, include=FALSE}
m_fit_4_3_s11_1 <- fit_m_ind_fun(
  m_dat, 
  m_summ_bin,
  "s11", 
  asym_naka_fun_mu,
  super_poisson_sigma_asym_naka_mu_q,
  c(2,  1.5, .00001,  -1.5,    .0001, 0.00001, 0.0001),
  c(40, 10,      .1,  .5,     10, 0.3, 4))

m_fit_4_3_s11_1$p
```

```{r asym naka mu super poisson sigma parameters s11, include=FALSE}
m_fit_4_3_s11_1$p_par
```

```{r asym naka mu super poisson sigma fits, include=FALSE}
individual_fits_4_3_1 <- bind_rows(
  m_fit_4_3_s01_1$fit,
  m_fit_4_3_s02_1$fit,
  m_fit_4_3_s03_1$fit,
  m_fit_4_3_s04_1$fit,
  m_fit_4_3_s05_1$fit,
  m_fit_4_3_s06_1$fit,
  m_fit_4_3_s07_1$fit,
  m_fit_4_3_s08_1$fit,
  m_fit_4_3_s09_1$fit,
  m_fit_4_3_s10_1$fit,
  m_fit_4_3_s11_1$fit
)
```

```{r asym naka mu super poisson sigma preds, include=FALSE}
individual_preds_4_3_1 <- bind_rows(
  m_fit_4_3_s01_1$pred,
  m_fit_4_3_s02_1$pred,
  m_fit_4_3_s03_1$pred,
  m_fit_4_3_s04_1$pred,
  m_fit_4_3_s05_1$pred,
  m_fit_4_3_s06_1$pred,
  m_fit_4_3_s07_1$pred,
  m_fit_4_3_s08_1$pred,
  m_fit_4_3_s09_1$pred,
  m_fit_4_3_s10_1$pred,
  m_fit_4_3_s11_1$pred
)
```

```{r asym naka mu super poisson sigma plot raw data, include=FALSE}
ggplot() + 
  facet_wrap(vars(participant), scales= "free") +
    geom_point(data = m_dat, aes(x = c, y = r_norm))+
    geom_line(data = individual_preds_4_3_1, 
              aes(x = x, y = mu), color = "aquamarine4", linewidth = 1.2)
```

```{r asym naka mu super poisson sigma plot mean, include=FALSE}
ggplotly(ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = m_norm)) +
    geom_line(data = individual_preds_4_3_1, 
              aes(x = x, y = mu, color = "modulated and q"),linewidth = 1) +
  geom_line(data = individual_preds_4_2_1, 
              aes(x = x, y = mu, color = "poisson and q"), linewidth = 1) +
  geom_line(data = individual_preds_4_2, 
              aes(x = x, y = mu, color = "possion"),linewidth = 1) +
  geom_line(data = individual_preds_4_3, 
              aes(x = x, y = mu, color = "modulated poisson"), linewidth = 1) +
    geom_line(data = individual_preds_4_5, 
              aes(x = x, y = mu, color = "power"), linewidth = 1))
  



```

```{r asym naka mu super poisson sigma sd, include=FALSE}
ggplotly(ggplot() + 
  facet_wrap(vars(participant), scales = "free") +
    geom_point(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = m_summ_bin, aes(x = c, y = sta_dev_norm)) +
    geom_line(data = individual_preds_4_3_1, 
              aes(x = x, y = sigma, color = "modulated and q"),linewidth = 1) +
  geom_line(data = individual_preds_4_2_1, 
              aes(x = x, y = sigma, color = "poisson and q"), linewidth = 1) +
  geom_line(data = individual_preds_4_2, 
              aes(x = x, y = sigma, color = "possion"),linewidth = 1) +
  geom_line(data = individual_preds_4_3, 
              aes(x = x, y = sigma, color = "modulated poisson"), linewidth = 1) +
    geom_line(data = individual_preds_4_5, 
              aes(x = x, y = sigma, color = "power"), linewidth = 1) +

  
  ylim(0, NA) )

```

```{r asym naka mu super poisson sigma delta, include=FALSE}
ggplot() +
  facet_wrap(vars(participant)) +
  geom_line(data = individual_preds_4_3_1, 
            aes(x, delta_m), color = "aquamarine4", linewidth = 0.9) +
  geom_line(data = individual_preds_4_5, 
            aes(x, delta_m), color = "red", linewidth = 0.9) 
```

```{r}
individual_test <- bind_rows(
  individual_fits_4_2 |> mutate(model = "poisson"),
  individual_fits_4_2_1 |> mutate(model = "poisson q"),
  individual_fits_4_3 |> mutate(model = "modulated"),
  individual_fits_4_3_1 |> mutate(model = "modulated q"),
  individual_fits_4_5 |> mutate(model = "power"))
```

```{r}
ggplotly(ggplot() +
  facet_wrap(vars(participant), scales = "free") +
  geom_point(data = individual_test,
             aes(x = "AIC", y = AIC, color = model))) 
  
```

```{r}
individual_test |> group_by(participant) |> slice_min(AIC)
```
