---
title: "Deltas comparison"
format: html
editor: source
---


## Delta from magnitude estimation:

Delta measured as: 
$$
\Large \delta =\frac{\mu'(x)}{\sigma(x)}
$$
Where mu' is the derivative of the mu and sigma is the standard deviation of the noise.

From the model 4_5

Asymmetric Naka- Rushton mu 
$$
\mu = \frac{p_1 \cdot x^{p_2}}{x^{p_2 + p_4} + p_3^{p_2 + p_4}}
$$

power sigma

$$
\sigma = p_5 \cdot (\mu)^{p_7} + {p_6}
$$


```{r plot delta me, echo=FALSE}
m_delta <- individual_preds_4_5

m_delta |> 
  ggplot() +
  facet_wrap(vars(participant)) +
  geom_line(aes(x, delta_m), color = "aquamarine4", linewidth = 0.9)
```
Log
```{r plot delta log me, echo=FALSE}
m_der_delta_log <- m_delta |> 
         mutate(der_m = c(NA, diff(delta_m_log) / diff(x_log))) |> 
  group_by(participant) |> 
  slice_tail(n = 1) 

m_delta |> 
  ggplot(aes(x_log, delta_m_log)) +
  facet_wrap(vars(participant)) +
  geom_line(color = "aquamarine4", linewidth = 0.9) 

```


## Delta from discrimination: 

```{r delta from discrimination, include=FALSE}
d_delta <- d_delta_asym|> 
  rename(delta_d = delta) |> 
  mutate(x_log = log10(x),
         delta_d_log = log10(delta_d))
```


```{r plot delta from discrimination, echo=FALSE}
  ggplot() +
  facet_wrap(vars(participant)) +
  geom_line(data= d_delta, aes(x, delta_d), color = "darkorchid4", linewidth = 0.9)
```
Log
```{r plot delta discrimination log, echo=FALSE}
d_delta_log <- d_delta |> 
  mutate(der_d = c(NA, diff(delta_d_log) / diff(x_log))) |> 
  group_by(participant) |> 
  slice_tail(n = 1) 


d_delta |> 
  ggplot(aes(x_log, delta_d_log)) +
  facet_wrap(vars(participant)) +
  geom_line(color = "darkorchid4", linewidth = 0.9)
```


## Deltas comparison
Plot of the deltas together by participant:

```{r plot deltas together, echo=FALSE}
ggplot() +
  geom_line(data = m_delta, aes(x, delta_m), color = "aquamarine4", linewidth = 0.9) +
  facet_wrap(vars(participant)) +
  geom_line(data = d_delta, aes(x, delta_d), color = "darkorchid4", linewidth = 0.9)
```

Log
```{r plot deltas together log, echo=FALSE}
ggplot() +
  geom_line(data = m_delta, aes(x_log, delta_m_log), color = "aquamarine4", linewidth = 0.9) +
  facet_wrap(vars(participant), scales = "free") +
  geom_line(data = d_delta, aes(x_log, delta_d_log), color = "darkorchid4", linewidth = 0.9) 
    #geom_abline(data =  d_delta_log, aes(intercept =delta_d_log - der_d * x_log , slope = der_d), color = "red", linetype = "dashed", size = 1) +
    #geom_abline(data =  m_delta_log, aes(intercept =delta_m_log - der_m * x_log , slope = der_m), color = "blue", linetype = "dashed", size = 1)+

  
```


### Analysis:

#### Contrast at max sensitivy

Correlation of the contrast at which the sensitivity is higher by participant:
```{r correlation contrast max, include=FALSE}
max_c_m <- m_delta |>
  slice_max(delta_m) |> rename(c_max_m = x)


max_c_d <- d_delta |> 
  filter(delta_d == max(delta_d)) |> rename(c_max_d = x)

 
c_combined <- left_join(max_c_m, max_c_d, by = "participant")

shapiro.test(max_c_m$c_max_m)
shapiro.test(max_c_d$c_max_d)

c_combined |> 
  ggplot()+
  geom_point(aes(x = c_max_m, y = 1), size = 3, alpha = 0.7) +
  geom_point(aes(x = c_max_d, y = .5), size = 3, alpha = 0.7)

```

```{r correlationt tests at which contrast max, echo=FALSE}

cor.test(c_combined$c_max_d, 
                    c_combined$c_max_m)

correlationBF(c_combined$c_max_d, 
                    c_combined$c_max_m)

ttestBF(c_combined$c_max_d, 
          c_combined$c_max_m, paired = TRUE)

t.test(c_combined$c_max_d, c_combined$c_max_m, paired = TRUE)
```

Plot means contrast at max sensitivity
```{r plot means contrast max, echo=FALSE}
c_combined |> 
  pivot_longer(cols = c(c_max_d, c_max_m), names_to = "model", values_to = "contrast") |> 
  group_by(model) |> 
  summarise(calculate_t_ci(contrast)) |> 
  ggplot(aes(x = model, y = estimate, color=model)) +
  geom_point(data = c_combined |> 
               pivot_longer(cols = c(c_max_d, c_max_m), names_to = "model", values_to = "contrast"), 
             aes(x = model, y = contrast, color=model), alpha = 0.8) +
  geom_line(data = c_combined |> 
               pivot_longer(cols = c(c_max_d, c_max_m), names_to = "model", values_to = "contrast"), 
             aes(x = model, y = contrast, group = participant, color=model), color = "gray70", alpha = 0.8) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  scale_color_manual(values = c(
    "c_max_d" = "darkorchid4",
    "c_max_m" = "aquamarine4"
  )) +
  ylab("Position") +
  xlab("Model")

```

Linear regression:
```{r linear regresion contrast max, echo=FALSE}
lm_c_max <- lm(c_max_m ~ c_max_d, data = c_combined)
lm_c_max

linearHypothesis(lm_c_max, "(Intercept) = 0")

linearHypothesis(lm_c_max, "c_max_d = 1")

```

Plot of the correlation:
```{r plot contrast max, echo=FALSE}
c_combined |> 
  ggplot()+
  geom_point(aes(x = c_max_d, y = c_max_m, color = as_factor(participant))) +
  coord_equal() +
  geom_abline(slope = 1, intercept = 0) +
  geom_abline(slope = lm_c_max$coefficients[2], intercept = lm_c_max$coefficients[1], linetype = "dashed") +
  xlim(-.01, .04) +
  ylim(-.01, .04) +
  xlab("Position D") +
  ylab("Position M")
``` 


#### Contrast at max sensitivy log


```{r correlacion max contrast log, include=FALSE}
max_c_m_log <- m_delta |>
  slice_max(delta_m_log) |> rename(c_max_m_log = x_log)


max_c_d_log <- d_delta |> 
  filter(delta_d_log == max(delta_d_log)) |> rename(c_max_d_log = x_log) 

  
c_combined_log <- left_join(max_c_m_log, max_c_d_log, by = "participant")

shapiro.test(max_c_m_log$c_max_m_log)
shapiro.test(max_c_d_log$c_max_d_log)

c_combined_log |> 
  ggplot()+
  geom_point(aes(x = c_max_m_log, y = 1),  size = 3, alpha = 0.7) +
  geom_point(aes(x = c_max_d_log, y = .5), size = 3, alpha = 0.7)

```


```{r test correlacion contrast max log, echo=FALSE}
cor.test(c_combined_log$c_max_d_log, 
                    c_combined_log$c_max_m_log)

correlationBF(c_combined_log$c_max_d_log, 
                    c_combined_log$c_max_m_log)


ttestBF(c_combined_log$c_max_d_log, 
                    c_combined_log$c_max_m_log, paired = TRUE)
t.test(c_combined_log$c_max_d_log, c_combined_log$c_max_m_log, paired = TRUE)
```

Plot means contrast at max sensitivity log
```{r plot means contrast max log, echo=FALSE}
c_combined_log |> 
  pivot_longer(cols = c(c_max_d_log, c_max_m_log), names_to = "model", values_to = "contrast") |> 
  group_by(model) |> 
  summarise(calculate_t_ci(contrast)) |> 
  ggplot(aes(x = model, y = estimate, color=model)) +
    geom_point(size = 3) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  geom_point(data = c_combined_log |> 
               pivot_longer(cols = c(c_max_d_log, c_max_m_log), names_to = "model", values_to = "contrast"), 
             aes(x = model, y = contrast, color=model), alpha = 0.8) +
  geom_line(data = c_combined_log |> 
               pivot_longer(cols = c(c_max_d_log, c_max_m_log), names_to = "model", values_to = "contrast"), 
             aes(x = model, y = contrast, group = participant, color=model), color = "gray70", alpha = 0.8) +
  scale_color_manual(values = c(
    "c_max_d_log" = "darkorchid4",
    "c_max_m_log" = "aquamarine4"
  )) +
  ylab("Position") +
  xlab("Model")

```

Linear Regresion 
```{r linrear regression contrast max log, echo=FALSE}
lm_c_max_log <- lm(c_max_m_log ~ c_max_d_log, data = c_combined_log)
lm_c_max_log

linearHypothesis(lm_c_max_log, "(Intercept) = 0")

linearHypothesis(lm_c_max_log, "c_max_d_log = 1")

``` 


Plot of log correlation:

```{r c combine log, echo=FALSE}
c_combined_log |> 
  ggplot()+
  geom_point(aes(x = c_max_d_log, y = c_max_m_log, color = as_factor(participant))) +
  coord_equal() +
  geom_abline(slope = 1, intercept = 0) +
  geom_abline(slope = lm_c_max_log$coefficients[2], intercept = lm_c_max_log$coefficients[1], linetype = "dashed") +
  xlab("Position D") +
  ylab("Position M")
```




#### Max sensitivy

Correlation of higher sensitivity by participant:
```{r correlacion of max sensitivity, include=FALSE}
max_m <- m_delta |> 
  group_by(participant) |> 
  summarise(max_m = max(delta_m, na.rm = TRUE)) 


max_d <- d_delta |> 
  group_by(participant) |> 
  summarise(max_d = max(delta_d, na.rm = TRUE)) 


max_combined <- left_join(max_m, max_d, by = "participant")

shapiro.test(max_m$max_m)
shapiro.test(max_d$max_d)

max_combined  |> 
  ggplot()+
  geom_point(aes(x = max_m, y = 1), size = 3, alpha = 0.7) +
  geom_point(aes(x = max_d, y = .5), size = 3, alpha = 0.7)

```

```{r test correlation max sensitivity, echo=FALSE}

cor.test(max_combined$max_m, 
                    max_combined$max_d)

correlationBF(max_combined$max_m, 
                    max_combined$max_d)

ttestBF(max_combined$max_m, 
                    max_combined$max_d, paired = TRUE)

t.test(max_combined$max_m, max_combined$max_d, paired = TRUE)
```

Plot means at max sensitivity 
```{r plot means max, echo=FALSE}
max_combined |> 
  pivot_longer(cols = c(max_d, max_m), names_to = "model", values_to = "contrast") |> 
  group_by(model) |> 
  summarise(calculate_t_ci(contrast)) |> 
  ggplot(aes(x = model, y = estimate, color=model)) +
    geom_point(size = 3) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  geom_point(data = max_combined |> 
               pivot_longer(cols = c(max_d, max_m), names_to = "model", values_to = "contrast"), 
             aes(x = model, y = contrast, color=model), alpha = 0.8) +
  geom_line(data = max_combined |> 
               pivot_longer(cols = c(max_d, max_m), names_to = "model", values_to = "contrast"), 
             aes(x = model, y = contrast, group = participant, color=model), color = "gray70", alpha = 0.8) +
  scale_color_manual(values = c(
    "max_d" = "darkorchid4",
    "max_m" = "aquamarine4"
  )) +
  ylab("Amplitude") +
  xlab("Model")

```


Linear regression:
```{r linear regression max sensitivity, echo=FALSE}
lm_max <- lm(max_m ~ max_d, data = max_combined)
lm_max

linearHypothesis(lm_max, "(Intercept) = 0")

linearHypothesis(lm_max, "max_d = 1")

```

Plot of the correlation:
```{r plot max sensitivity, echo=FALSE}
max_combined |> 
  ggplot()+
  geom_point(aes(x = max_d, y = max_m, color = as_factor(participant))) +
  coord_equal() +
  geom_abline() +
  geom_abline(slope = lm_max$coefficients[2], intercept = lm_max$coefficients[1], linetype = "dashed") +
  xlab("Max Sensitivity D") +
  ylab("Max Sensitivity M")
```

#### Max sensitivity log
```{r correlacion max sensitivity log, include=FALSE}
max_m_log <- m_delta |> 
  group_by(participant) |> 
  summarise(max_m_log = max(delta_m_log, na.rm = TRUE)) 

max_d_log <- d_delta |> 
  group_by(participant) |> 
  summarise(max_d_log = max(delta_d_log, na.rm = TRUE))

max_combined_log <- left_join(max_m_log, max_d_log, by = "participant")

shapiro.test(max_m_log$max_m_log)
shapiro.test(max_d_log$max_d_log)

max_combined_log  |> 
  ggplot()+
  geom_point(aes(x = max_m_log, y = 1), size = 3, alpha = 0.7) +
  geom_point(aes(x = max_d_log, y = .5), size = 3, alpha = 0.7)

```

```{r test correlation max sensitivity log, echo=FALSE}
cor.test(max_combined_log$max_m_log, 
                    max_combined_log$max_d_log)

correlationBF(max_combined_log$max_m_log, 
                    max_combined_log$max_d_log)

ttestBF(max_combined_log$max_m_log, 
                    max_combined_log$max_d_log, paired = TRUE)
t.test(max_combined_log$max_m_log, max_combined_log$max_d_log, paired = TRUE)
```

Plot means at max sensitivity log
```{r plot means max log, echo=FALSE}
max_combined_log |> 
  pivot_longer(cols = c(max_d_log, max_m_log), names_to = "model", values_to = "contrast") |> 
  group_by(model) |> 
  summarise(calculate_t_ci(contrast)) |> 
  ggplot(aes(x = model, y = estimate, color=model)) +
    geom_point(size = 3) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  geom_point(data = max_combined_log|> 
               pivot_longer(cols = c(max_d_log, max_m_log), names_to = "model", values_to = "contrast"), 
             aes(x = model, y = contrast, color=model), alpha = 0.8) +
  geom_line(data = max_combined_log |> 
               pivot_longer(cols = c(max_d_log, max_m_log), names_to = "model", values_to = "contrast"), 
             aes(x = model, y = contrast, group = participant, color=model), color = "gray70", alpha = 0.8) +
  scale_color_manual(values = c(
    "max_d_log" = "darkorchid4",
    "max_m_log" = "aquamarine4"
  )) +
  ylab("Amplitude") +
  xlab("Model")

```

Linear regression 
```{r linear regression max sensitivity log, echo=FALSE}
lm_max_log <- lm(max_m_log ~ max_d_log, data = max_combined_log)
lm_max_log

linearHypothesis(lm_max_log, "(Intercept) = 0")

linearHypothesis(lm_max_log, "max_d_log = 1")
```

Plot of the correlation:
```{r plot max sensitivity log, echo=FALSE}
max_combined_log |> 
  ggplot()+
  geom_point(aes(x = max_d_log, y = max_m_log, color = as_factor(participant))) +
  coord_equal() +
  geom_abline() +
  geom_abline(slope = lm_max_log$coefficients[2], intercept = lm_max_log$coefficients[1], linetype = "dashed") +
  xlab("Max Sensitivity D") +
  ylab("Max Sensitivity M")
```


#### Derivative of the log deltas at the higher contrast 
(Weber's law)


```{r correlacion der log deltas, echo=FALSE}
c_combined_der <- left_join(d_delta_log, m_der_delta_log, by = "participant")

cor.test(c_combined_der$der_m, 
                    c_combined_der$der_d)
correlationBF(c_combined_der$der_m, 
                    c_combined_der$der_d)

ttestBF(c_combined_der$der_m, 
                    c_combined_der$der_d, paired = TRUE)

t.test(c_combined_der$der_m, c_combined_der$der_d, paired = TRUE)
```

Plot means of the derivative of the log deltas
```{r plot der log, echo=FALSE}
c_combined_der |> 
  pivot_longer(cols = c(der_d, der_m), names_to = "model", values_to = "contrast") |> 
  group_by(model) |> 
  summarise(calculate_t_ci(contrast)) |> 
  ggplot(aes(x = model, y = estimate, color=model)) +
    geom_point(size = 3) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  geom_point(data = c_combined_der |> 
               pivot_longer(cols = c(der_d, der_m), names_to = "model", values_to = "contrast"), 
             aes(x = model, y = contrast, color=model), alpha = 0.8) +
  geom_line(data = c_combined_der |> 
               pivot_longer(cols = c(der_d, der_m), names_to = "model", values_to = "contrast"), 
             aes(x = model, y = contrast, group = participant, color=model), color = "gray70", alpha = 0.8) +
  scale_color_manual(values = c(
    "der_d" = "darkorchid4",
    "der_m" = "aquamarine4"
  )) +
  ylab("Der") +
  xlab("Model")

```

Linear regression:
```{r linear regression der log deltas, echo=FALSE}
lm_der <- lm(der_m ~ der_d, data = c_combined_der)
lm_der

linearHypothesis(lm_der, "(Intercept) = 0")

linearHypothesis(lm_der, "der_d = 1")

```

Plot of the correlation:
```{r plot der log deltas, echo=FALSE}
c_combined_der |> 
  ggplot()+
  geom_point(aes(x = der_d, y = der_m, color = as_factor(participant))) +
  coord_equal() +
  geom_abline() +
  geom_abline(slope = lm_der$coefficients[2], intercept = lm_der$coefficients[1], linetype = "dashed") +
  xlab("Der D") +
  ylab("Der M")
```

#### Mean Sensitivity:
```{r mean sensitivity, include=FALSE}
mean_m <- m_delta |> 
  group_by(participant) |> 
  summarise(mean_m = mean(delta_m, na.rm = TRUE))

mean_d <- d_delta |> 
  group_by(participant) |> 
  summarise(mean_d = mean(delta_d, na.rm = TRUE))
mean_combined <- left_join(mean_m, mean_d, by = "participant")

```

## Correlation of the delta curves intra subjects: {.hidden}

```{r correlation of the delta curves, include=FALSE}
common_grid <- seq(
  min(c(d_delta$x, m_delta$x)), 
  max(c(d_delta$x, m_delta$x)), 
  length.out = 200
)

interp_d <- d_delta |> 
  group_by(participant) |> 
  summarise(
    sens_d = list(approx(x, delta_d, xout = common_grid)$y),
    .groups = "drop"
  )


interp_m <- m_delta |> 
  group_by(participant) |> 
  summarise(
    sens_m = list(approx(x, delta_m, xout = common_grid)$y),
    .groups = "drop"
  )


deltas <- interp_d |> 
  inner_join(interp_m, by = "participant")


cor_suj <- deltas|> 
  mutate(cor = map2_dbl(sens_d, sens_m, ~ cor(.x, .y, use = "complete.obs"))) |> 
  ungroup()

cor_suj

```

```{r test correlation of the deltas, include=FALSE}
t.test(cor_suj$cor, mu = 0) 
```


```{r plot all participants bad, include=FALSE}
ggplot()+
  geom_line(data = d_delta |> group_by(x) |> 
              summarise(calculate_t_ci(delta_d)), aes(x, estimate),  color = "darkorchid4") +
  geom_line(data = m_delta |> 
              drop_na() |> 
              group_by(x) |> 
              summarise(calculate_t_ci(delta_m)), aes(x, estimate), color = "aquamarine4") +
  geom_ribbon(data = d_delta |> group_by(x) |> 
                summarise(calculate_t_ci(delta_d)), aes(x, ymin = conf.low, ymax = conf.high), fill = "darkorchid4", alpha = 0.4) +
  geom_ribbon(data = m_delta |> 
                drop_na() |> 
                group_by(x) |> 
                summarise(calculate_t_ci(delta_m)), aes(x, ymin = conf.low, ymax = conf.high),, fill = "aquamarine4", alpha = 0.4)
```

```{r plot confidence interval of deltas all participnts, include=FALSE}

d_delta_all <- d_delta |> 
  select(participant, x, delta_d)

m_delta_all <- m_delta |> 
  select(participant, x, delta_m)


deltas <- d_delta_all |> 
  inner_join(m_delta_all, by = c("participant", "x"))

sum_deltas <- deltas |> 
  drop_na() |> 
  pivot_longer(cols = c(delta_m, delta_d), names_to = c("model"), values_to = "deltas") |>
  group_by(model, x) |> 
  summarise(
    calculate_t_ci(deltas)
  )
  
```


```{r funtion to calculate t test, include=FALSE}
calculate_t_test <- function(.x, .y) {
  ci <- t.test(.x, .y, paired = TRUE) |> 
    tidy() |> 
    select(p.value)
  
  ci
}
```


```{r t test of deltas all participants, include=FALSE}
xx <- deltas |> 
  drop_na() |>
  ungroup() |> 
  group_by(x) |> 
  summarise(t_test=calculate_t_test(delta_d, delta_m)) |> 
  unnest(t_test) |> 
  mutate(sig = if_else(p.value < 0.05, "yes", "no"))


xx
```


## Deltas of all participants together:

```{r plot confidence interval of deltas all participnts with t test, echo=FALSE}
ggplotly(ggplot(sum_deltas) +
  geom_line(aes(x, estimate, color = model), linewidth = 1) +
  geom_ribbon(aes(x, ymin = conf.low, ymax = conf.high, fill = model), alpha = 0.4) +
  #geom_line(data = threshold_logistic_all, aes(x = c_pedestal, y = delta), color = "black", linetype = "dashed", size = 1) +
  scale_color_manual(values = c("darkorchid4", "aquamarine4")) +
  scale_fill_manual(values = c("darkorchid4", "aquamarine4")) +
  geom_segment(
  data = filter(xx, sig == "yes"),
  aes(
    x = x,
    xend = x,
    y = 0,     # límite inferior
    yend = 5   # límite superior
  ),
  color = "grey"
))
```





