---
title: "Untitled"
editor: source
---


```{r}
linear_mu <- quote(k*x)
power_mu<- quote(k*x^alpha)
sym_naka_mu <- quote(k*x^beta / nu^beta+x^beta)
asym_naka_mu <- quote(k*x^beta / nu^{beta-alpha} + x^{beta-alpha})

ad_sigma <- quote(sigma[0])
poisson_sigma <- quote(sigma[0] + mu^0.5)
poisson_sigma_escalar <- quote(sigma[0] + q*mu^0.5)
modulated_poisson_sigma <- quote(sigma[0] + sqrt(mu + g^2*mu))
modulated_poisson_sigma_escalar <- quote(sigma[0] + q*sqrt(mu + g^2*mu))
mult_sigma <- quote(sigma[0] + q*mu)
power_sigma <- quote(sigma[0] + q*mu^gamma)
```

#Linear models: 
##constant sigma

```{r}

p_1_1 <- plot_suplementary_model(individual_fits_1_1) +
  labs(title = bquote(mu == .(linear_mu) ~ "," ~ sigma == .(ad_sigma)))
p_1_1

```

##Poisson sigma

```{r}

p_1_2 <- plot_suplementary_model(individual_fits_1_2) +
  labs(title = bquote(mu == .(linear_mu) ~ "," ~ sigma == .(poisson_sigma)))
p_1_2
```

##Modulated Poisson sigma

```{r}
p_1_3 <-plot_suplementary_model(individual_fits_1_3) +
  labs(title = bquote(mu == .(linear_mu) ~ "," ~ sigma == .(modulated_poisson_sigma)))
p_1_3
```

##Multiplicative sigma

```{r}
p_1_4 <-plot_suplementary_model(individual_fits_1_4) +
  labs(title = bquote(mu == .(linear_mu) ~ "," ~ sigma == .(mult_sigma)))
p_1_4
```

##Power sigma

```{r}
p_1_5 <-plot_suplementary_model(individual_fits_1_5) +
  labs(title = bquote(mu == .(linear_mu) ~ "," ~ sigma == .(power_sigma)))
p_1_5
```

Graph

```{r}
p_1 <- plot_grid(p_1_1, p_1_2, p_1_3, p_1_4, p_1_5,
          nrow = 5,
          labels = c("A", "B", "C", "D", "E"),
          label_size = 10)

ggsave("figures/p_1.pdf", p_1, width = 7.5, height = 8.5)
```

#Power model 
##constant sigma

```{r}
p_2_1 <- plot_suplementary_model(individual_fits_2_1) +
  labs(title = bquote(mu == .(power_mu) ~ "," ~ sigma == .(ad_sigma)))
p_2_1

```

##Poisson sigma

```{r}
p_2_2 <- plot_suplementary_model(individual_fits_2_2) +
  labs(title = bquote(mu == .(power_mu) ~ "," ~ sigma == .(poisson_sigma)))
p_2_2
```

##Modulated Poisson sigma

```{r}
p_2_3 <-plot_suplementary_model(individual_fits_2_3) +
  labs(title = bquote(mu == .(power_mu) ~ "," ~ sigma == .(modulated_poisson_sigma)))
p_2_3
```

##Multiplicative sigma

```{r}
p_2_4 <-plot_suplementary_model(individual_fits_2_4) +
  labs(title = bquote(mu == .(power_mu) ~ "," ~ sigma == .(mult_sigma)))
p_2_4
```

##Power sigma

```{r}
p_2_5 <-plot_suplementary_model(individual_fits_2_5) +
  labs(title = bquote(mu == .(power_mu) ~ "," ~ sigma == .(power_sigma)))
p_2_5
```

graph

```{r}
p_2 <- plot_grid(p_2_1, p_2_2, p_2_3, p_2_4, p_2_5,
          nrow = 5,
          labels = c("A", "B", "C", "D", "E"),
          label_size = 10)

ggsave("figures/p_2.pdf", p_2, width = 7.5, height = 8.5)
```

#Sym naka model ##constant sigma

```{r}
p_3_1 <- plot_suplementary_model(individual_fits_3_1) +
  labs(title = bquote(mu == .(sym_naka_mu) ~ "," ~ sigma == .(ad_sigma)))
p_3_1

```

##Poisson sigma

```{r}
p_3_2 <- plot_suplementary_model(individual_fits_3_2) +
  labs(title = bquote(mu == .(sym_naka_mu) ~ "," ~ sigma == .(poisson_sigma)))
p_3_2
```

## Modulated Poisson sigma

```{r}
p_3_3 <-plot_suplementary_model(individual_fits_3_3) +
  labs(title = bquote(mu == .(sym_naka_mu) ~ "," ~ sigma == .(modulated_poisson_sigma)))
p_3_3
```

##Multiplicative sigma

```{r}
p_3_4 <-plot_suplementary_model(individual_fits_3_4) +
  labs(title = bquote(mu == .(sym_naka_mu) ~ "," ~ sigma == .(mult_sigma)))
p_3_4
```

##Power sigma

```{r}
p_3_5 <-plot_suplementary_model(individual_fits_3_5) +
  labs(title = bquote(mu == .(sym_naka_mu) ~ "," ~ sigma == .(power_sigma)))
p_3_5
```

graph

```{r}
p_3 <- plot_grid(p_3_1, p_3_2, p_3_3, p_3_4, p_3_5,
          nrow = 5,
          labels = c("A", "B", "C", "D", "E"),
          label_size = 10)

ggsave("figures/p_3.pdf", p_3, width = 7.5, height = 8.5)
```

#Asym naka model ##constant sigma

```{r}
p_4_1 <- plot_suplementary_model(individual_fits_4_1) +
  labs(title = bquote(mu == .(asym_naka_mu) ~ "," ~ sigma == .(ad_sigma)))
p_4_1

```

##Poisson sigma

```{r}
p_4_2 <- plot_suplementary_model(individual_fits_4_2) +
  labs(title = bquote(mu == .(asym_naka_mu) ~ "," ~ sigma == .(poisson_sigma)))
p_4_2
```

##Modulated Poisson sigma

```{r}

p_4_3 <-plot_suplementary_model(individual_fits_4_3) +
  labs(title = bquote(mu == .(asym_naka_mu) ~ "," ~ sigma == .(modulated_poisson_sigma)))
p_4_3
```

##Multiplicative sigma

```{r}
p_4_4 <-plot_suplementary_model(individual_fits_4_4) +
  labs(title = bquote(mu == .(asym_naka_mu) ~ "," ~ sigma == .(mult_sigma)))
p_4_4
```

##Power sigma

```{r}

p_4_5 <-plot_suplementary_model(individual_fits_4_5) +
  labs(title = bquote(mu == .(asym_naka_mu) ~ "," ~ sigma == .(power_sigma)))
p_4_5
```

##graph

```{r}
p_4 <- plot_grid(p_4_1, p_4_2, p_4_3, p_4_4, p_4_5,
          nrow = 5,
          labels = c("A", "B", "C", "D", "E"),
          label_size = 10)

ggsave("figures/p_4.pdf", p_4, width = 7.5, height = 8.5)
```

##Poisson sigma vs modulated Poisson sigma for the asym naka model #poisson

```{r}
p_4_2_1 <-plot_suplementary_model(individual_fits_4_2_1) +
  labs(title = bquote(mu == .(asym_naka_mu) ~ "," ~ sigma == .(poisson_sigma_escalar)))
p_4_2_1
```

## modulated Poisson

```{r}
p_4_3_1 <-plot_suplementary_model(individual_fits_4_3_1) +
  labs(title = bquote(mu == .(asym_naka_mu) ~ "," ~ sigma == .(modulated_poisson_sigma_escalar)))
p_4_3_1
```

##graph

```{r}
p_4_1 <- plot_grid(p_4_2_1, p_4_3_1,
          nrow = 5,
          labels = c("A", "B"),
          label_size = 10)

ggsave("figures/p_4_1.pdf", p_4_1, width = 7.5, height = 8.5)#8.5)width = 7.5
```

#Logistic function:

```{r}
plot_p_correct_log <- ggplot() +
  facet_wrap(vars(participant), ncol = 4, axes= "all", axis.labels="margins") +
  geom_point(data = prop_logistic_d_p_correct,
             aes(x = (10^x + c_pedestal)*100, y = prop, color = factor(c_pedestal*100)), shape=16, size = 0.5) +
  geom_line(data = psy_logistic_d_p_correct,
            aes(x = (10^x + c_pedestal)*100, y = prop, color = factor(c_pedestal*100)), linewidth=0.3) +
  geom_text(data = prop_logistic_d_p_correct|> group_by(participant) |> slice(1), 
            aes(x = 7, y = 0.5, label = participant),
            size = 2, hjust=0) +
  scale_color_manual(values = c("#CBB2DD", "#9F73C2","#7436A6","#4B1A78")) +
  theme_paper(7) +
  scale_y_continuous(breaks = seq(0, 1, .25)) +
  scale_x_log10(limits = c(NA, 15), expand = c(0, 0)) +
  theme(legend.position = "none",
        strip.text = element_blank(),
        strip.background = element_blank()) +
  xlab("Contrast (%)") +
  ylab("Proportion correct")


legend_discr_log <- get_legend(
  plot_p_correct_log + 
    theme(legend.position = "right") +
    labs(color = "Reference (%)") +
    guides(color = guide_legend(ncol = 2)))


plot_p_correct_legend_log <- ggdraw(plot_p_correct_log) + 
  draw_grob(legend_discr_log, x = 0.81, y = 0.1, width = 0.15, height = 0.3)
plot_p_correct_legend_log
```

```{r}
p_deltas_log <- 
  ggplot() +
  geom_point(data = threshold_logistic, aes(x = c_pedestal*100, y = delta, color = "Discr(thres)"), size = 0.5) +
  geom_line(data = threshold_logistic, aes(x = c_pedestal*100, y = delta, color = "Discr(thres)"), linewidth = 0.2, linetype="dashed") +
  facet_wrap(vars(participant), axes= "all", axis.labels="margins") +
  geom_line(data = m_delta_a, aes(x*100, delta_m, color = "ME"), linewidth = 0.2) +
  geom_line(data = d_delta_a, aes(x*100, delta_d, color = "Discr"), linewidth = 0.2) +
  scale_color_manual(name=NULL,
                     values = c("darkorchid4", "aquamarine4", "darkorchid4"),
                     labels = c("ME" = "ME", "Discr" = "Discr", "Discr(thres)" = "Discr(thres)"),
                     guide = "legend",
                     breaks = c("Discr", "ME", "Discr(thres)")) +
  geom_text(data =  m_delta_a|> group_by(participant) |> slice(1), 
            aes(x = 10, y = 350, label = participant),
            size = 2, hjust=0) +
  theme_paper(7) +
  theme(strip.text = element_blank(),
        strip.background = element_blank(),
          legend.position = "none",
          guides(color = guide_legend(override.aes = list(
    shape = c(NA, NA, 16),            
    linetype = c(1, 1, NA)
  )))) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 2), expand=c(0,0), limits=c(0, NA)) +
  scale_x_continuous(limits=c(0, NA), expand=c(0,0)) +
  xlab("Contrast (%)") +
  ylab("D")

```

```{r}
p_deltas_all_log <- ggplot(sum_deltas |> mutate(contrast=x*100)) +
  geom_point(data = threshold_logistic_all, aes(x = c_pedestal*100, y = delta, color="dot")) +
  geom_line(data = threshold_logistic_all, aes(x = c_pedestal*100, y = delta, color = "dot"), linewidth=0.3, linetype="dashed") +
  geom_line(aes(contrast, estimate, color = model), linewidth=0.3) +
  scale_color_manual(name=NULL,
                     values = c("darkorchid4", "darkorchid4", "aquamarine4"),
                     labels = c("dot" = "Discr(thres)","delta_d" = "Discr", "delta_m" = "ME"),
                     guide = "legend",
                     breaks = c("dot", "delta_d", "delta_m")) +
  theme_paper(7) +
  theme(legend.position = "right")+
  scale_y_continuous(breaks = scales::pretty_breaks(n = 2), expand=c(0,0), limits=c(0, NA)) +
  scale_x_continuous(limits=c(0, NA), expand=c(0,0)) +
  xlab("Contrast (%)") +
  ylab("D") +
  coord_cartesian(ylim=c(0, NA)) +
  guides(color = guide_legend(override.aes = list(
    shape = c(16, NA, NA),            
    linetype = c(1, 1, 1)
  )))
p_deltas_all_log
```

```{r}
p_deltas_all_log_leg <- get_legend(p_deltas_all_log + 
    guides(fill="none") +
    theme(legend.position = "right",
          legend.text = element_text(size=6)))

p_discr_log <- plot_grid(
  plot_p_correct_legend_log,
  p_deltas_log,
  p_deltas_all_log,
  NULL,
  nrow = 2,
  ncol = 2,
  #align = 'vh',
  labels = c("A", "B", "C"),
  label_size = 10)
p_discr_log

p_discr_log_legend <- ggdraw(p_discr_log + 
  draw_grob(p_deltas_all_log_leg, x = 0.9, y = 0.53, width = 0.10, height = 0.2))
p_discr_log_legend
ggsave("figures/p_discr_log_legend.pdf", p_discr_log_legend, width = 6.5, height = 4.7)
```
